### 2020-07-07 article_figures.Rmd
up second part

---
title: "Article - Figures"
author: "Ricour Florian"
date: "June 24 2020"
output: 
  github_document:
    toc : yes
    #number_sections: yes
    fig_width : 8
    fig_height : 6
    #keep_tex : yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, fig.height=4)
library(dplyr)
library(plyr)
library(plotly)
library(grid)
library(gridExtra)
#library(tidyverse)
library(lubridate)
library(ggplot2)
library(chron)
library(ncdf4)
library(reshape2)
#library(ggforce)
library(gsw)
library(suncalc)
library(latex2exp)
```

## Load a bunch of data previously computed

```{r data, echo=T}
# FUCK IT FUCK THIS ARTICLE AND FUCK THE BLACK SEA ÇA ME GONFLE
load(file='dataJune26_2020.RData')
#load(file='../dataJune26_2020.RData')
```

## Chla correction with Raw + Roesler + FDOM + NPQ

```{r chla_correction_functions, include = F, results=F}
#1 Extract data from any variable available in the float data files
ExtractVar <- function(Var,FloatInfo){

  with(FloatInfo,{
    # This function should return a dataframe for the chosen variable with value, qc, iprofile and ilevel
    lvar             <- ncvar_get(ncfile,Var)
    lvar_qc          <- ncvar_get(ncfile,paste0(Var,"_QC"))
    lvar_qctab       <- llply(lvar_qc,function(qcstring){
      as.numeric(unlist(strsplit(qcstring,split="")))
    })
    lvar_qctab <- do.call(cbind,lvar_qctab)

    lvar_dir       <- ncvar_get(ncfile,"DIRECTION")
    lvar_direction <- llply(lvar_dir,function(dirstring){
      strsplit(dirstring,split="")
    })
    lvar_direction <- unlist(lvar_direction)
    # making dataframes, removing the NANs  
    alevels <- 1:N_LEVELS
    d <- ldply(as.list(1:N_PROF),function(iprof){
      indexes <- !(is.na(lvar[,iprof])|is.na(lvar[,iprof]))
      if(sum(indexes) == 0){
        return (data.frame())
      }

      data.frame(value    = lvar[indexes,iprof],
                 qc       = as.integer(lvar_qctab[indexes,iprof]),
                 alevel   = alevels[indexes],
                 depth    = pres[indexes,iprof],
                 dir      = lvar_direction[iprof],
                 aprofile = iprof,
                 variable = Var)
    })

    d$juld <- juld[d$aprofile]
    d$lon  <- lon[d$aprofile]
    d$lat  <- lat[d$aprofile]

    return(d=d)
  })
}  
#2 five-points median filter
mmed <- function(x,n=5){runmed(x,n)}
#3 Determination of day/night profiles
DayOrNight <- function(dataframe){

  d <- ldply(as.list(unique(dataframe$juld)), function(juld){

    #print(juld)

    origin <- ymd_hms("1950-01-01 00:00:00") # julian day origin for the Argo program

    # get temporary profile and metadata
    tmp <- dataframe[dataframe$juld == juld,]
    lat <- tmp$lat[1]
    lon <- tmp$lon[1]
    n <- length(tmp$depth) #number of points in the profile

    # determine day or night
    tmp_juld <- origin + juld * 3600 * 24 #conversion of juld in working day and hour
    date <- format(tmp_juld, tz="Europe/Sofia", usetz=TRUE)
    date2 <- as.Date(as.POSIXct(tmp_juld, 'Europe/Sofia')) # convert juld into a a "Date" object

    hour <- format(as.POSIXct(strftime(tmp_juld,"%Y-%m-%d %H:%M:%S",tz="Europe/Sofia", usetz = T)),format = "%H")
    data <- data.frame(date = date2, lat = lat, lon = lon) # create a dataframe for the function getSunlightTimes
    sun_cycle <- getSunlightTimes(data = data, keep = c("sunset", "sunrise"), tz = "Europe/Sofia")# get the sunset and sunrise hours

    # local sunrise/sunset hours
    hour_sunrise <- as.numeric(format(sun_cycle$sunrise, "%H"))
    hour_sunset <- as.numeric(format(sun_cycle$sunset, "%H"))

    if(is.na(hour_sunrise)){ # needed for profiles without latitude/longitude
      sun <- "NA"
    }else if(as.numeric(hour) < hour_sunset & as.numeric(hour) > hour_sunrise){
      sun <- "day"
    }else{
      sun <- "night"
    }

    date <- rep(date, times = n)
    sun <- rep(sun, times = n)

    data.frame(date = date, day_night = sun)

  })

  return(d)
}
#4 Function to reinitialize dataframes after cleaning (row numbers, new IDs)
clean_remove <- function(dataframe, vector_filter){
  dataframe <- dataframe[dataframe$juld %in% vector_filter,]
  rownames(dataframe) <- NULL
  dataframe <- transform(dataframe, id=as.numeric(factor(juld)))
  dataframe <- dataframe[order(dataframe$id),]
}
#5 Function to normalize data 
normalize <- function(data){
  data <- (data - min(data, na.rm = T))/(max(data, na.rm = T) - min(data, na.rm = T))
}
########
# DATA #
########
filename <- "6903240_Mprof2020.nc"
data <- ldply(as.list(filename),function(file){

  #Opening the file in a open-only mode
  ncfile   <<- nc_open(file, write = FALSE, verbose = F, suppress_dimvals = FALSE)

  print(file)

  #Dimensions
  N_PROF   <- ncol(ncvar_get(ncfile,"PRES"))
  N_LEVELS <- nrow(ncvar_get(ncfile,"PRES"))
  juld     <- ncvar_get(ncfile,"JULD")
  pres     <- ncvar_get(ncfile,"PRES")
  lon      <- ncvar_get(ncfile,"LONGITUDE")
  lat      <- ncvar_get(ncfile,"LATITUDE")

  FloatInfo <- list(N_PROF=N_PROF,
                    N_LEVELS=N_LEVELS,
                    juld=juld,
                    pres=pres,
                    lon=lon,
                    lat=lat)

  chladf <- ExtractVar("CHLA", FloatInfo)
  bbpdf <- ExtractVar("BBP700", FloatInfo)

  if (file == "7900591_Mprof.nc" | file == "7900592_Mprof.nc"){ #change M for merged or S for synthetic profiles
    cdomdf <- as.data.frame(rep(NA, length(chladf$value)))
    colnames(cdomdf) <- "value"
  }else{
    cdomdf <- ExtractVar("CDOM", FloatInfo)
  }

  # for a dimension mismatch issue occurring with FLOAT WMO 6900807 (between BBP and CHLA)
  if(file == "6900807_Mprof.nc"){
    chladf <- join(bbpdf, chladf, by = c("alevel", "aprofile"))
    chladf <- chladf[,11:18]
    cdomdf <- join(bbpdf, cdomdf, by = c("alevel", "aprofile"))
    cdomdf <- cdomdf[,11:18]
  }

  id <- ncvar_get(ncfile, "PLATFORM_NUMBER")

  day_night <- DayOrNight(chladf)

  data.frame(depth    = chladf$depth,
             juld     = chladf$juld,
             fluo     = chladf$value,# fluo = chla converted from fluo data
             bbp      = bbpdf$value,
             cdom     = cdomdf$value,
             qc_fluo  = chladf$qc,
             qc_bbp   = bbpdf$qc, #no qc_cdom because qc_cdom is always 0 so we cannot exploit it
             day      = month.day.year(chladf$juld,c(1,1,1950))$day,
             month    = month.day.year(chladf$juld,c(1,1,1950))$month,
             year     = month.day.year(chladf$juld,c(1,1,1950))$year,
             DOY      = as.integer(strftime(as.Date(chladf$juld,origin = '1950-01-01'), format ="%j")),#Day Of Year
             lon      = chladf$lon,
             lat      = chladf$lat,
             dir      = chladf$dir,
             day_night = day_night$day_night,
             date_long = day_night$date,
             platform = as.numeric(unique(id))
  )
})
```

```{r chla_correction_filter, include = F, results=F}
#REMOVE BAD DATA
data <- data[-(which(data$qc_fluo == 4)),] 
rownames(data) <- NULL
data <- data[-(which(data$depth < 0)),]
#Day of deployment
data <- data[data$DOY == 88 & data$year == 2018,]
smoothed_fluo <- ldply(as.list(unique(data$juld)), function(i){
  tmp <- data[data$juld == i,]
  tmp <- mmed(tmp$fluo, 5)
  data.frame(smoothed_fluo = tmp)
})
smoothed_cdom <- ldply(as.list(unique(data$juld)), function(i){
  tmp <- data[data$juld == i,]
  tmp <- mmed(tmp$cdom, 5)
  data.frame(smoothed_cdom = tmp)
})
#REPLACE FLUO WITH SMOOTHED FLUO & CDOM
data[,3] <- smoothed_fluo
data[,4] <- smoothed_cdom
data <- clean_remove(data, unique(data$juld))
data_info <- ddply(data,~juld,summarize,
                    qc_fluo = qc_fluo[which.max(fluo)],
                    depthmax = depth[which.max(fluo)],
                    maxvalue = fluo[which.max(fluo)],
                    depthmin = depth[which.max(fluo):length(fluo)][which.min(fluo[which.max(fluo):length(fluo)])],
                    integration = sum(fluo),
                    bottomdepth = max(depth),
                    min_depth = min(depth),
                    dir = dir[1],
                    lon=mean(lon),
                    lat=mean(lat),
                    platform = platform[1],
                    day = day[1], month = month[1],
                    year = year[1], DOY = DOY[1])
rm(ncfile, smoothed_cdom, smoothed_fluo)
```

```{r chla_correction_density, include = F, results=F}
# compute density profiles
density_profiles <- ldply(as.list(filename),function(file){

  ncfile   <<- nc_open(file, write = FALSE, verbose = F, suppress_dimvals = FALSE)
  N_PROF   <- ncol(ncvar_get(ncfile,"PRES"))
  N_LEVELS <- nrow(ncvar_get(ncfile,"PRES"))
  juld     <- ncvar_get(ncfile,"JULD")
  pres     <- ncvar_get(ncfile,"PRES")
  lon      <- ncvar_get(ncfile,"LONGITUDE")
  lat      <- ncvar_get(ncfile,"LATITUDE")
  FloatInfo<-list(N_PROF=N_PROF,
                  N_LEVELS=N_LEVELS,
                  juld = juld,
                  pres=pres,
                  lon=lon,
                  lat=lat)

  #NO ADJUSTED VALUE FOR PSAL AND TEMP FOR EACH FLOAT
  tempdf <- ExtractVar("TEMP",FloatInfo)
  tempdf$value[which(tempdf$qc == 4 | tempdf$qc == 3)] <- NA
  psaldf <- ExtractVar("PSAL",FloatInfo)
  psaldf$value[which(psaldf$qc == 4 | psaldf$qc == 3)] <- NA

  #DENSITY ANOMALY BASED ON TEOS-10
  psal <- gsw_SA_from_SP(psaldf$value,psaldf$depth,psaldf$lon,psaldf$lat)
  temp <- gsw_CT_from_t(psal,tempdf$value,tempdf$depth)
  sigma <- gsw_sigma0(psal,temp)

  id <- ncvar_get(ncfile, "PLATFORM_NUMBER")

  data.frame(sigma = sigma,
             depth = tempdf$depth, 
             juld  = tempdf$juld, 
             dir   = tempdf$dir,
             lon   = tempdf$lon,
             lat   = tempdf$lat,
             #day      = month.day.year(tempdf$juld,c(1,1,1950))$day,
             month    = month.day.year(tempdf$juld,c(1,1,1950))$month,
             year     = month.day.year(tempdf$juld,c(1,1,1950))$year,
             DOY   = as.integer(strftime(as.Date(tempdf$juld,origin = '1950-01-01'), 
                                         format ="%j")),
             platform = as.numeric(unique(id)))
})
density_profiles <- clean_remove(density_profiles, unique(data$juld))
data_info <- transform(data_info,id=as.numeric(factor(juld)))
density_profiles <- transform(density_profiles,id=as.numeric(factor(juld)))
#MLD computation
sigma_criteria <- 0.03
depth_ref <- 10
MLDdf <- ldply(as.list(1:length(unique(density_profiles$id))), function(i){

  tmp <- density_profiles[density_profiles$id == i,]
  rownames(tmp) <- NULL

  if(all(is.na(tmp$sigma)) == TRUE){
    MLD <- NA
    sigma_surface <- NA
  }else if(length(tmp$sigma[!is.na(tmp$sigma)==TRUE])>=2){
    sigma_surface<-NA
    sigma_surface <- approx(tmp$depth,tmp$sigma,depth_ref)$y
  }

  if(is.na(sigma_surface) == FALSE){
    MLD <- max(tmp$depth[tmp$sigma <= (sigma_surface + sigma_criteria)], na.rm = T)
  }else{
    MLD <- NA
  }

  if(is.na(MLD) == TRUE){
    sigmaMaxMLD <- NA
  }else{
    sigmaMaxMLD <- mean(tmp$sigma[which(tmp$depth == MLD)], na.rm =T) #check this, pq max mld? #####################################################################
  }

  show(i)

  data.frame(sigma_surface = sigma_surface, MLD = MLD, sigmaMaxMLD = sigmaMaxMLD,
             juld = tmp$juld[1], lat=tmp$lat[1], lon=tmp$lon[1], day = month.day.year(tmp$juld[1],c(1,1,1950))$day,
             month = month.day.year(tmp$juld[1],c(1,1,1950))$month,
             year = month.day.year(tmp$juld[1],c(1,1,1950))$year,
             DOY = as.integer(strftime(as.Date(tmp$juld[1],origin = '1950-01-01'), 
                                       format ="%j")),
             platform = tmp$platform[1])
})
# manual adjust because density inversion
MLDdf$MLD[3] <- 23.5
```

```{r chla_correction_roesler, include = F, results=F}
# add a column to the 'profiles' dataframe with OLD_CHLA (will save the uncorrected chla, can be useful for some plots)
data$raw_fluo <- data$fluo
# Add Roesler Correction
data$fluo <- data$fluo * 0.65
data$raw_roesler <- data$fluo
#EACH PROFILES HAS BEEN VALIDATED SO FAR ==> CALIBRATION EXERCISE STARTS NOW
#LET'S DO IT ONLY FOR THE DEEP PROFILE
#FDOM-based method (Xing et al. 2017)
#keep only the validation profile (i.e. id = 1)
data <- data[data$id == 3,]
data_info <- clean_remove(data_info, unique(data$juld))
MLDdf <- clean_remove(MLDdf, unique(data$juld))
data <- transform(data,id=as.numeric(factor(juld)))
#FDOM-BASED CORRECTION AND MINIMUM-OFFSET CORRECTION
FDOM_OR_MINIMUM_OFFSET_CORRECTION <- ldply(as.list(1:length(unique(data$id))), function(i){
  tmp <- data[data$id == i,]
  MaxDepth <- data_info$bottomdepth[i]#Max depth of the profile
  TopDepth <- data_info$depthmin[i]#Apparent minimum

  if(all(is.na(tmp$cdom)) == TRUE){#no cdom sensor hence minimum-offset correction procedure
    offset <- tmp$fluo[which(tmp$depth == TopDepth)]
    fluo_cor <- tmp$fluo - offset
    fluo_cor[which(tmp$depth == TopDepth):length(tmp$depth)] <- 0
    slope_fdom <- NA
    C <- NA
  }else{#FDOM-based method
    calibrange <- tmp[which(tmp$depth == TopDepth):length(tmp$depth),]
    linearMod <- lm(fluo ~ cdom, data = calibrange)
    slope_fdom <- coef(linearMod)[[2]]
    C <- coef(linearMod)[[1]]
    fluo_cor <- tmp$fluo - slope_fdom*tmp$cdom - C
  }

  data.frame(depth = tmp$depth, fluo_cor = fluo_cor, 
             slope_fdom = rep(slope_fdom, length(fluo_cor)),
             C = rep(C, length(fluo_cor)), juld = tmp$juld[1], platform = tmp$platform[1], year = tmp$year[1])
})
#USE THE FDOM
data[,3] <- FDOM_OR_MINIMUM_OFFSET_CORRECTION$fluo_cor
data$raw_roesler_fdom <- data$fluo
```

```{r chla_correction_quenching, include = F, results=F}
#QUENCHING CORRECTION
#NOTE : This function was given to me by Marin Cornec (PhD Student at the LOV)
quenching_correction <- function(fluo,depth,MLD) {
  if(is.na(MLD) == FALSE){
    f <- fluo[!is.na(fluo) & depth <= MLD]
    d <- depth[!is.na(fluo) & depth <= MLD]
    zMax <- d[which.max(f)]
    Max <- max(f)
    Corfluo <- fluo
    #Criteria from Schmechtig et al. 2014
    if(!is.na(MLD) & min(f[d<=zMax])<=(0.9*Max)) Corfluo[depth<=zMax] <- Max
    return(Corfluo)
  }else{
    return(fluo)
  }
}
#NPQ correction adapted to daily and nightly (DN) profiles
NPQ_correction_DN_adapted <- ldply(as.list(1:length(unique(data$id))), function(i){

  tmp <- data[data$id == i,]

  if(tmp$day_night[1] == "day"){
    correction <- quenching_correction(tmp$fluo, tmp$depth, MLDdf$MLD[i]) # NPQ correction only applies for daily profiles
  }else{correction <- tmp$fluo}#for nightly profiles

  data.frame(fluo_NPQ = correction)
})
data$fluo <- NPQ_correction_DN_adapted$fluo_NPQ # all correction here except the "positivation step" : fluo here = RAW + ROESLER + FDOM + NPQ
#REPLACE < 0 of CHLA by 0 (fair assumption.. ?) ===> MUST BE DONE AFTER THE FDOM CORRECTION (in that case we need to RENORMALIZE CHLA DATA IN PROFILES)
# data$fluo[which(data$fluo < 0)] <- 0
# data$fluo_npq[which(data$fluo_npq < 0)] <- 0
```

```{r RMSE COMPUTATION}

# COMPUTE STATS BELOW

depth_hplc <- c(0,30,50,70,90,100,140,200,250,500,750,1000)
chla_hplc <- c(0.6111,0.6433,0.3090,0.0675,0.0229,0.0168,0.012,0.0032,
               0.0035, 0.0023, 0.0039, 0.0042)
hplc <- as.data.frame(cbind(depth_hplc, chla_hplc))

indexdepth <- vector()

for (i in 1:length(hplc$chla)){
  indexdepth[i] <- which.min(abs(data$depth - hplc$depth_hplc[i]))
}

# RMSE DEEP LAYER FDOM CORRECTED PROFILE
index <- which(hplc$depth_hplc > data_info$depthmin & hplc$depth_hplc < data_info$bottomdepth)
deep_layer <- indexdepth[index]
rmse_deep_layer <- sqrt(sum((hplc$chla_hplc[index] - data$raw_roesler_fdom[deep_layer])^2)/length(hplc$depth_hplc[index]))

# SAME FOR THE RAW PROFILE
rmse_deep_layer_old <- sqrt(sum((hplc$chla_hplc[index] - data$raw_fluo[deep_layer])^2)/length(hplc$depth_hplc[index]))

# RMSE SURFACE LAYER
index <- which(hplc$depth_hplc < data_info$depthmin & hplc$depth_hplc < data_info$bottomdepth)
surface_layer <- indexdepth[index]
rmse_surface_layer <- sqrt(sum((hplc$chla_hplc[index] - data$raw_roesler_fdom[surface_layer])^2)/length(hplc$depth_hplc[index]))

# RMSE SURFACE LAYER with NPQ
index <- which(hplc$depth_hplc < data_info$depthmin & hplc$depth_hplc < data_info$bottomdepth)
surface_layer <- indexdepth[index]
rmse_surface_layer <- sqrt(sum((hplc$chla_hplc[index] - data$fluo[surface_layer])^2)/length(hplc$depth_hplc[index]))

# SAME FOR THE RAW PROFILE
rmse_surface_layer_old <- sqrt(sum((hplc$chla_hplc[index] - data$raw_fluo[surface_layer])^2)/length(hplc$depth_hplc[index]))

## ALL PROFILES RMSE BLABLABLA ---

index <- 1:12
surface_layer <- indexdepth[index]
#fdom
rmse_fdom <- sqrt(sum((hplc$chla_hplc[index] - data$raw_roesler_fdom[surface_layer])^2)/length(hplc$depth_hplc[index]))

#fdom+npq
rmse_npq <- sqrt(sum((hplc$chla_hplc[index] - data$fluo[surface_layer])^2)/length(hplc$depth_hplc[index]))

#raw
rmse_raw <- sqrt(sum((hplc$chla_hplc[index] - data$raw_fluo[surface_layer])^2)/length(hplc$depth_hplc[index]))

```

```{r correction_fig, include = T}
day <- doxy$juld[236208]
oxy <- doxy[doxy$juld == day,] # closest oxy profile (in time) .. (it's the good float at least ..)
#HPLC DATA FROM DEPLOYMENT
depth_hplc <- c(0,30,50,70,90,100,140,200,250,500,750,1000)
chla_hplc <- c(0.6111,0.6433,0.3090,0.0675,0.0229,0.0168,0.012,0.0032,
               0.0035, 0.0023, 0.0039, 0.0042)
hplc <- as.data.frame(cbind(depth_hplc, chla_hplc))

#trick for CDOM
df <- subset(data, select = c('depth', 'cdom'))
df <- df[!duplicated(df$depth),]

deployment <- ggplot(data, aes(x = fluo, y = depth, colour = "ROESLER + FDOM + NPQ")) + geom_path(size = 0.5) +
  scale_y_reverse() + geom_path(data = data, aes(x = raw_roesler_fdom, y = depth, colour = "ROESLER + FDOM")) +
  xlab(expression(Chlorophyll~a~(mg/m^3)))+ ylab("Depth [m]") +
  geom_hline(yintercept = data_info$depthmin[1], color = "black", lty = 2) +
  annotate("text", x = .8, y = data_info$depthmin[1]-20, label = "CHLA MINIMUM") +
  geom_path(data = data, aes(x = raw_fluo, y = depth, colour = "None (RAW)")) + 
  geom_path(data = data, aes(x = raw_roesler, y = depth, colour = "ROESLER")) + 
  geom_point(data = df, aes(x = cdom/10, y = depth), colour = "black", size = .5) + 
  geom_point(data=hplc, aes(y = depth_hplc, x = chla_hplc), colour = "red", size = 2, shape = 15)  + 
  scale_color_discrete(name = "Correction") +
  theme_bw() + theme(legend.position = "none")

zoom_deployment <- ggplot(data, aes(x = fluo, y = depth, colour = "ROESLER + FDOM + NPQ")) + geom_path(size = 0.5) +
  scale_y_reverse(limits = c(100,0)) + geom_path(data = data, aes(x = raw_roesler_fdom, y = depth, colour = "ROESLER + FDOM")) +
  xlab(expression(Chlorophyll~a~(mg/m^3)))+ ylab("Depth [m]") +
  geom_path(data = data, aes(x = raw_fluo, y = depth, colour = "None (RAW)")) + 
  geom_path(data = data, aes(x = raw_roesler, y = depth, colour = "ROESLER")) + 
  geom_point(data=hplc, aes(y = depth_hplc, x = chla_hplc), colour = "red", size = 2, shape = 15)  + 
  scale_color_discrete(name = "Correction") +
  theme_bw() + theme(axis.title.y=element_blank())

grid.arrange(deployment, zoom_deployment, nrow = 1, ncol = 2)
```

# Profile shapes + fitted curves

```{r shapes, include = T}
fit_curve <- function(i){
  tmp <- init_fit[i,]
  juld <- tmp$juld
  tmp2 <- init_profiles[init_profiles$juld == juld,]
  shape <- as.character(tmp$shape)
  tmp2$fluo <- normalize(tmp2$fluo) #
  depthindex <- which.min(tmp2$depth <= 90)
  tmp2 <- tmp2[1:depthindex,]
  tab <- data.frame(x=tmp2$depth,y=tmp2$fluo)
  z <- tab$x
  # only 4 shapes (E has not been encountered)
  if(shape == "G"){
    dat <- as.data.frame(fgauss(z, tmp$Fmax, tmp$Zmax, tmp$dz))
    colnames(dat) <- "fit"
    dat$fit <- normalize(dat$fit)
    dat <- cbind(tmp2$depth, dat)
  }else if(shape == "S"){
    dat <- as.data.frame(fsigmoid(z, tmp$Fsurf, tmp$Zdemi, tmp$s))
    colnames(dat) <- "fit"
    dat$fit <- normalize(dat$fit)
    dat <- cbind(tmp2$depth, dat)
  }else if(shape == "GS"){
    dat <- as.data.frame(fgauss_sigmoid(z, tmp$Fsurf, tmp$Zdemi, tmp$s, tmp$Fmax, tmp$Zmax, tmp$dz))
    colnames(dat) <- "fit"
    dat$fit <- normalize(dat$fit)
    dat <- cbind(tmp2$depth, dat)
  }else if(shape == "GE"){
    dat <- as.data.frame(fgauss_expo(z, tmp$Fsurf, tmp$Zdemi, tmp$Fmax, tmp$Zmax, tmp$dz))
    colnames(dat) <- "fit"
    dat$fit <- normalize(dat$fit)
    dat <- cbind(tmp2$depth, dat)
  }
  ggplot(tmp2, aes(x = fluo, y = depth)) + geom_point() + scale_y_reverse(limits = c(90,0)) +
    xlab("Normalized Chla") + ylab("Depth [m]") + geom_path(data = dat, aes(x = fit, y = tmp2$depth), colour = "red") +
    #theme(text=element_text(size=12)) 
    theme_bw()

}
```

```{r profile_examples}
# # i = 7: jolie sigmoide
# # GS : 12, 103 ! ==> aussi voir 154, 156
# # G : 111 143 178 183 331 487 542 730 830 , TRÈS souvent des doubles pics ..
# # GE : 119, 195
flabels <- c("Gaussian (G)","Sigmoid (S)","Gaussian-Sigmoid (GS)","Gaussian-Exponential (GE)")
profID  <- c(111,7,12,195)

# require(plyr)
# pl<-llply(seq(length(flabels)), function(i){
#   fit_curve(profID[i])+ggtitle(flabels[i])  
# })
# do.call(grid.arrange, pl)

ex1 <- fit_curve(profID[1])+ggtitle(flabels[1]) + theme(axis.title.x=element_blank())
ex2 <- fit_curve(profID[2])+ggtitle(flabels[2]) + theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
ex3 <- fit_curve(profID[3])+ggtitle(flabels[3]) 
ex4 <- fit_curve(profID[4])+ggtitle(flabels[4]) + theme(axis.title.y=element_blank())

grid.arrange(ex1, ex2, ex3, ex4, nrow = 2, ncol = 2)

```

### 2020-07-07 dcm_investigation_clean_Results_AC.Rmd
up second part

---
title: "DCM_investigation"
author: "MAST"
date: "February 20, 2020"
output: 
  github_document:
    toc : yes
    #number_sections: yes
    fig_width : 8
    fig_height : 6
    #keep_tex : yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, fig.height=4)
library(dplyr)
library(plyr)
#library(plotly)
library(grid)
library(gridExtra)
library(processx)
library(lubridate)
library(plyr)
library(ggplot2)
library(latex2exp)
library(pracma)
```

```{r data}
# Load a bunch of data previously computed
# load(file='../wetransfer-fcfe00/data.RData')

load(file='../dataJune2020.RData')

freshstart = FALSE
```

# Validation HPLC ...

# Morphology of the Black Sea Deep Chlorophyll Maximum

The vertical CHl distributions is first explored here by classifying profiles in terms of analytical shape,
in order to identify a subset of profiles presenting DCM signatures.
Despite the use of an adjusted R-squared metric to classify the Chla profiles, it seems that the plasticity of the sigmoid-gaussian formulation provides a best fit in most cases, both for DCMs (Fig. 3a) and non-DCMs (Fig. 3b) profiles.

Non-DCM profiles dominates from October to April.
No cases of exponential profiles are observed. 
The pure sigmoid profiles, denoting a well-homogenized plantkonic biomass in the surface
layer, happen from October to April with a clear peak in December/January consistent with the known dynamic of the mixed
layer depth in the Black Sea (Capet et al., 2014).

DCMs profiles starts to dominate from April to September.
First DCM profiles are recognized as GS and partly GE. 
Only from July, some profiles depicts a pure gaussian shape, denoting a depletion of surface Chla content.
* In principle corresponds to periods where subsurface CHL content is max?*

```{r nicehistogram}
# compute stats per months
tmp_fit <- filter(init_fit, year %in% c(2014:2019)) # remove 2014 
stats_month <- ddply(tmp_fit, ~month, summarize,
                      profiles = length(unique(juld)))

non_dcm <- filter(tmp_fit, !juld %in% unique(fit$juld))
dcm <- filter(tmp_fit, juld %in% unique(fit$juld))

# rename shapes in 'dcm'
# PAS COMPRIS POURQUOI J'AI GALÉRÉ AUTANT
#dcm$shape <- gsub('GS', 'GS_true', dcm$shape) # M'ONT BIEN CASSÉ LES *** LES LEVELS (merci https://stackoverflow.com/questions/21187603/replace-characters-from-a-column-of-a-data-frame-r)

dcm$shape <- gsub('GS', 'GS_true', dcm$shape) 
dcm$shape <- gsub('GE', 'GE_true', dcm$shape)
dcm[dcm$shape == "G",]$shape <- "G_true"

#put it all back in a single fit dataframe
tmp_fit <- rbind(non_dcm, dcm)

stupid <- ddply(tmp_fit, ~month~shape, summarize,
                count = length(unique(juld)),
                count2 = length(unique(juld)))

#stupid2
for (i in c(1:12)){
  stupid[stupid$month == i,]$count <- stupid[stupid$month == i,]$count/stats_month$profiles[i]
  stupid[stupid$month == i,]$count2 <- stats_month$profiles[i]
}

# define colours (avec le "O" shape entre les deux Arthur?)
# https://www.thinkingondata.com/something-about-viridis-library/
# 
#myColors <- c("#440154FF", "#404788FF", "#287D8EFF", "#3CBB75FF","#DCE319FF") #based on viridis (https://www.thinkingondata.com/something-about-viridis-library/)
# https://bhaskarvk.github.io/colormap/
myColors <- c("#13306DFF", "#6B4596FF", "#403891FF", "#042333FF", "#A65C85FF", "#EB8055FF", "#F9B641FF", "#E8FA5BFF")
#myColors <- brewer.pal(5,"Set1") # can be modified for other colours
names(myColors) <- c("G", "GE", "GS", "S", "O", "G_true", "GS_true", "GE_true") #https://stackoverflow.com/questions/6919025/how-to-assign-colors-to-categorical-variables-in-ggplot2-that-have-stable-mappin
colScale <- scale_fill_manual(name = "shape",values = myColors)

library(scales)
# https://askcodez.com/ggplot-remplace-count-avec-un-pourcentage-dans-geom_bar.html

mylabs<-lapply(seq(12), function(i){paste0(month.abb[i],'\n',format(ddply(tmp_fit, ~month, summarize,
                count = length(unique(juld)))$count[i]))})

ggplot(stupid, aes(x = month, fill = shape, y = count)) +
  geom_bar(stat='identity') +
  theme_bw() + 
  scale_x_continuous(breaks = c(1:12), labels = mylabs,name='') +
  scale_y_continuous(breaks = c(0,0.25,0.5,0.75,1), labels = scales::percent(c(0,0.25,0.5,0.75,1)),name='') +
  scale_fill_manual(name = "Best-fitting Form",values = myColors,
                    labels=list("non-DCM : Sigmoïd",
                                "non-DCM : Gaussian-Sigmoïd",
                                "non-DCM : Gaussian-Exponential",
                                "non-DCM : Gaussian",
                                "Others",
                                "DCM : Gaussian-Sigmoïd",
                                "DCM : Gaussian-Exponential",
                                "DCM : Gaussian"))

```

# Seasonal Time-Series

```{r Processing, error=FALSE, warning=FALSE, echo=FALSE, message=FALSE, results='hide', include=FALSE, eval=TRUE}
# Prepare data for Temporal Series
if (freshstart){

tmp <- init_profiles
tmp_fit <- init_fit

## MODIF to avoid ordering errors ##
#tmp_fit$dcm_or_not <- NA
fit$dcm_or_not <- 1
tmp_fit <- merge(tmp_fit, fit[,c('juld','platform','dcm_or_not')],by=c('juld','platform'), all = TRUE)
tmp_fit$dcm_or_not[is.na(tmp_fit$dcm_or_not)]<-0
#tmp_fit$dcm_or_not[which(tmp_fit$juld %in% fit$juld)] <- "DCM"
####

# Add scalr diagnostics to the complete dataframe for vertical integration
complete_tmp <- merge(tmp,tmp_fit[,c('juld','platform','MLD','Zmax','Zdemi')], by=c('juld','platform'))

#### This is making trouble .; probably because depth of light and other measurement are different.. 
#complete_tmp_par <- merge(complete_tmp,
#                          initPAR[,c('depth','juld','par','platform')],
#                          by=c('depth','juld','platform'),
#                          all.x=TRUE)

optical_depth <- c(6,6,6,7.5,7,7,7.5,9,8,6.5,6,6) #1/k = optical depth ==> we have a value for each month

}
```

```{r Functions, error=FALSE, warning=FALSE, echo=FALSE, message=FALSE, results='hide', include=FALSE, eval=TRUE}
############
# Functions to apply to profiles
############

# Attempt for uniroot.. not working for now. 
content_z<-function(z, depth, fluo,total){
  print(paste0('my total is', as.character(total)))
  ztot <- sum(approx(x=depth, y=fluo,xout = seq(0,z), rule = 2)$y, na.rm=T)
  print(paste0('my local total for Z:',as.character(z),'is', as.character(ztot)))
  diff <- 0.9*total-ztot
  return (diff)
}

# Stupid function to find the lower boundary of core X% CHL content.
depth90B<-function(depth, fluo, total,p=.9){
#  print(total)
  # return the depth over which integration should be doe to capture 95 % of the total CHL content.
  loctot<-0
  z90 <-14
  while(loctot<p*total){
      z90=z90+1
      loctot = sum(approx(x=depth, y=fluo,xout = seq(0,z90), rule = 2)$y, na.rm=T)
  }
  return(z90)
}

depth90T<-function(depth, fluo, total,p=.9){
#  print(total)
  # return the depth over which integration should be doe to capture 95 % of the total CHL content.
  loctot<-0
  z90 <-100
  while(loctot<p*total){
      z90=z90-1
      loctot = sum(approx(x=depth, y=fluo,xout = seq(z90,200), rule = 2)$y, na.rm=T)
  }
  return(z90)
}

#########
# Light #
#########

grad_att <- function(PRESr,k,PAR0){
  PAR<-PRESr*0
  kint<-(c(k[1],k)+c(k,k[length(k)]))/2
  PAR[1]<-PAR0*exp(-kint[1]*PRESr[1])
  for (i in 2:length(PAR)){
    PAR[i]<-PAR[i-1]*exp(-((kint[i]+kint[i])/2    )*(PRESr[i]-PRESr[i-1]))
  }
  return(PAR)
}

Att_2band <- function(PRES,PAR0,ks0,kl0,depthP0=0) {
  ##  "CHL_2BANDS" ##
  # CHLA specific attenuation + two bandwidths
  if (depthP0 !=0){
    PAR0  = PAR0/(parts*exp(-ks0*depthP0)+(1-parts)*exp(-kl0*depthP0)  ) 
  }
  PAR0s <- PAR0*parts
  PAR0l <- PAR0*(1-parts)
  ks    <- rep(ks0,length(PRES))
  kl    <- rep(kl0,length(PRES))
  PARs  <- grad_att(PRES,ks,PAR0s)
  PARl  <- grad_att(PRES,kl,PAR0l)
  PAR<-PARs+PARl
  return(PAR)
}

p2b_start = c(PAR0 = 1500 ,  ks0 = 0.04 , kl0=0.001) 
p2b_lower = c(PAR0 = 0    ,  ks0 = 0    , kl0=0    )
p2b_upper = c(PAR0 = 2500 ,  ks0 = 3   , kl0=10)

Out_Default <- data.frame("PAR0"=NA,
                          "ks0"=NA,
                          "kl0"=NA)
parts = 0.37
DefOut_isoPAR <-NA

## Filter function to select eligible profiles
#countcheck<-1
FilterForPAR<-function(depth,PAR){
 # countcheck<<-countcheck+1
  # if (countcheck<10){
  #   print(depth)
  #   print(PAR)
  #   print(sum(is.na(PAR))>length(PAR)/2)
  #   readline(prompt="Press [enter] to continue")
  # }
  return (sum(is.na(PAR))<length(PAR)/2)
}

## First attempt derives APR @ 1m from interpolation and look for 1/100 of this value
isoPAR <- function(depth, PAR){
  require(pracma)
  # Intended for Casted DF
  if (FilterForPAR(depth,PAR)){
    out    <- try_default({
    d <- depth[which( !is.na(depth) & PAR>0.1  )]
    P <- PAR[which( !is.na(depth) & PAR>0.1  )]
             p1 <-interp1(d,P, 1)      
      z100 <- interp1(P,d, p1/100) 
      return(z100)},
      DefOut_isoPAR)
  }else{
    out <- DefOut_isoPAR
  }
  return(out)
}

## Second option 
isoPARb <- function(depth, PAR){
  require(pracma)
  # Intended for Casted DF
  if (FilterForPAR(depth,PAR)){
    out    <- try_default({
    d <- depth[which( !is.na(depth) & PAR>0.1  )]
    P <- PAR[which( !is.na(depth) & PAR>0.1  )]

    m <<-nls(PAR ~ Att_2band(depth,PAR0,ks0,kl0),
           data = data.frame(depth=depth, PAR=PAR),
           start = p2b_start, 
           lower = p2b_lower,
           upper = p2b_upper,
           algorithm = "port", 
           control = list(maxiter= 1000)
           )
    mcoef  <<- coef(m)
    PAR0   <-mcoef[1]
    PARcon <- predict(m,data.frame(depth=seq(1,200)))    
    z100 <- interp1(PARcon,seq(1,200), PAR0/100) 
      return(z100)},
      DefOut_isoPAR)
  }else{
    out <- DefOut_isoPAR
  }
  return(out)
}

# PAR2bands <- function(profile){
#   # Intended for Casted DF
#   if (FilterForPAR(profile)){
#     out <-try_default({
#       m   <-nls(PAR ~ Att_2band(depth,PAR0,ks0,kl0),
#           data = profile,
#           start = p2b_start, 
#           lower = p2b_lower,
#           upper = p2b_upper,
#           algorithm = "port", 
#           control = list(maxiter= 1000)
#           )
#       return(as.data.frame(t(coef(m))))},
#     Out_Default)
#   }else{
#     out <- Out_Default
#   }
#   return(out)
# }

# depth90b<-function(depth, fluo, total){
#   # return the depth over which integration should be doe to capture 95 % of the total CHL content.
#   print(total)
#   print(content_z(20, depth=depth, fluo=fluo, total=total))
#     print(content_z(30, depth=depth, fluo=fluo, total=total))
#       print(content_z(40, depth=depth, fluo=fluo, total=total))
#   z90=uniroot(content_z,c(10,200), depth=depth, fluo=fluo, total=total,tol = 1)
#   print(z90)
#   return(z90)
# }
```

```{r light integrated diags, error=FALSE, warning=FALSE, echo=FALSE, message=FALSE, results='hide', include=FALSE, eval=TRUE}

# To compute light diagnostics, ie. iso 1% of surface PAR. 
## Two methods are operational. (see functions isoPAR and isoPARb)
## At the moment, the second one allows more values, as the first one is not working when no light data are available near-surface.

if (freshstart){
integrated_diags_par <- ddply(initPAR, .(juld,platform), summarize,
                          Ziso1 = isoPAR(depth = depth , PAR = par),
                          Ziso1b = isoPARb(depth = depth , PAR = par)
                          )
}

```

```{r}
# Add scalr diagnostics to the complete dataframe for vertical integration
if (freshstart){
complete_tmp2 <- merge(complete_tmp,integrated_diags_par, by=c('juld','platform'), all.x = TRUE)
}

```

```{r IntegratedDiagsdf, error=FALSE, warning=FALSE, echo=FALSE, message=FALSE, results='hide', include=FALSE, eval=TRUE}
# TOTAL CHL, integration using first linear interpolation on a regular grid, then sum.
if (freshstart){
integrated_diags <- ddply(complete_tmp2, .(juld,platform), summarize,
                          # TOTAL CHL, integration using first linear interpolation on a regular grid, then sum.
                            total_chla    = sum(approx(x=depth, y=fluo,xout = seq(0,200), rule = 2)$y, na.rm=T),
                          # chl content relative to MLD depth
                            DoMLD_chla    = sum(approx(x=depth, y=fluo,xout = seq(0,200), rule = 2)$y[round(unique(MLD)):200]),
                            UpMLD_chla    = sum(approx(x=depth, y=fluo,xout = seq(0,200), rule = 2)$y[  0:round(unique(MLD))]),
                            RaMLD_chla    = UpMLD_chla/total_chla*100,
                          # Visible part based on monthly optical depth
                            optic_depth   = optical_depth[unique(month)]*3,
                            visible_chla  = sum(approx(x=depth, y=fluo,xout = seq(0, optic_depth), rule = 2)$y, na.rm=T), 
                            visible_ratio = visible_chla/total_chla*100, 
                          # Content around DCM 
                            DCMcontent    = try_default(
                              sum(approx(x=depth, y=fluo,xout = seq(round(unique(Zmax)-10), round(unique(Zmax)+10)), rule = 2)$y, na.rm=T),
                              NA, quiet = FALSE), 
                            DCMratio      = DCMcontent/total_chla*100 ,
                          # sigma @ Zdemi 
                          # by definition, sigma @ MLD follows sig surface by a fixed amont. 
                            #sigmaMLD      = sigma[which.min(depth)],
                            ZLow           = min(depth[fluo<0.01]),
                          #  Z90           = depth90b(depth = depth , fluo = fluo,total = total_chla),
                            Z90B           = depth90B(depth = depth , fluo = fluo,total = total_chla, p=0.75),
                            Z90T           = depth90T(depth = depth , fluo = fluo,total = total_chla, p=0.75),
                            sigmalow       = try_default(approx(x=depth, y=sigma, xout=ZLow, rule=2)$y,NA, quiet = FALSE),
                            sigma90B       = try_default(approx(x=depth, y=sigma, xout=Z90B, rule=2)$y,NA, quiet = FALSE),
                            sigma90T       = try_default(approx(x=depth, y=sigma, xout=Z90T, rule=2)$y,NA, quiet = FALSE),
                            sigmaMLD       = min(sigma, na.rm = TRUE),#[which.min(depth)],  !! THIS IS NOT CORRECT !!
                            sigmaMAX       = try_default(approx(x=depth, y=sigma, xout=unique(Zmax), rule=2)$y,NA, quiet = FALSE),
                            sigmaDEMI      = try_default(approx(x=depth, y=sigma, xout=unique(Zdemi), rule=2)$y,NA, quiet = FALSE), 
                            #Ziso1         = isoPAR(depth = depth , PAR = par),
                            sigmaiso1      = try_default(approx(x=depth, y=sigma, xout=unique(Ziso1b), rule=2)$y,NA, quiet = FALSE)
                          )
}
```

```{r IntegratedDiagsMerge, error=FALSE, warning=FALSE, echo=FALSE, message=FALSE, results='hide', include=FALSE, eval=TRUE}
if (freshstart){
# !!!!! Carefull here, this is much cleaner that the following commented line
# which does not ensure that the order corresponds, only hte number of elements !!!!!!
# Took me a while to track why this was causing different results !! 
tmp_fitc<-merge(tmp_fit ,integrated_diags, by = c('juld','platform'))

tmp_fitc<-merge(tmp_fitc ,integrated_diags_par, by = c('juld','platform'), all.x = TRUE)
#tmp_fit$total_chla_content <- total_chla_content$total_chla

# remove 2014 .. (not enough data) or not.
tmp_fitc   <- tmp_fitc[tmp_fit$year %in% c(2014:2019),]

tmp_my <- ddply(tmp_fitc, .(month,year), summarize,
                nprof = length(dcm_or_not),
                percentage_dcm =  sum(dcm_or_not)/length(dcm_or_not)*100
                ) 
}
```

```{r}
# Just to save time when kniotting multiple times. 
if (freshstart) {
 save.image(file='./CleanResultsData.RData') 
}else{
load(file='./CleanResultsData.RData')
}
```

To avoid overinterpreting in winter, we remove for DCM characs, the months for which percentage DCM is below 50.
So diagnostics based on DCM criterion are cancelled for those periods for which DCM dynamics is not representative.
```{r}

tmp_fitco<- tmp_fitc
tmp_fitco$dcm_or_not[tmp_fitco$shape=="O"]<-1
tmp_fitc[which((tmp_fitc$month<4)|(tmp_fitc$month>10)),c('Zmax','sigmaMAX','DCMratio')]<-NA
tmp_fitco[which((tmp_fitco$month<4)|(tmp_fitco$month>10)),c('Zmax','sigmaMAX','DCMratio','chla_dcm')]<-NA
#tmp_fitco[which((tmp_fitco$month<4)|(tmp_fitco$month>10)),c('Zmax','sigmaMAX','DCMratio')]<-NA
```

# Back Scattering Validation of the DCM -> DPM relation

I want to use backscattering values, to comment on the fact that DCM correspond to a maximum in DBM, or relates on to another in some ways.

## First Approach.

* I'll use all DCM profiles
* I'll normalize them using 
    * CHL@DCM to normalize chl
    * z@DCM to normalize the vertical scale. 
* Plot this, plot bbp on the same normalized axis.

```{r}
dbdf<- subset(complete_tmp2, select = c('juld','platform','depth','sigma','fluo','bbp','Zmax','month','lon'))
dbdf<-merge(dbdf, subset(tmp_fitc,select = c('juld','platform','dcm_or_not','chla_dcm','sigmaMAX','sigmaMLD','MLD')), by = c('juld','platform'))
dbdf<- subset(dbdf,dcm_or_not==1)

dbdf<-subset(dbdf, (month>2)&(month<11))
dbdf<-subset(dbdf, !is.nan(Zmax))

dbdf$fluo_norm <- dbdf$fluo/dbdf$chla_dcm
dbdf$sigma_norm <- (dbdf$sigma-dbdf$sigmaMLD)/(dbdf$sigmaMAX-dbdf$sigmaMLD+.00000001)
dbdf$depth_norm <- (dbdf$depth-dbdf$MLD)/(dbdf$Zmax-dbdf$MLD+.00000001)
#dbdf$depth_norm_layers<-factor(dbdf$depth_norm_layers,levels=rev(levels(dbdf$depth_norm_layers)))

dbdf<-ddply(dbdf,.(platform, juld),mutate,
            bbpmax= max(bbp[depth_norm<1.5]),
            bbp_norm1 = bbp/bbpmax,
            bbp_DCM = approx(depth,bbp,Zmax)$y,
            bbp_norm2 = bbp/bbp_DCM)

dbdf$sigma_norm_layers <- cut(dbdf$sigma_norm,seq(0.05,3.05,.1))
dbdf$depth_norm_layers <- cut(dbdf$depth_norm,seq(0.05,3.05,.1))
```

```{r}
blbl<-subset(dbdf, select=c("sigma_norm_layers","fluo_norm", "depth_norm_layers","depth_norm","sigma_norm","bbp_norm1","month",'lon'))
require(reshape2)
blbl<-melt(blbl, id.vars=.(sigma_norm_layers,depth_norm_layers,month,depth_norm,sigma_norm,lon))

blbl$monthn<-factor(blbl$month, labels = month.abb[unique(blbl$month)])

blbl$variable<-as.character(blbl$variable)
blbl$variable[which(blbl$variable=="fluo_norm")]<-"Chla - norm."
blbl$variable[which(blbl$variable=="bbp_norm1")]<-"Bbp - norm."

blbl$variable<-factor(blbl$variable, levels=c("Chla - norm.","Bbp - norm."))

bigplot1<-ggplot(subset(blbl, month %in% c(3,4,5,6)), aes(x=depth_norm, y=value))+
      geom_boxplot(aes(group=depth_norm_layers), outlier.size=0.5)+
  theme_bw()+coord_flip(xlim = c(0,2), ylim=c(0,1.5))+
  facet_grid(monthn~variable)+
  geom_vline(xintercept  = 1)+xlab('Depth - norm.')+ylab('')

bigplot2<-ggplot(subset(blbl, month %in% c(7,8,9,10)), aes(x=depth_norm, y=value))+
      geom_boxplot(aes(group=depth_norm_layers), outlier.size=0.5)+
  theme_bw()+coord_flip(xlim = c(0,2), ylim=c(0,1.5))+
  facet_grid(monthn~variable)+
  geom_vline(xintercept  = 1)+xlab('Depth - norm.')+ylab('')
```

```{r bigplotbackscat}
grid.arrange(bigplot1+scale_x_reverse(),
             bigplot2+scale_x_reverse(), nrow=1)
```

## Second Approach

Using DBM from analytical fits

```{r}
bothfit<-merge(fit, fit_BBP, by=c("platform", "juld","month",'lon','lat'))

bothfit$monthn<-factor(bothfit$month, labels = month.abb[unique(bothfit$month)])

ggplot(subset(bothfit, (dcm_or_not==1) &
                (r2adj.y>0.95)&
                grepl('G',bothfit$shape.y)&
                (month %in% seq(3,10))),
       aes(x=Zmax.x, y=Zmax.y, color=factor(month)))+
  geom_point()+theme_bw()+ylim(c(-10,60))+xlim(c(-10,60))+geom_abline(slope = 1,intercept = 0)+
  facet_wrap(~monthn)+xlab(TeX('$z_{DCM}'))+ylab(TeX('$z_{DBM}'))
```

# Depth horizons

!!! Probably have to add lights characteristics !!!

Let's consider $Z_{1/2}$ as indicative of the lower boundary of the depth area with signicant CHL concentration. 
Indeed, Sigmoid gaussian profiles are dominant through the years, with a long tail covering insignifiant CHL values over a large depth range.

**C'est clair ça ? **

The deeper winter MLD bounds the productive area in winter. 
Starting with the stratification onset in March, when MLD goes up, the chloropyll content penetrates deeper, with a rapid creation of DCM.
$Z_{DCM}$ starts at $Z_{1/2}$ (April), dissociate from $Z_{1/2}$ in June, and can't **(?)** be distinguished from $Z_{1/2}$ from July on.

Very low variabiliity of summer MLD, but larger in winter. 
Most probably winter MLD scatter is associated with spatial variability **(can be answered, I mean in regards with interannual variability)**.

```{r depth}
require(reshape2)
MyPal<-'Dark2'

# To remove/add line in the plot below, simply remove/add a variable in the list. (e.g. add 'Zdemi',)
tmp_zmax1 <- subset(tmp_fitco, select = c('month','year','dcm_or_not','shape','MLD','Zmax','ZLow','Z90B','Z90T','Ziso1b'))

tmp_zmax1$Zmax[tmp_zmax1$dcm_or_not==0]<-NA
tmp_zmax1$Zmax[tmp_zmax1$Zmax>200]<-NA
tmp_zmax1$Zdemi[tmp_zmax1$shape %in% c("O","GE","G")]<-NA

tmp_zmax <- melt(tmp_zmax1[,-which(colnames(tmp_zmax1)=='dcm_or_not')], id.vars=c('month','year','shape'))

ggplot(tmp_zmax, aes(x=month, fill=variable, color=variable)) +
    geom_smooth(aes(y=value),stat = 'summary',
#              fun.data = median_hilow,
             fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95), alpha=0.5)+
  geom_boxplot(aes(y=value, group=interaction(month,variable)), alpha=0.2, notch = TRUE)+
        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12)) +
          scale_y_reverse(breaks = seq(100,0,-10), minor_breaks = NULL) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab('[m]')+theme_bw()+coord_cartesian(ylim=c(100,0))+
  #scale_y_reverse()+
    scale_color_brewer(aesthetics = c("colour", "fill"),
                       type = qual ,
                       palette=MyPal,
                       name="Depth Horizons", 
                       labels=list(TeX('$z_{MLD}$'),
                                TeX('$r_{DCM}$'),
                                TeX('$z_{low}$'),
                                TeX('$z_{50,bottom}$'),
                                TeX('$z_{50,top}$'),
                                TeX('$z_{\\mathrm{PAR}\\,1%}$')))
```

## Density Horizons

Density framework shows less spatial variability, and more stable seasonal evolution.

The deepest winter MLD sets pycnal layer of Z_1/2, which remains stable from February to September.
From may to june, a DCM forms and migrate to higher layers.

Unlike the previous plot, the pycnal coordinates allow to dissociate DCM from June to September.
This is indicative of pycnal or mixing forces ruling the location of the DCM, rather than restrictevely light conditions wich tend to be more related to the depth [m] scale.

Obviously nutrient content follows isopycnal layers.
Konovalov (2006) locates the nitrate nitracline at 15.5 kg/m3.

Between August and October, it seems the lower part of CHL limited and Sigma_1/2 rejoins Sigma_max. Light limitation by a well formed DCM ? 
Indeed, it's in August that the percentage of CHL around DCM is highest, so that CHL density in the DCM zone is the thickest. 
**Something strange with MLD .. How many defined MLD in summers ? Is there less ? is that what explain low variability in summer?**
**I changed the definition of sigma MLD above, but ... dont get it.**

```{r sigma}
tmp_sig1 <- subset(tmp_fitco, select = c('month','sigmaMLD','sigmaMAX','sigmalow','sigma90B','sigma90T','sigmaiso1' ,'dcm_or_not','year','shape'))

tmp_sig1$sigmaMAX[tmp_sig1$dcm_or_not==0]<-NA
tmp_sig1$sigmaMAX[tmp_sig1$Zmax>200]<-NA
#tmp_sig1$Zdemi[tmp_sig1$shape %in% c("O","GE","G")]<-NA

tmp_sig <- melt(tmp_sig1[,-which(colnames(tmp_sig1)=='dcm_or_not')], id.vars=c('month','year','shape'))

ggplot(tmp_sig, aes(x=month, fill=variable, color=variable)) +
    geom_smooth(aes(y=value),stat = 'summary',
#              fun.data = median_hilow,
              fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95), alpha=0.5)+
  geom_boxplot(aes(y=value, group=interaction(month,variable)), alpha=0.2, notch = TRUE)+
        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab('[kg/m3]')+theme_bw()+coord_cartesian(ylim=c(16,10))+scale_y_reverse()+
      scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal,
                       name="Density Horizons", 
                       labels=list(TeX('$\\sigma_{MLD}$'),
                                TeX('$\\sigma_{DCM}$'),
                                TeX('$\\sigma_{low}$'),
                                TeX('$\\sigma_{50,bottom}$'),
                                TeX('$\\sigma_{50,top}$'),
                                TeX('$\\sigma_{\\mathrm{PAR}\\,1%}$')))+
  geom_hline( yintercept = 14.5)

## How to maintain all data even those out of axis limits : https://stackoverflow.com/questions/25685185/limit-ggplot2-axes-without-removing-data-outside-limits-zoom

```

## Vertical distribution of the CHL content

In Summer, about 50-60 % (up to 75%) of the total chlorophyll content is located in a narrow 20m band around the DCM. 
This DCM is located between 30-40m, which is about 4 times the optical depth estimated as the inverse of PAR attenuation profiles.

The question is how much of this is missed by satellite ? 
From May to August, less than 20% of the total Chl content is above the MLD (~)
```{r parts}
require(reshape2)
tmp_part <- melt(subset(tmp_fitco, select = c('month','year','RaMLD_chla','DCMratio')), id.vars=c('month','year'))
#,'visible_ratio'

ggplot(tmp_part, aes(x=month, fill=variable, color=variable)) +
    geom_smooth(aes(y=value),stat = 'summary',
#              fun.data = median_hilow,
              fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95), alpha=0.5)+
        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12)) +
        scale_y_continuous(breaks = seq(0,100,10), minor_breaks = NULL) +
    geom_boxplot(aes(y=value, group=interaction(month,variable)), alpha=0.2)+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab('[%]')+theme_bw()+
  scale_color_brewer(name='Part of tot. Chl:',
                     labels=c('above MLD','within 5m of DCM','above optical depth'),
                     aesthetics = c("colour", "fill"),type = qual ,palette=MyPal)#+ylim(c(0,100))
```
## Concentrations

Here we compare CHL concentrations at DCM and surface to the average Chl Content.

Average CLH content is considered by dividing the vertically integrated chla content with a constant scaling depth of 40m, 
chosen as the mean of Z 1/2, as discussed above.

Except from the hint of a bloom in March, the total CHL content does not
indicate very strong seasonal variations.

Instead, the surface chlorophyll content does decrease by a factor two from April to September, while chl concentrations at DCM are above average.

We note the increase in August, that was suggested to limit CHL at depth in the previous sections (ref{sec_season_sigma}).

```{r concentrations}
require(reshape2)
tmp_conc1<-subset(tmp_fitco, select = c('total_chla','chla_surf','chla_dcm','month','year','dcm_or_not'))

tmp_conc1$chla_dcm[tmp_conc1$dcm_or_not==0]<-NA

tmp_conc1$total_chla<-tmp_conc1$total_chla/40

tmp_conc <- melt(tmp_conc1[,-which(colnames(tmp_conc1)=='dcm_or_not')], id.vars=c('month','year'))

  ggplot(tmp_conc, aes(x=month, fill=variable, color=variable)) +
      geom_smooth(aes(y=value),stat = 'summary',
  #              fun.data = median_hilow,
                fun.data = mean_cl_boot,
                fun.args = list(conf.int = 0.95), alpha=0.5)+
          scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12)) +
      geom_boxplot(aes(y=value, group=interaction(month,variable)), alpha=0.2)+
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    ylab('[mg/m3]')+theme_bw()+coord_cartesian(ylim=c(0,3.5))+
    scale_color_brewer(aesthetics = c("colour", "fill"),type = qual,
                       palette=MyPal, 
                       name="Chla concentrations",
                       labels=c("Average","Surface","DCM"))
```

# Satellite confrontation

L4 products obtained from CMEMS.
Match-up extracted from CMEMS satellite products at Argo Locations.

Decent correlation (0.59, p<1e-13) between satellite CHL and surface CHL from Argo profilers.
Clear multiplicative bias of 2.1 (larger Argo values).

Here we want to discuss in relative terms about the location of the bulk of Chl content, and how the seasonal cycle of Chloropyll can be grasped by satellite. 
In the following, we thus multiply satellite products by a corrective factor of two, in order to compare seasonal evolutions on a similar scale. 
We do not have at our disposal, sufficient in-situ HPLC data to conclude on the absolute value of CHL here, but the relative context is sufficient for our argument.

A very close relationship is observed between Argo and satellite products at colocation points (nothwithstanding the multiplicative bias).
The Argo curve of surface CHl concetration on this figure, is also in agreement with the seasonal behavior described above considering ARGo profiles over a larger period.

**Attention here, we need to discuss Quenching correction, and the fact that Argo profiles do not extend to surface**

```{r Satellite}

source("AddSat.R")
tmp2019 <- subset(tmp_fit,year==2019)
Sat_tmp2019 <- AddSat(tmp2019)

tmp_sa1        <- subset(Sat_tmp2019, select = c('satCHL','chla_surf','month','year'))
tmp_sa1$satCHL <- tmp_sa1$satCHL
tmp_sa         <- melt(tmp_sa1, id.vars=c('month','year'))

ggplot(tmp_sa,aes(x=month, fill=variable, color=variable))+
geom_smooth(aes(y=value),stat = 'summary',
#              fun.data = median_hilow,
              fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95), alpha=0.5)+
        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12)) +
    geom_boxplot(aes(y=value, group=interaction(month,variable)), alpha=0.2)+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+theme_bw()+ylab('[mg/m3]')+
  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal, name="Surface Chla", labels=c("Satellite","Argo"))

```

## Satellite Comparison

```{r Satellite2}
# Used for coef on next plots.
#-summary(lm(satCHL~chla_surf, Sat_tmp2019))

ggplot(Sat_tmp2019,aes(x=chla_surf,y=satCHL,color=factor(month)))+
  geom_point()+theme_bw()+
  #geom_smooth(method='lm')+
  xlim(c(0,1.5))+ylim(c(0,1.5))+
  geom_abline(intercept = 0,slope = 1,size=2)+
  #geom_abline(intercept = 0,slope = .5,linetype=3)+
  xlab("Argo - [mg/m3]")+ylab("Satellite - [mg/m3]")+
  scale_color_discrete(name='', labels=month.abb)
```

```{r Satellite2_coefs}
cor.test(Sat_tmp2019$satCHL,Sat_tmp2019$chla_surf)

rmserr(Sat_tmp2019$chla_surf,Sat_tmp2019$satCHL)
```

# Discussion

## "Correction of Satellite value"
A DCM dynamics dominates from April to October.
Contains about 50-70 % of total chl content.
Due to this seasonal change in the vertical distribution of Chlorophyll, considering only surface information (as for instance provided by satellite) might lead to underestimate summer total chl content by a factor of up to 3.5 in august.

To estimate this factor, we divided here the average CHL content as defined in Sect. ... (total content/ divided by 40m) by surface content as provided by Argo Floats.

```{r}
tmp_ra2 <- tmp_conc1

tmp_ra2$surfcorrection <- tmp_ra2$total_chla/tmp_ra2$chla_surf

tmp_corr <- melt(subset(tmp_ra2,select=c('month','year','surfcorrection')), id.vars=c('month','year'))

ggplot(tmp_corr, aes(x=month, fill=variable, color=variable)) +
    geom_smooth(aes(y=value),stat = 'summary',
#              fun.data = median_hilow,
              fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95), alpha=0.5)+
        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12)) +
    geom_boxplot(aes(y=value, group=interaction(month,variable)), alpha=0.2)+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab('DCM scaling factor')+theme_bw()+scale_y_continuous(limits=c(0,10), breaks = seq(0,10))+
  scale_colour_discrete(guide=FALSE)+scale_fill_discrete(guide=FALSE)
```

## Navarro's Ratio

First, using Flo's approach

```{r sigma ratio 1, echo=TRUE}
# Compute the SIGMA@MAX MLD for each year and each platform
MLDdf_info1 <- ddply(init_MLD, ~year~platform, summarize,
                maxMLD = max(MLD, na.rm = T),
                sigmaMaxMLD = sigmaMaxMLD[which.max(MLD)])

# Compute the sigma_ratio, i.e. SIGMA@DCM/SIGMA@MAX MLD
 sigma_ratio1 <- ldply(as.list(unique(MLDdf$juld)), function(i){
   tmp <- MLDdf[MLDdf$juld == i,]
   tmp2 <- fit[fit$juld == i,]
   tmp3 <- profiles[profiles$juld == i,]
   sigmaMaxMLD <- MLDdf_info1$sigmaMaxMLD[which(MLDdf_info1$year == tmp$year & MLDdf_info1$platform == tmp$platform)]
   sigmaDCM <- approx(tmp3$depth, tmp3$sigma, tmp2$Zmax)$y #interpolation
   ratio = sigmaDCM/sigmaMaxMLD
   data.frame(ratio = ratio, juld = tmp$juld[1], month = tmp$month[1])
 })

# 1. First plot to see the spread in sigma MAX mld (amongst platfrom).
ggplot(MLDdf_info1, aes(x=factor(year), y=sigmaMaxMLD, color=factor(platform)))+geom_point()+scale_y_continuous(limits=c(13.8,15.0))

 ggplot(sigma_ratio1, aes(x=month, y=ratio)) +
    geom_smooth(stat = 'summary',
#              fun.data = median_hilow,
             fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95), alpha=0.5)+
  geom_boxplot(aes(group=month), alpha=0.2, notch = TRUE)+
  theme_bw()+scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12))+
  scale_y_continuous(breaks = seq(0.8,1.2,0.05), minor_breaks = NULL) +
  ylab('sigma@DCM/sigma@MLD_MAX')
```

First, using Art's approach

```{r sigma_ratio_2, echo=TRUE}
require(scales)
# # # # # # # # # # # # # #
 # As I would have done it #

MLDdf_info2 <- ddply(tmp_fitco, .(year,platform), summarize,
                maxMLD = max(MLD, na.rm = T),
                sigmaMaxMLD = max(sigmaMLD, na.rm = T))

sigma_ratio2 <- ddply(tmp_fitco, .(platform, juld), mutate,
   sigmaMaxMLD = MLDdf_info2$sigmaMaxMLD[which((MLDdf_info2$year == unique(year))
                                              & (MLDdf_info2$platform == unique(platform)))],
   ratio = sigmaMAX/sigmaMaxMLD)

ggplot(MLDdf_info2, aes(x=factor(year), y=sigmaMaxMLD, color=factor(platform)))+geom_point()+scale_y_continuous(limits=c(13.8,15.0))

discfig1<-ggplot(sigma_ratio2, aes(x=month, y=ratio)) +
    geom_smooth(stat = 'summary',
#              fun.data = median_hilow,
             fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95), alpha=0.5,color=brewer_pal(palette = MyPal)(2)[1],fill=brewer_pal(palette = MyPal)(2)[1])+
  geom_boxplot(aes(group=month), alpha=0.2, notch = TRUE,color=brewer_pal(palette = MyPal)(2)[1],fill=brewer_pal(palette = MyPal)(2)[1])+
  theme_bw()+scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12))+
  scale_y_continuous(breaks = seq(0.8,1.2,0.05), minor_breaks = NULL) +
  ylab(TeX('$\\sigma_{DCM}/\\sigma_{MLD,max}$'))
print(discfig1)
```

Comparing Both

```{r sigma_ratio_comp, echo=TRUE, include=FALSE}
###
require(reshape2)
M1<-MLDdf_info1[,c('year','platform','sigmaMaxMLD')]
colnames(M1)[3]<-'sigmaMaxMLD_1'
M2<-MLDdf_info2[,c('year','platform','sigmaMaxMLD')]
colnames(M2)[3]<-'sigmaMaxMLD_2'

MM <- merge(M1,M2,by=c('year','platform'))

ggplot(MM, aes(x=sigmaMaxMLD_1, y=sigmaMaxMLD_2, color=factor(platform), shape=factor(year)))+geom_point()

s1<-subset(sigma_ratio1,select = c("month", "ratio"))
colnames(s1)[2]<-'ratio_1'
s2<-subset(sigma_ratio2,select = c("month", "ratio"))
colnames(s2)[2]<-'ratio_2'

ss <- merge(s1,s2,by=c('month'))
ss <- melt(ss,id.vars=c("month"))

ggplot(ss, aes(x=month, y=value, fill=variable, color=variable))+
  geom_smooth(stat = 'summary',
#              fun.data = median_hilow,
             fun.data = mean_cl_boot,
             fun.args = list(conf.int = 0.95), alpha=0.5)+
  geom_boxplot(aes(group=interaction(month,variable)),
               alpha=0.2, notch = TRUE)+
  theme_bw()+scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12))+
  scale_y_continuous(breaks = seq(0.8,1.2,0.05), minor_breaks = NULL) +
  ylab('sigma@DCM/sigma@MLD_MAX')

```

Interannual checkup
```{r ratio_interannual, include=FALSE}

sigma_ratio2d<-ddply(sigma_ratio2,.(platform, juld), mutate,
                    mY = dmy(paste0("15",sprintf("%02d",month),year)))

ggplot(sigma_ratio2d, aes(x=mY, y=ratio)) +
    geom_smooth(stat = 'summary',
#              fun.data = median_hilow,
             fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95), alpha=0.5)+
  geom_boxplot(aes(group=mY), alpha=0.2, notch = TRUE)+
  theme_bw()+
  scale_y_continuous(breaks = seq(0.8,1.2,0.05), minor_breaks = NULL) +
  ylab('sigma@DCM/sigma@MLD_MAX')

ggplot(sigma_ratio2d, aes(x=mY, y=sigmaMAX)) +
    geom_smooth(stat = 'summary',
#              fun.data = median_hilow,
             fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95), alpha=0.5)+
  geom_boxplot(aes(group=mY), alpha=0.2, notch = TRUE)+
  theme_bw()+coord_cartesian(ylim=c(15,12))+scale_y_reverse()
```

```{r ratio spatial, fig.width=8,fig.height=8}
require(ggmap)
mm <- get_map

mycoord <- c(27,40.5,42,47)
myMap_stamen <- get_map(location=mycoord,source="stamen", maptype="watercolor")
save(myMap_stamen, file="BS_StaMap.Rdata") 
#load(file="BS_StaMap.Rdata")

ms<-ggmap(myMap_stamen, darken = c(0.6,"white"))
ms1<-ms+geom_point(data=subset(sigma_ratio2,(month>3)&(month<11)&(!is.na(ratio))), aes(x=lon,y=lat, color=ratio))+facet_wrap(~month, scale="fixed", ncol=3)+theme_bw()
ms1+scale_color_distiller(palette = 'RdYlBu')#,limits=c(0.9,1.0))
```

```{r ratio_spatial2b}

ddd <- subset(sigma_ratio2,(month %in% c(3,4,5,6,7,8,9,10))&(!is.na(ratio)))
ddd$cutlon <- cut(ddd$lon,breaks = c(27,34.5,42))
ddd$bibi <- factor(interaction(ddd$month,ddd$cutlon), ordered = TRUE)

discfigb1<-ggplot(ddd, 
       aes(x = month, y = ratio, color=cutlon, fill=cutlon))+
  theme_bw()+
   geom_boxplot(aes(group= bibi),
                alpha=0.2, notch = TRUE, varwidth = FALSE, position='dodge2')+
  scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12))+
  scale_color_brewer(aesthetics = c("colour", "fill"),
                     type = qual ,palette=MyPal, name="Longitude", labels=c('West','East')) +
  ylab(TeX('$\\sigma_{DCM}/\\sigma_{MLD,max}$'))

discfigb1

```

## and what about light at DCM ?

```{r paratdcm}
# Attempt to derive PARfraction at the DCM depth

loc <- merge(initPAR, subset(tmp_fitc,select = c("platform","juld","Zmax","Z90T")),by=c("platform","juld"))

PARpartDCM <- function(depth, PAR , Zmax){
  require(pracma)
  #require(nls2)
  if (FilterForPAR(depth,PAR)){
    out    <- try_default({
      d <<- depth[which( !is.na(depth) & PAR>0.1  )]
      P <- PAR[which( !is.na(depth) & PAR>0.1  )]

      # ? nls2
      m <<-nls(PAR ~ Att_2band(depth,PAR0,ks0,kl0),
               data = data.frame(depth=depth, PAR=PAR),
               start = p2b_start, 
               lower = p2b_lower,
               upper = p2b_upper,
               algorithm = "port", 
               control = list(maxiter= 1000)
      )
      mcoef  <<- coef(m)
      PAR0   <-  mcoef[1]
      PARcon <- predict(m,data.frame(depth=c(5,Zmax)))  
      PARpartDCM <- PARcon[2]/PAR0

      ## Other approach ##
      #PARconB <- approx(x = depth,y=PAR,xout = Zmax)$y
      #PARpartDCM <- PARconB/PAR0
      return(PARpartDCM)},
      DefOut_isoPAR)
  }else{
    out <- DefOut_isoPAR
  }
}

integrated_diags_par2 <- ddply(loc, .(juld,platform), summarize,
                          PARpartDCM = PARpartDCM(depth = depth , PAR = par, Zmax=unique(Zmax))                          )

```

```{r PARatDCM2}
#tmp_fitc<-tmp_fitc[,-which(colnames(tmp_fitc)=="PARpartDCM")]
tmp_fitcl<-merge(tmp_fitc ,integrated_diags_par2, by = c('juld','platform'), all.x = TRUE)

discfig2<-ggplot(tmp_fitcl, aes(x=month, y=PARpartDCM*100)) +
    geom_smooth(stat = 'summary',
#              fun.data = median_hilow,
             fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95),
              alpha=0.5,
              color=brewer_pal(palette = MyPal)(2)[2],
              fill=brewer_pal(palette = MyPal)(2)[2])+
  geom_boxplot(aes(group=month), alpha=0.2, notch = TRUE, color=brewer_pal(palette = MyPal)(2)[2],fill=brewer_pal(palette = MyPal)(2)[2])+
  theme_bw()+scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12))+
  scale_y_continuous(breaks = seq(0,5,1), minor_breaks = NULL, limit=c(0,5)) +
  ylab('[% of surface PAR at DCM]')
print(discfig2)

```

```{r PARatDCM2BIS}
#tmp_fitc<-tmp_fitc[,-which(colnames(tmp_fitc)=="PARpartDCM")]
tmp_fitcl<-merge(tmp_fitc ,integrated_diags_par2, by = c('juld','platform'), all.x = TRUE)

tmp_fitcl$cutlon <- cut(tmp_fitcl$lon,breaks = c(27,34.5,42))
tmp_fitcl$bibi         <- factor(interaction(tmp_fitcl$month,tmp_fitcl$cutlon), ordered = TRUE)

# discfigb2<-ggplot(tmp_fitcl, aes(x=cutlon, y=PARpartDCM*100, color=factor(month), fill=factor(month))) +
#   geom_boxplot(aes(group=bibi), alpha=0.2, notch = TRUE)+
#   theme_bw()+#scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12))+
#   scale_y_continuous(breaks = seq(0,5,1), minor_breaks = NULL, limit=c(0,5)) +
#   scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal, name="Month") +
#   ylab('[% of surface PAR at DCM]')
discfigb2<-ggplot(tmp_fitcl, 
       aes(x = month, y = PARpartDCM*100, color=cutlon, fill=cutlon))+
  theme_bw()+
   geom_boxplot(aes(group= bibi),
                alpha=0.2, notch = TRUE, varwidth = FALSE, position='dodge2')+
  scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12))+
  scale_y_continuous(breaks = seq(0,5,1), minor_breaks = NULL, limit=c(0,5)) +
  scale_color_brewer(aesthetics = c("colour", "fill"),
                     type = qual ,palette=MyPal, name="Longitude", labels=c('West','East')) +
  ylab('[% of surface PAR at DCM]')

discfigb2
```

```{r discfig}

 gA <- ggplotGrob(discfig1+geom_text(label='a)', x=3.5, y= 1.05, size=5))
 gB <- ggplotGrob(discfig2+geom_text(label='b)', x=3.5, y= 4.8 , size=5 ))

grid::grid.newpage()
grid::grid.draw(rbind(gA, gB))

#grid.arrange(discfig1+geom_text(label='a)', x=3.5, y= 1.05)+theme(axis.line.y.left=element_text(margin = margin(t = 20)),#+ylab('')
 #            discfig2+geom_text(label='b)', x=3.5, y= 4.8),#+ylab('')
#             ncol=1)
```
```{r discfigb}

 gA <- ggplotGrob(discfigb1+geom_text(label='a)', x=3.5, y= 1.05, size=5, color='black'))
 gB <- ggplotGrob(discfigb2+geom_text(label='b)', x=3.5, y= 4.8 , size=5, color='black' ))

grid::grid.newpage()
grid::grid.draw(rbind(gA, gB))

#grid.arrange(discfig1+geom_text(label='a)', x=3.5, y= 1.05)+theme(axis.line.y.left=element_text(margin = margin(t = 20)),#+ylab('')
 #            discfig2+geom_text(label='b)', x=3.5, y= 4.8),#+ylab('')
#             ncol=1)
```

```{r ratio_PARatDCM, fig.width=10,fig.height=10, include=FALSE, eval=FALSE}

require(ggmap)
mm <- get_map

mycoord <- c(27,40.5,42,47)
myMap_stamen <- get_map(location=mycoord,source="stamen", maptype="watercolor")
save(myMap_stamen, file="BS_StaMap.Rdata") 
#load(file="BS_StaMap.Rdata")

ms<-ggmap(myMap_stamen, darken = c(0.6,"white"))
ms1<-ms+geom_point(data=subset(tmp_fitc,(month>3)&(month<11)&(!is.na(PARpartDCM))), aes(x=lon,y=lat, color=PARpartDCM*100))+facet_wrap(~month, scale="fixed", ncol=2)+theme_bw()
ms1+scale_color_distiller(palette = 'RdYlBu',limits=c(0,6))

# ms2<-ms+geom_point(data=tmp_fitco, aes(x=lon,y=lat, color=factor(shape)))+
#   facet_wrap(~month, scale="fixed")+theme_bw()
# ms2#+scale_color_discrete(name="", labels=c('non-DCM','DCM'))

```

# Potential Additional sections.

## Spatial

Numerous Spatial analysis have been done without concluding results beyond "Homogeneous behavior across the central basin".

```{r spatial}

require(ggmap)
mm <- get_map

mycoord <- c(27,40.5,42,47)
myMap_stamen <- get_map(location=mycoord,source="stamen", maptype="watercolor")
save(myMap_stamen, file="BS_StaMap.Rdata") 
#load(file="BS_StaMap.Rdata")

ms<-ggmap(myMap_stamen, darken = c(0.6,"white"))
ms1<-ms+geom_point(data=tmp_fitco, aes(x=lon,y=lat, color=factor(dcm_or_not)))+facet_wrap(~month, scale="fixed")+theme_bw()
ms1+scale_color_discrete(name="", labels=c('non-DCM','DCM'))

# ms2<-ms+geom_point(data=tmp_fitco, aes(x=lon,y=lat, color=factor(shape)))+
#   facet_wrap(~month, scale="fixed")+theme_bw()
# ms2#+scale_color_discrete(name="", labels=c('non-DCM','DCM'))

```

## Inter-annual variability.

Here we repeat all plots made above, but with single lines marking interannual variability.

```{r, include=FALSE}
require(reshape2)

tmp_zmaxC<- dcast(tmp_zmax,formula = month~variable, fun.aggregate = mean, na.rm=TRUE)
tmp_zmaxA<-melt(tmp_zmaxC, id.vars=c('month'))

P_years_depth <- ggplot(tmp_zmax, aes(x=month, fill=variable, color=variable)) +
    geom_line(data=tmp_zmaxA,aes(y=value),alpha =0.5, size=3)+
      geom_smooth(aes(y=value, group=interaction(year, variable)),stat = 'summary',
             fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.1))+scale_x_continuous(name='', breaks=c(), labels="")+
  ylab('[m]')+theme_bw()+coord_cartesian(ylim=c(90,0), expand = FALSE)+scale_y_reverse()+
  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal)+facet_grid(.~year)

P_years_depth
```

```{r, include=FALSE}

tmp_sigC<- dcast(tmp_sig,formula = month~variable, fun.aggregate = mean, na.rm=TRUE)
tmp_sigA<-melt(tmp_sigC, id.vars=c('month'))

P_years_sig <-ggplot(tmp_sig, aes(x=month, fill=variable, color=variable)) +
       geom_line(data=tmp_sigA,aes(y=value),alpha =0.5, size=3)+
      geom_smooth(aes(y=value, group=interaction(year, variable)),stat = 'summary',
             fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.1))+scale_x_continuous(name='', breaks=c(), labels="")+
  ylab('[kg/m3]')+theme_bw()+coord_cartesian(ylim=c(10,16))+scale_y_reverse()+
  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal)+facet_grid(.~year)

P_years_sig

```

```{r, include=FALSE}

tmp_partC<- dcast(tmp_part,formula = month~variable, fun.aggregate = mean, na.rm=TRUE)
tmp_partA<-melt(tmp_partC, id.vars=c('month'))

P_years_part <-ggplot(tmp_part, aes(x=month, fill=variable, color=variable)) +
       geom_line(data=tmp_partA,aes(y=value),alpha =0.5, size=3)+
      geom_smooth(aes(y=value, group=interaction(year, variable)),stat = 'summary',
             fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.1))+scale_x_continuous(name='', breaks=c(), labels="")+
  ylab('[%]')+theme_bw()+coord_cartesian(ylim=c(0,100))+
  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal,
                     name='part of tot CHL content', labels=c('above MLD',
                                                              'within a 10m band around DCM',
                                                              'above optical depth'))+
  facet_grid(.~year)

P_years_part

```

```{r, include=FALSE}

tmp_concC<- dcast(tmp_conc,formula = month~variable, fun.aggregate = mean, na.rm=TRUE)
tmp_concA<-melt(tmp_concC, id.vars=c('month'))

P_years_conc <-ggplot(tmp_conc, aes(x=month, fill=variable, color=variable)) +
       geom_line(data=tmp_concA,aes(y=value),alpha =0.5, size=3)+
      geom_smooth(aes(y=value, group=interaction(year, variable)),stat = 'summary',
             fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.1))+scale_x_continuous(name='', breaks=c(), labels="")+
  ylab('[%]')+theme_bw()+coord_cartesian(ylim=c(0,4))+
  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal)+
  facet_grid(.~year)

P_years_conc

```

```{r, include=FALSE}
tmp_corrC<- dcast(tmp_corr,formula = month~variable, fun.aggregate = mean, na.rm=TRUE)
tmp_corrA<-melt(tmp_corrC, id.vars=c('month'))

P_years_corr <-ggplot(tmp_corr, aes(x=month, fill=variable, color=variable)) +
       geom_line(data=tmp_corrA,aes(y=value),alpha =0.5, size=3)+
      geom_smooth(aes(y=value, group=interaction(year, variable)),stat = 'summary',
             fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.1))+scale_x_continuous(name='', breaks=c(), labels="")+
  ylab('[-]')+theme_bw()+coord_cartesian(ylim=c(0,4))+
  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal)+
  facet_grid(.~year)

P_years_corr
```

```{r, fig.height=15, fig.width=10}
grid.arrange(P_years_depth+theme(legend.position = ''),
             P_years_sig+theme(legend.position = '', strip.background = element_blank(),strip.text.x = element_blank()), 
             P_years_part+theme(legend.position = '', strip.background = element_blank(),strip.text.x = element_blank()),
             P_years_conc+theme(legend.position = '', strip.background = element_blank(),strip.text.x = element_blank()),
             P_years_corr+theme(legend.position = '', strip.background = element_blank(),strip.text.x = element_blank()) ,
             ncol=1)

```

## Quick interannual Anomalies and correlations 
```{r}
# compute annual anomalies ? 
Zmulti<-ddply(tmp_zmax, .(month,year,variable), function(d){
    do<-d
    do$anom = d$value - subset(tmp_zmaxA, (month==d$month[1]) & (variable==d$variable[1]))[,'value']
    return(do)
   })
```

```{r}
Smulti<-ddply(tmp_sig, .(month,year,variable), function(d){
    do<-d
    do$anom = d$value - subset(tmp_sigA, (month==d$month[1]) & (variable==d$variable[1]))[,'value']
    return(do)
   })
```

```{r}
Cmulti<-ddply(tmp_conc, .(month,year,variable), function(d){
    do<-d
    do$anom = d$value - subset(tmp_concA, (month==d$month[1]) & (variable==d$variable[1]))[,'value']
    return(do)
   })

Pmulti<-ddply(tmp_part, .(month,year,variable), function(d){
    do<-d
    do$anom = d$value - subset(tmp_partA, (month==d$month[1]) & (variable==d$variable[1]))[,'value']
    return(do)
   })

Xmulti<-ddply(tmp_corr, .(month,year,variable), function(d){
    do<-d
    do$anom = d$value - subset(tmp_corrA, (month==d$month[1]) & (variable==d$variable[1]))[,'value']
    return(do)
   })
```

```{r}
PA_years_depth <- ggplot(Zmulti, aes(x=month, fill=variable, color=variable)) +
    geom_smooth(aes(y=anom, group=interaction(year, variable)),stat = 'summary',
             fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.9))+scale_x_continuous(name='', breaks=c(), labels="")+
#  geom_boxplot(aes(y=anom), alpha=.2)+
  ylab('[m]')+theme_bw()+
  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette='Set1')+facet_grid(variable~year, scales = 'free_y')

PA_years_depth
```

```{r}
PA_years_sig <- ggplot(Smulti, aes(x=month, fill=variable, color=variable)) +
    geom_smooth(aes(y=anom, group=interaction(year, variable)),stat = 'summary',
             fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.9))+scale_x_continuous(name='', breaks=c(), labels="")+
#  geom_boxplot(aes(y=anom), alpha=.2)+
  ylab('[m]')+theme_bw()+
  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette='Set1')+facet_grid(variable~year, scales = 'free_y')

PA_years_sig
```

```{r}
PA_years_conc <- ggplot(Cmulti, aes(x=month, fill=variable, color=variable)) +
    geom_smooth(aes(y=anom, group=interaction(year, variable)),stat = 'summary',
             fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.9))+scale_x_continuous(name='', breaks=c(), labels="")+
#  geom_boxplot(aes(y=anom), alpha=.2)+
  ylab('[m]')+theme_bw()+
  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal)+facet_grid(variable~year, scales = 'free_y')

PA_years_conc
```

```{r}
ZmultiCast <-  dcast(Zmulti,year~variable, value.var = 'anom', fun.aggregate = mean, na.rm=TRUE)
ZmultiCastSD <-  dcast(Zmulti,year~variable, value.var = 'anom', fun.aggregate = sd, na.rm=TRUE)
ZmultiCast<-ZmultiCast[,-which(colnames(ZmultiCast)=='Zdemi')]

SmultiCast <-  dcast(Smulti,year~variable, value.var = 'anom', fun.aggregate = mean, na.rm=TRUE)

PmultiCast <-  dcast(Pmulti,year~variable, value.var = 'anom', fun.aggregate = mean, na.rm=TRUE)

CmultiCast <-  dcast(Cmulti,year~variable, value.var = 'anom', fun.aggregate = mean, na.rm=TRUE)

pdt <- merge(ZmultiCast,SmultiCast,by = c('year'))
pdt <- merge(pdt,PmultiCast,by = c('year'))
pdt <- merge(pdt,CmultiCast,by = c('year'))

require(GGally)
ggpairs(pdt,columns = 3:11 )+theme_bw()
```

```{r}
ggcorr(pdt, method = c("everything", "spearman"), geom = 'circle')
```

```{r}
ZmultiCastM   <-  dcast(Zmulti,year+month~variable, value.var = 'anom', fun.aggregate = mean, na.rm=TRUE)

ZmultiCastMSD <-  dcast(Zmulti,year+month~variable, value.var = 'anom',
                        fun.aggregate = sd, na.rm=TRUE)
ZmultiCastM   <-      ZmultiCastM[,-which(colnames(ZmultiCastM)=='Zdemi')]

SmultiCastM <-  dcast(Smulti,month+year~variable, value.var = 'anom', fun.aggregate = mean, na.rm=TRUE)

PmultiCastM <-  dcast(Pmulti,month+year~variable, value.var = 'anom', fun.aggregate = mean, na.rm=TRUE)

CmultiCastM <-  dcast(Cmulti,month+year~variable, value.var = 'anom', fun.aggregate = mean, na.rm=TRUE)

pdtM <- merge(ZmultiCastM,SmultiCastM,by = c('year','month'))
pdtM <- merge(pdtM,PmultiCastM,by = c('year','month'))
pdtM <- merge(pdtM,CmultiCastM,by = c('year','month'))

ggpairs(pdtM,columns = c(3,4,5,9,10,14,16,17,18) )+theme_bw()
```

```{r}
ggcorr(pdtM, method = c("pairwise.complete.obs", "spearman"), geom = 'circle')

```

```{r}
ggplot(pdt,aes(x=Z90B, y=Zmax, color=factor(year)))+
  geom_point(size=4)+
  geom_point(data=pdtM)+theme_bw()
```

```{r}
ggplot(pdt,aes(x=DCMratio, y=Zmax, color=factor(year)))+
  geom_point( size=4)+
  geom_point(data = pdtM, size=1)+
  theme_bw()
```

```{r}
ggplot(pdt,aes(x=DCMratio, y=sigmaMAX, color=factor(year)))+
  geom_point()+theme_bw()
```

```{r}

ggplot(pdtM,aes(x=sigmaMLD, y=sigmaMAX, shape=factor(year), color=factor(month)))+
  geom_point()+theme_bw()+facet_wrap(~month)

```

# Defining ? and compare ? different type of variability.

How to characterize the Seasonal STD and Annual STD ?

* Spatial STD, would be the time average of the std within month+year bins
* Seasonal STD, would be the seasonal STD of monthly means. 
* Interannual STD, would be interannual STD of monthly averages, averaged over the months ?

```{r}
SDMAT<- function(tab_multi,tab_A,tab_all ) {

  # How to characterize the Seasonal STD and Annual STD ? 
  ##     Spatial STD, would be the time average of the std within month+year bins
  ##    Seasonal STD, would be the seasonal STD of monthly means. 
  ## Interannual STD, would be interannual STD of monthly averages, averaged over the months ?

multiCastMSD <-  dcast(tab_multi,year+month~variable, value.var = 'anom', fun.aggregate = sd, na.rm=TRUE)
mSpatialSD <- dcast(melt(multiCastMSD, id.vars = .(year,month)), variable~.,fun.aggregate = mean, na.rm=TRUE)
colnames(mSpatialSD)<-c('variable','SpatialSD')

mSeasonalSD <- dcast(tab_A, variable~., fun.aggregate = sd, na.rm=TRUE)
colnames(mSeasonalSD)<-c('variable','SeasonalSD')

mC2 <- dcast(tab_all,formula = year+month~variable, fun.aggregate = mean, na.rm=TRUE)
mC3 <- dcast(melt(mC2,id.vars = .(month,year)), formula=variable+month~.,fun.aggregate = sd, na.rm=TRUE )
colnames(mC3)[3]<-"sd"

mAnnualSD <- ddply(mC3, .(variable),summarize,AnnualSD=mean(sd, na.rm=TRUE) )

tt<- merge(mSpatialSD,mSeasonalSD, by="variable")
tt<- merge(tt,mAnnualSD , by="variable")

ttNorm <- ddply(tt, .(variable), mutate, 
                OneSD=mean(c(SpatialSD,SeasonalSD,AnnualSD) ),
                SpatialSDNorm  = SpatialSD/OneSD, 
                SeasonalSDNorm = SeasonalSD/OneSD, 
                AnnualSDNorm   = AnnualSD/OneSD)

return(ttNorm)
}
```

```{r}
sdZ<- SDMAT(Zmulti, tmp_zmaxA, tmp_zmax)

sdS<- SDMAT(Smulti, tmp_sigA , tmp_sig)
sdC<- SDMAT(Cmulti, tmp_concA, tmp_conc)

allsd<-rbind(sdZ, sdS, sdC)

OrderedSDPlot<- function(t,allsd, norm=TRUE){
  if (norm){normstring="Norm"}else{normstring=""}
bibi<- allsd[,c("variable",paste0(t,"SD",normstring))]
bibi$variable<-factor(bibi$variable,
                      levels=bibi$variable[order(bibi[,paste0(t,"SD",normstring)], decreasing = TRUE)], ordered=TRUE)

p<-ggplot(bibi, aes_string(x="variable", y=paste0(t,"SD",normstring)))+
  geom_col(position = 'dodge')+theme_bw()+
  theme(axis.text.x = element_text(angle = 90))
return(p)
}

OrderedSDPlot("Spatial" , allsd, norm=TRUE)
OrderedSDPlot("Annual"  , allsd, norm=TRUE)
OrderedSDPlot("Seasonal", allsd, norm=TRUE)

OrderedSDPlot("Spatial" , sdZ, norm=FALSE)
OrderedSDPlot("Spatial" , sdS, norm=FALSE)

```

```{r}

allsd$variable<-factor(allsd$variable,
                      levels=allsd$variable[order(allsd[,paste0("Spatial","SD","Norm")], decreasing = TRUE)], ordered=TRUE)

ggplot(melt(subset(allsd, select=c("variable","SpatialSDNorm","SeasonalSDNorm","AnnualSDNorm")),
            id.vars=.(variable), variable.name = "Stat"), 
       aes(x=variable, y=value, color=Stat, fill=Stat))+
  geom_col(position = 'dodge')+theme_bw()+
  theme(axis.text.x = element_text(angle = 90))+
  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal)

```

## As introduction before processing

### Depth
Fig. [DEPTH] shows the mean Chla content per boxes of X METERS-width over periods of ten days for
all Chla profiles.
Over-imposed is the spatial median of the 1 and 10% isolumes.
**Would be better if computed on the same time-bins, for simplicity**
Those were obtained by fitting simple exponential decay of PAR to derive both PAR0 and attenuation parameters. 
Only about half (**?**) of the profiles contain PAR measurements.

We observe here :

* Subsurface CHL maximum from ~day 100 to 280.
* Core CHL is:
    * above 10% from 280 to 100 ; 
    * more or less at 1% (or below) from 100 to 150. 
    * in the upper part of the 1% 10% interval from 150 to 180.

**It is important to comment on the relevance of the analysis.**
The width of temporal and vertical bins in this processing have been chosen to ensure that the relative error on displayed mean chl content is below 20% all over the plot (or strip parts if not possible).
This also ensure a meaningfull analysis, despite spatial variability in the horizontal dimension which is integrated in our approach.

![alt text](./mean_chla_Z_context.png)

### SIGMA

Fig. [RHO] follows the same organization than Fig. [DEPTH] using XXX width for the bins. 
Here, we added MLD computed from profiles's T & S following Kara et al. 2008.
In particular, we indicate the range of maximum density of the mixed layer, reached around d50.

We note that :

* CHL remains above MLDmax all year long

* CHL is
    * above MLD from ~320 to 25.
    * across mld in [25 - 100] and [280-315].
    * below MDL from 100-280.

![alt text](./sigma_context.png)

```{r, include=FALSE}

seasonplot<- function(vavar,vname, df=tmp_fitc){
g<-  ggplot(df, aes_string(x="month",y=vavar)) +
    geom_boxplot(aes(group=month), notch = T)+
    geom_smooth(stat = 'summary',
#              fun.data = median_hilow,
              fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95), alpha=0.5)+
  scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab(vname)+theme_bw()

return(g)
}

P_season_tot <- seasonplot("total_chla","Total Chla Content - [mg/m²]")
P_season_tot

P_season_UpMLD <- seasonplot("UpMLD_chla","Chl above MLD - [mg/m²]")
P_season_UpMLD

P_season_DoMLD <- seasonplot("DoMLD_chla","Chl below MLD - [mg/m²]")
P_season_DoMLD

P_season_RaMLD <- seasonplot("RaMLD_chla","part of TotCHL above MLD - [%]")
P_season_RaMLD

P_season_Vis <- seasonplot("visible_chla","Chl above Optical Depth - [mg/m²]")
P_season_Vis

P_season_VisR <- seasonplot("visible_ratio","Part of visible CHL - [%]")
P_season_VisR

P_season_Zmax <- seasonplot("Zmax","Depth of DCM - [m]")
P_season_Zmax+ylim(c(100,0))

```

## Number of profiles and number of DCM profiles.

```{r, fig.height=3}
ggplot(tmp_my, aes(x=month, color=factor(year), y=nprof)) +
    geom_line()+theme_bw()+ylab('number of profiles -[%]')+ 
  scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12))

ggplot(tmp_my, aes(x=month, color=factor(year), y=percentage_dcm)) +
    geom_line()+theme_bw()+ylab('percentage of DCM profiles -[%]')+ 
  scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12)) 
```

This makes much more sense if we integrate 'Other' as DCM profiles.

```{r percentprofiles}

tmp_my2<-ddply(tmp_fitc, .(month,year), summarize,
                nprof = length(dcm_or_not),
                percentage_dcm =  sum(dcm_or_not)/length(dcm_or_not)*100
                )

tmp_myo<-ddply(tmp_fitco, .(month,year), summarize,
                nprof = length(dcm_or_not),
                percentage_dcm =  sum(dcm_or_not)/length(dcm_or_not)*100
                )

ggplot(tmp_my, aes(x=month, color=factor(year), y=percentage_dcm)) +
    geom_line()+theme_bw()+ylab('percentage of DCM profiles -[%]')+ 
  scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12))

ggplot(melt(merge(tmp_my2[,c(1,2,4)],tmp_myo[,c(1,2,4)],by=c('month','year')),id.vars=c('month','year')),
       aes(x=month,  y=value, fill=variable, color=variable)) +
  geom_smooth(stat = 'summary',
#              fun.data = median_hilow,
              fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95), alpha=0.5)+
    #geom_smooth(data=tmp_myo,stat = 'summary',
#              fun.data = median_hilow,,
     #         fun.data = mean_cl_boot,
      #        fun.args = list(conf.int = 0.95), alpha=0.5, fill='blue', color='blue')+
    theme_bw()+ylab('[%]')+ 
  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual,
                     palette=MyPal,
                     name='percentage of DCM profiles',
                     labels=c('excl. "Others"', 'incl. "Others"'))+
  scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12))

# ggplot(tmp_my2, aes(x=month, y=percentage_dcm)) +
#     geom_line()+geom_smooth(aes(y=value),stat = 'summary',
# #              fun.data = median_hilow,
#               fun.data = mean_cl_boot,
#               fun.args = list(conf.int = 0.95), alpha=0.5)+
#   theme_bw()+ylab('percentage of DCM profiles -[%]')+ 
#   scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12))

```

## Optical Community Index

Optical Community Index use the ratio between backscattering and fluorescence to infer changes in the optical properties of plankton cells, and thereby on planktonic groups.

Here, we used the depth horizons given above (and derived for each profile) to distinguisch depth ranges :

* Above the CHl Bulk.
* Within the Bulk
* Below.

A significant difference in this index is observed for the layer above the bulk CHL, with much higer BBP/chl ratio.

The same analysis was attempted considering additional layers (eg. involving a narrow band around DCM), but only surface planktons depicted a 
clear optical community index signature.

```{r bbratio}
loc <- subset(tmp,
              (fluo>0.1) & (!is.na(sigma))& (!is.na(depth)) & (sigma<15.5),
              select = c('depth','month','fluo','sigma','bbp','juld','platform'))

ll<-merge(loc,tmp_fitc,by=c('juld','platform'))

lld <- ddply(ll,.(juld, platform, depth), transform, 
                DepthRegion= ifelse(depth < Z90T, 'Above',
                                    ifelse(depth < Z90B, 'Within Bulk',
                                           'Below')))

g1 <- ggplot(lld,aes(y=bbp/fluo, fill=factor(DepthRegion)))+#cut(sigma,c(9,13.5,14.5,15.5))
  geom_boxplot(notch = TRUE, outlier.size = 0.2)+
  theme_bw()+
  facet_grid(~cut(month.x, breaks = c(0,2,4,6,8,10,12)))+
  scale_x_discrete()+
  scale_fill_brewer(palette = 3,type='seq',name='Layers - [kg/m3]')

print(g1)
```

## Others profiles

All "other" profiles emerges from DCM profiles, and goes back to DCM profiles. 
The succession between shape is hard to read in z coordinates.

In sigma coordinates it to emergence of a secondary bloom on top of the (stable) DCM. 
This never last for more than a month (check) and may be induced by local events such as mesoscale dynamics.

```{r other1}

tmp_fitc$dshape<- paste(tmp_fitc$dcm_or_not,tmp_fitc$shape,sep='_')

tee<-subset(tmp_fitc, select = c("juld","dshape","month","year","platform","dcm_or_not"))

which(tee$dshape=="0_O")

tee[which(tee$dshape=="0_O"),]

ggplot(tee[which(tee$dshape=="0_O")-1,],aes(x=dshape))+geom_bar()+ggtitle("dshape before Others")
ggplot(tee[which(tee$dshape=="0_O")+1,],aes(x=dshape))+geom_bar()+ggtitle("dshape after Others")

ggplot(tee[which(tee$dshape=="0_O")-1,],aes(x=dcm_or_not))+geom_bar()+ggtitle("dshape after Others")

```

```{r other2}
#rr  <- subset(complete_tmp, (platform=="7900591")&(juld>23900)&(juld<24000))
#rr2 <- subset(tmp_fitc, (platform=="7900591")&(juld>23900)&(juld<24000))

##
rr  <- subset(complete_tmp, (platform=="6903240")&(juld>25350)&(juld<25440))
rr2 <- subset(tmp_fitc, (platform=="6903240")&(juld>25350)&(juld<25440))

red<-5

ggplot(rr, aes(y=-depth, x=fluo +(juld-23946)/red, color=factor(juld)))+
  geom_path(size=2)+ylim(c(-100,0))+
  geom_errorbarh(aes(y=-Zmax, xmin=(juld-23946)/red, xmax=1+(juld-23946)/red))+theme_bw()

ggplot(rr, aes(y=-sigma, color=factor(juld)))+
  geom_path(aes(x=fluo+(juld-23946)/red),size=2)+
  geom_errorbarh(data=rr2, aes(y=-sigmaMAX, xmin=(juld-23946)/red, xmax=1+(juld-23946)/red))+theme_bw()

```

```{r other3}
rr  <- subset(complete_tmp, (platform=="7900591")&(juld>23900)&(juld<24000))
rr2 <- subset(tmp_fitc, (platform=="7900591")&(juld>23900)&(juld<24000))

red<-5

ggplot(rr, aes(y=-depth, x=fluo +(juld-23946)/red, color=factor(juld)))+
  geom_path(size=2)+ylim(c(-100,0))+
  geom_errorbarh(aes(y=-Zmax, xmin=(juld-23946)/red, xmax=1+(juld-23946)/red))+theme_bw()

ggplot(rr, aes(y=-sigma, color=factor(juld)))+
  geom_path(aes(x=fluo+(juld-23946)/red),size=2)+
  geom_errorbarh(data=rr2, aes(y=-sigmaMAX, xmin=(juld-23946)/red, xmax=1+(juld-23946)/red))+theme_bw()

```

```{r}
knitr::knit_exit()
```

### 2020-07-07 article_figures_ARTHUR_CAPET.Rmd
update Markdowns

--- 2020-07-07 dcm_investigation_clean_Results_AC.Rmd
@@
 title: "DCM_investigation"
-author: "MAST"
+author: "Capet Arthur"
 date: "February 20, 2020"

### 2020-07-07 article_figures_FLORIAN_RICOUR.Rmd
update Markdowns

--- 2020-07-07 article_figures.Rmd
@@
 library(gridExtra)
-#library(tidyverse)
 library(lubridate)
@@
 library(reshape2)
-#library(ggforce)
 library(gsw)
@@
 ```{r data, echo=T}
-# FUCK IT FUCK THIS ARTICLE AND FUCK THE BLACK SEA ÇA ME GONFLE
-load(file='dataJune26_2020.RData')
-#load(file='../dataJune26_2020.RData')
+load(file='DataPaper.RData')
 ```
@@
 ```{r chla_correction_functions, include = F, results=F}
-#1 Extract data from any variable available in the float data files
-ExtractVar <- function(Var,FloatInfo){
 
-  with(FloatInfo,{
-    # This function should return a dataframe for the chosen variable with value, qc, iprofile and ilevel
-    lvar             <- ncvar_get(ncfile,Var)
-    lvar_qc          <- ncvar_get(ncfile,paste0(Var,"_QC"))
-    lvar_qctab       <- llply(lvar_qc,function(qcstring){
-      as.numeric(unlist(strsplit(qcstring,split="")))
-    })
-    lvar_qctab <- do.call(cbind,lvar_qctab)
-
-    lvar_dir       <- ncvar_get(ncfile,"DIRECTION")
-    lvar_direction <- llply(lvar_dir,function(dirstring){
-      strsplit(dirstring,split="")
-    })
-    lvar_direction <- unlist(lvar_direction)
-    # making dataframes, removing the NANs  
-    alevels <- 1:N_LEVELS
-    d <- ldply(as.list(1:N_PROF),function(iprof){
-      indexes <- !(is.na(lvar[,iprof])|is.na(lvar[,iprof]))
-      if(sum(indexes) == 0){
-        return (data.frame())
-      }
-
-      data.frame(value    = lvar[indexes,iprof],
-                 qc       = as.integer(lvar_qctab[indexes,iprof]),
-                 alevel   = alevels[indexes],
-                 depth    = pres[indexes,iprof],
-                 dir      = lvar_direction[iprof],
-                 aprofile = iprof,
-                 variable = Var)
-    })
-
-    d$juld <- juld[d$aprofile]
-    d$lon  <- lon[d$aprofile]
-    d$lat  <- lat[d$aprofile]
-
-    return(d=d)
-  })
-}  
-#2 five-points median filter
-mmed <- function(x,n=5){runmed(x,n)}
-#3 Determination of day/night profiles
-DayOrNight <- function(dataframe){
-
-  d <- ldply(as.list(unique(dataframe$juld)), function(juld){
-
-    #print(juld)
-
-    origin <- ymd_hms("1950-01-01 00:00:00") # julian day origin for the Argo program
-
-    # get temporary profile and metadata
-    tmp <- dataframe[dataframe$juld == juld,]
-    lat <- tmp$lat[1]
-    lon <- tmp$lon[1]
-    n <- length(tmp$depth) #number of points in the profile
-
-    # determine day or night
-    tmp_juld <- origin + juld * 3600 * 24 #conversion of juld in working day and hour
-    date <- format(tmp_juld, tz="Europe/Sofia", usetz=TRUE)
-    date2 <- as.Date(as.POSIXct(tmp_juld, 'Europe/Sofia')) # convert juld into a a "Date" object
-
-    hour <- format(as.POSIXct(strftime(tmp_juld,"%Y-%m-%d %H:%M:%S",tz="Europe/Sofia", usetz = T)),format = "%H")
-    data <- data.frame(date = date2, lat = lat, lon = lon) # create a dataframe for the function getSunlightTimes
-    sun_cycle <- getSunlightTimes(data = data, keep = c("sunset", "sunrise"), tz = "Europe/Sofia")# get the sunset and sunrise hours
-
-    # local sunrise/sunset hours
-    hour_sunrise <- as.numeric(format(sun_cycle$sunrise, "%H"))
-    hour_sunset <- as.numeric(format(sun_cycle$sunset, "%H"))
-
-    if(is.na(hour_sunrise)){ # needed for profiles without latitude/longitude
-      sun <- "NA"
-    }else if(as.numeric(hour) < hour_sunset & as.numeric(hour) > hour_sunrise){
-      sun <- "day"
-    }else{
-      sun <- "night"
-    }
-
-    date <- rep(date, times = n)
-    sun <- rep(sun, times = n)
-
-    data.frame(date = date, day_night = sun)
-
-  })
-
-  return(d)
-}
 #4 Function to reinitialize dataframes after cleaning (row numbers, new IDs)
@@
 }
-#5 Function to normalize data 
-normalize <- function(data){
-  data <- (data - min(data, na.rm = T))/(max(data, na.rm = T) - min(data, na.rm = T))
-}
+
 ########
@@
 
-  print(file)
+  #print(file)
 
@@
 
-  if (file == "7900591_Mprof.nc" | file == "7900592_Mprof.nc"){ #change M for merged or S for synthetic profiles
+  if (file == "7900591_Mprof.nc" | file == "7900592_Mprof.nc"){ 
     cdomdf <- as.data.frame(rep(NA, length(chladf$value)))
@@
 ```{r chla_correction_filter, include = F, results=F}
+
 #REMOVE BAD DATA
@@
 data <- data[-(which(data$depth < 0)),]
+
 #Day of deployment
 data <- data[data$DOY == 88 & data$year == 2018,]
+
 smoothed_fluo <- ldply(as.list(unique(data$juld)), function(i){
@@
 })
+
 smoothed_cdom <- ldply(as.list(unique(data$juld)), function(i){
@@
 })
+
 #REPLACE FLUO WITH SMOOTHED FLUO & CDOM
@@
 ```{r chla_correction_density, include = F, results=F}
+
 # compute density profiles
@@
              lat   = tempdf$lat,
-             #day      = month.day.year(tempdf$juld,c(1,1,1950))$day,
              month = month.day.year(tempdf$juld,c(1,1,1950))$month,
@@
 density_profiles <- transform(density_profiles,id=as.numeric(factor(juld)))
+
 #MLD computation
@@
   }else{
-    sigmaMaxMLD <- mean(tmp$sigma[which(tmp$depth == MLD)], na.rm =T) #check this, pq max mld? #####################################################################
+    sigmaMaxMLD <- mean(tmp$sigma[which(tmp$depth == MLD)], na.rm =T) 
   }
@@
 })
+
 # manual adjust because density inversion
@@
 ```{r chla_correction_roesler, include = F, results=F}
+
 # add a column to the 'profiles' dataframe with OLD_CHLA (will save the uncorrected chla, can be useful for some plots)
 data$raw_fluo <- data$fluo
+
 # Add Roesler Correction
@@
 data$raw_roesler <- data$fluo
-#EACH PROFILES HAS BEEN VALIDATED SO FAR ==> CALIBRATION EXERCISE STARTS NOW
-#LET'S DO IT ONLY FOR THE DEEP PROFILE
-#FDOM-based method (Xing et al. 2017)
-#keep only the validation profile (i.e. id = 1)
+
+# EACH PROFILES HAS BEEN VALIDATED SO FAR ==> CALIBRATION EXERCISE STARTS NOW
+# LET'S DO IT ONLY FOR THE DEEP PROFILE
+# FDOM-based method (Xing et al. 2017)
+# keep only the validation profile 
 data <- data[data$id == 3,]
@@
 data <- transform(data,id=as.numeric(factor(juld)))
+
 #FDOM-BASED CORRECTION AND MINIMUM-OFFSET CORRECTION
@@
 })
-#USE THE FDOM
+
+#USE THE FDOM-corrected data
 data[,3] <- FDOM_OR_MINIMUM_OFFSET_CORRECTION$fluo_cor
@@
 ```{r chla_correction_quenching, include = F, results=F}
-#QUENCHING CORRECTION
-#NOTE : This function was given to me by Marin Cornec (PhD Student at the LOV)
+
+# QUENCHING CORRECTION
+# NOTE : This function was given to me by Marin Cornec (PhD Student at the LOV)
 quenching_correction <- function(fluo,depth,MLD) {
@@
 }
+
 #NPQ correction adapted to daily and nightly (DN) profiles
@@
 data$fluo <- NPQ_correction_DN_adapted$fluo_NPQ # all correction here except the "positivation step" : fluo here = RAW + ROESLER + FDOM + NPQ
-#REPLACE < 0 of CHLA by 0 (fair assumption.. ?) ===> MUST BE DONE AFTER THE FDOM CORRECTION (in that case we need to RENORMALIZE CHLA DATA IN PROFILES)
+
+# REPLACE < 0 of CHLA by 0 (after all corrections)
 # data$fluo[which(data$fluo < 0)] <- 0
@@
 
-```{r RMSE COMPUTATION}
-
-# COMPUTE STATS BELOW
-
-depth_hplc <- c(0,30,50,70,90,100,140,200,250,500,750,1000)
-chla_hplc <- c(0.6111,0.6433,0.3090,0.0675,0.0229,0.0168,0.012,0.0032,
-               0.0035, 0.0023, 0.0039, 0.0042)
-hplc <- as.data.frame(cbind(depth_hplc, chla_hplc))
-
-indexdepth <- vector()
-
-for (i in 1:length(hplc$chla)){
-  indexdepth[i] <- which.min(abs(data$depth - hplc$depth_hplc[i]))
-}
-
-# RMSE DEEP LAYER FDOM CORRECTED PROFILE
-index <- which(hplc$depth_hplc > data_info$depthmin & hplc$depth_hplc < data_info$bottomdepth)
-deep_layer <- indexdepth[index]
-rmse_deep_layer <- sqrt(sum((hplc$chla_hplc[index] - data$raw_roesler_fdom[deep_layer])^2)/length(hplc$depth_hplc[index]))
-
-# SAME FOR THE RAW PROFILE
-rmse_deep_layer_old <- sqrt(sum((hplc$chla_hplc[index] - data$raw_fluo[deep_layer])^2)/length(hplc$depth_hplc[index]))
-
-# RMSE SURFACE LAYER
-index <- which(hplc$depth_hplc < data_info$depthmin & hplc$depth_hplc < data_info$bottomdepth)
-surface_layer <- indexdepth[index]
-rmse_surface_layer <- sqrt(sum((hplc$chla_hplc[index] - data$raw_roesler_fdom[surface_layer])^2)/length(hplc$depth_hplc[index]))
-
-# RMSE SURFACE LAYER with NPQ
-index <- which(hplc$depth_hplc < data_info$depthmin & hplc$depth_hplc < data_info$bottomdepth)
-surface_layer <- indexdepth[index]
-rmse_surface_layer <- sqrt(sum((hplc$chla_hplc[index] - data$fluo[surface_layer])^2)/length(hplc$depth_hplc[index]))
-
-# SAME FOR THE RAW PROFILE
-rmse_surface_layer_old <- sqrt(sum((hplc$chla_hplc[index] - data$raw_fluo[surface_layer])^2)/length(hplc$depth_hplc[index]))
-
-## ALL PROFILES RMSE BLABLABLA ---
-
-index <- 1:12
-surface_layer <- indexdepth[index]
-#fdom
-rmse_fdom <- sqrt(sum((hplc$chla_hplc[index] - data$raw_roesler_fdom[surface_layer])^2)/length(hplc$depth_hplc[index]))
-
-#fdom+npq
-rmse_npq <- sqrt(sum((hplc$chla_hplc[index] - data$fluo[surface_layer])^2)/length(hplc$depth_hplc[index]))
-
-#raw
-rmse_raw <- sqrt(sum((hplc$chla_hplc[index] - data$raw_fluo[surface_layer])^2)/length(hplc$depth_hplc[index]))
-
-```
-
 ```{r correction_fig, include = T}
-day <- doxy$juld[236208]
-oxy <- doxy[doxy$juld == day,] # closest oxy profile (in time) .. (it's the good float at least ..)
 #HPLC DATA FROM DEPLOYMENT
@@
 ```{r profile_examples}
-# # i = 7: jolie sigmoide
-# # GS : 12, 103 ! ==> aussi voir 154, 156
-# # G : 111 143 178 183 331 487 542 730 830 , TRÈS souvent des doubles pics ..
-# # GE : 119, 195
+
 flabels <- c("Gaussian (G)","Sigmoid (S)","Gaussian-Sigmoid (GS)","Gaussian-Exponential (GE)")
 profID  <- c(111,7,12,195)
-
-# require(plyr)
-# pl<-llply(seq(length(flabels)), function(i){
-#   fit_curve(profID[i])+ggtitle(flabels[i])  
-# })
-# do.call(grid.arrange, pl)
 

### 2020-07-28 article_figures_FLORIAN_RICOUR.Rmd
update fig linewidth

@@
 
-deployment <- ggplot(data, aes(x = fluo, y = depth, colour = "ROESLER + FDOM + NPQ")) + geom_path(size = 0.5) +
-  scale_y_reverse() + geom_path(data = data, aes(x = raw_roesler_fdom, y = depth, colour = "ROESLER + FDOM")) +
+deployment <- ggplot(data, aes(x = fluo, y = depth, colour = "ROESLER + FDOM + NPQ"), lwd = 1.5) + geom_path(lwd = 1.5) +
+  scale_y_reverse() + geom_path(data = data, aes(x = raw_roesler_fdom, y = depth, colour = "ROESLER + FDOM"), lwd = 1.5) +
   xlab(expression(Chlorophyll~a~(mg/m^3)))+ ylab("Depth [m]") +
@@
   annotate("text", x = .8, y = data_info$depthmin[1]-20, label = "CHLA MINIMUM") +
-  geom_path(data = data, aes(x = raw_fluo, y = depth, colour = "None (RAW)")) + 
-  geom_path(data = data, aes(x = raw_roesler, y = depth, colour = "ROESLER")) + 
+  geom_path(data = data, aes(x = raw_fluo, y = depth, colour = "None"), lwd = 1.5) + 
+  geom_path(data = data, aes(x = raw_roesler, y = depth, colour = "ROESLER"), lwd = 1.5) + 
   geom_point(data = df, aes(x = cdom/10, y = depth), colour = "black", size = .5) + 
@@
 
-zoom_deployment <- ggplot(data, aes(x = fluo, y = depth, colour = "ROESLER + FDOM + NPQ")) + geom_path(size = 0.5) +
-  scale_y_reverse(limits = c(100,0)) + geom_path(data = data, aes(x = raw_roesler_fdom, y = depth, colour = "ROESLER + FDOM")) +
+zoom_deployment <- ggplot(data, aes(x = fluo, y = depth, colour = "ROESLER + FDOM + NPQ")) + geom_path(lwd = 1.5) +
+  scale_y_reverse(limits = c(100,0)) + geom_path(data = data, aes(x = raw_roesler_fdom, y = depth, colour = "ROESLER + FDOM"), lwd = 1.5) +
   xlab(expression(Chlorophyll~a~(mg/m^3)))+ ylab("Depth [m]") +
-  geom_path(data = data, aes(x = raw_fluo, y = depth, colour = "None (RAW)")) + 
-  geom_path(data = data, aes(x = raw_roesler, y = depth, colour = "ROESLER")) + 
+  geom_path(data = data, aes(x = raw_fluo, y = depth, colour = "None"), lwd = 1.5) + 
+  geom_path(data = data, aes(x = raw_roesler, y = depth, colour = "ROESLER"), lwd = 1.5) + 
   geom_point(data=hplc, aes(y = depth_hplc, x = chla_hplc), colour = "red", size = 2, shape = 15)  + 

### 2020-07-29 DataExtractionCleaning.R
clean and update

@@ -634,7 +634,7 @@ profiles$fluo[which(profiles$fluo < 0)] <- 0
 init_profiles <- profiles
 init_density_profiles <- filter(density_profiles, juld %in% profiles$juld)
 
-# keep MLD data for 2014-2018 before the fit
+# keep MLD data before the fit
 init_MLD <- filter(MLDdf, juld %in% profiles$juld)
 
 ################################################

### 2020-07-29 article_figures_FLORIAN_RICOUR.Rmd
clean and update

@@
 
-# EACH PROFILES HAS BEEN VALIDATED SO FAR ==> CALIBRATION EXERCISE STARTS NOW
-# LET'S DO IT ONLY FOR THE DEEP PROFILE
-# FDOM-based method (Xing et al. 2017)
-# keep only the validation profile 
+# EACH PROFILES HAS BEEN VALIDATED SO FAR
 data <- data[data$id == 3,]

### 2020-07-29 article_figure_ARTHUR_CAPET.Rmd
clean and update

--- 2020-07-07 dcm_investigation_clean_Results_AC.Rmd
@@
 library(plyr)
-#library(plotly)
 library(grid)
@@
 ```{r data}
-# Load a bunch of data previously computed
-# load(file='../wetransfer-fcfe00/data.RData')
-
-load(file='../dataJune2020.RData')
-
-freshstart = FALSE
-```
-
-# Validation HPLC ...
-
-# Morphology of the Black Sea Deep Chlorophyll Maximum
-
-The vertical CHl distributions is first explored here by classifying profiles in terms of analytical shape,
-in order to identify a subset of profiles presenting DCM signatures.
-Despite the use of an adjusted R-squared metric to classify the Chla profiles, it seems that the plasticity of the sigmoid-gaussian formulation provides a best fit in most cases, both for DCMs (Fig.
-3a) and non-DCMs (Fig.
-3b) profiles.
-
-Non-DCM profiles dominates from October to April.
-No cases of exponential profiles are observed. 
-The pure sigmoid profiles, denoting a well-homogenized plantkonic biomass in the surface
-layer, happen from October to April with a clear peak in December/January consistent with the known dynamic of the mixed
-layer depth in the Black Sea (Capet et al., 2014).
-
-DCMs profiles starts to dominate from April to September.
-First DCM profiles are recognized as GS and partly GE. 
-Only from July, some profiles depicts a pure gaussian shape, denoting a depletion of surface Chla content.
-* In principle corresponds to periods where subsurface CHL content is max?*
-
-```{r nicehistogram}
+# Load data previously computed
+load(file='./DataPaper.RData')
+
+freshstart <- T
+```
+
+# Evolution of the Black Sea Deep Chlorophyll Maximum
+
+```{r Fig3}
 # compute stats per months
-tmp_fit <- filter(init_fit, year %in% c(2014:2019)) # remove 2014 
+tmp_fit <- filter(init_fit, year %in% c(2014:2019)) 
 stats_month <- ddply(tmp_fit, ~month, summarize,
@@
 dcm <- filter(tmp_fit, juld %in% unique(fit$juld))
-
-# rename shapes in 'dcm'
-# PAS COMPRIS POURQUOI J'AI GALÉRÉ AUTANT
-#dcm$shape <- gsub('GS', 'GS_true', dcm$shape) # M'ONT BIEN CASSÉ LES *** LES LEVELS (merci https://stackoverflow.com/questions/21187603/replace-characters-from-a-column-of-a-data-frame-r)
 
@@
 
-stupid <- ddply(tmp_fit, ~month~shape, summarize,
+tmp_stu <- ddply(tmp_fit, ~month~shape, summarize,
                 count = length(unique(juld)),
@@
 
-#stupid2
+# continue
 for (i in c(1:12)){
-  stupid[stupid$month == i,]$count <- stupid[stupid$month == i,]$count/stats_month$profiles[i]
-  stupid[stupid$month == i,]$count2 <- stats_month$profiles[i]
-}
-
-# define colours (avec le "O" shape entre les deux Arthur?)
-# https://www.thinkingondata.com/something-about-viridis-library/
-# 
-#myColors <- c("#440154FF", "#404788FF", "#287D8EFF", "#3CBB75FF","#DCE319FF") #based on viridis (https://www.thinkingondata.com/something-about-viridis-library/)
-# https://bhaskarvk.github.io/colormap/
+  tmp_stu[tmp_stu$month == i,]$count <- tmp_stu[tmp_stu$month == i,]$count/stats_month$profiles[i]
+  tmp_stu[tmp_stu$month == i,]$count2 <- stats_month$profiles[i]
+}
+
+# define colours 
 myColors <- c("#13306DFF", "#6B4596FF", "#403891FF", "#042333FF", "#A65C85FF", "#EB8055FF", "#F9B641FF", "#E8FA5BFF")
-#myColors <- brewer.pal(5,"Set1") # can be modified for other colours
 names(myColors) <- c("G", "GE", "GS", "S", "O", "G_true", "GS_true", "GE_true") #https://stackoverflow.com/questions/6919025/how-to-assign-colors-to-categorical-variables-in-ggplot2-that-have-stable-mappin
@@
 
-ggplot(stupid, aes(x = month, fill = shape, y = count)) +
+ggplot(tmp_stu, aes(x = month, fill = shape, y = count)) +
   geom_bar(stat='identity') +
@@
 ```{r Processing, error=FALSE, warning=FALSE, echo=FALSE, message=FALSE, results='hide', include=FALSE, eval=TRUE}
+
 # Prepare data for Temporal Series
@@
 
-#### This is making trouble .; probably because depth of light and other measurement are different.. 
-#complete_tmp_par <- merge(complete_tmp,
-#                          initPAR[,c('depth','juld','par','platform')],
-#                          by=c('depth','juld','platform'),
-#                          all.x=TRUE)
-
 optical_depth <- c(6,6,6,7.5,7,7,7.5,9,8,6.5,6,6) #1/k = optical depth ==> we have a value for each month
@@
 ```{r Functions, error=FALSE, warning=FALSE, echo=FALSE, message=FALSE, results='hide', include=FALSE, eval=TRUE}
+
 ############
@@
 
-# Attempt for uniroot.. not working for now. 
 content_z<-function(z, depth, fluo,total){
@@
 
-# Stupid function to find the lower boundary of core X% CHL content.
+# Simple function to find the lower boundary of core X% CHL content.
 depth90B<-function(depth, fluo, total,p=.9){
@@
 
-# PAR2bands <- function(profile){
-#   # Intended for Casted DF
-#   if (FilterForPAR(profile)){
-#     out <-try_default({
-#       m   <-nls(PAR ~ Att_2band(depth,PAR0,ks0,kl0),
-#           data = profile,
-#           start = p2b_start, 
-#           lower = p2b_lower,
-#           upper = p2b_upper,
-#           algorithm = "port", 
-#           control = list(maxiter= 1000)
-#           )
-#       return(as.data.frame(t(coef(m))))},
-#     Out_Default)
-#   }else{
-#     out <- Out_Default
-#   }
-#   return(out)
-# }
-
-# depth90b<-function(depth, fluo, total){
-#   # return the depth over which integration should be doe to capture 95 % of the total CHL content.
-#   print(total)
-#   print(content_z(20, depth=depth, fluo=fluo, total=total))
-#     print(content_z(30, depth=depth, fluo=fluo, total=total))
-#       print(content_z(40, depth=depth, fluo=fluo, total=total))
-#   z90=uniroot(content_z,c(10,200), depth=depth, fluo=fluo, total=total,tol = 1)
-#   print(z90)
-#   return(z90)
-# }
 ```
@@
 if (freshstart){
-# !!!!! Carefull here, this is much cleaner that the following commented line
-# which does not ensure that the order corresponds, only hte number of elements !!!!!!
-# Took me a while to track why this was causing different results !! 
 tmp_fitc<-merge(tmp_fit ,integrated_diags, by = c('juld','platform'))
@@
 tmp_fitc<-merge(tmp_fitc ,integrated_diags_par, by = c('juld','platform'), all.x = TRUE)
-#tmp_fit$total_chla_content <- total_chla_content$total_chla
-
-# remove 2014 .. (not enough data) or not.
+
 tmp_fitc   <- tmp_fitc[tmp_fit$year %in% c(2014:2019),]
@@
 ```{r}
-# Just to save time when kniotting multiple times. 
-if (freshstart) {
- save.image(file='./CleanResultsData.RData') 
-}else{
-load(file='./CleanResultsData.RData')
-}
-```
-
-To avoid overinterpreting in winter, we remove for DCM characs, the months for which percentage DCM is below 50.
-So diagnostics based on DCM criterion are cancelled for those periods for which DCM dynamics is not representative.
-```{r}
 
@@
 tmp_fitco[which((tmp_fitco$month<4)|(tmp_fitco$month>10)),c('Zmax','sigmaMAX','DCMratio','chla_dcm')]<-NA
-#tmp_fitco[which((tmp_fitco$month<4)|(tmp_fitco$month>10)),c('Zmax','sigmaMAX','DCMratio')]<-NA
-```
-
-# Back Scattering Validation of the DCM -> DPM relation
-
-I want to use backscattering values, to comment on the fact that DCM correspond to a maximum in DBM, or relates on to another in some ways.
-
-## First Approach.
-
-* I'll use all DCM profiles
-* I'll normalize them using 
-    * CHL@DCM to normalize chl
-    * z@DCM to normalize the vertical scale. 
-* Plot this, plot bbp on the same normalized axis.
+```
+
+# Back Scattering Validation of the DCM
 
@@
 dbdf<-ddply(dbdf,.(platform, juld),mutate,
-            bbpmax= max(bbp[depth_norm<1.5]),
+            bbpmax= mean(bbp[depth_norm<1.2], na.rm=TRUE),
             bbp_norm1 = bbp/bbpmax,
@@
 
-dbdf$sigma_norm_layers <- cut(dbdf$sigma_norm,seq(0.05,3.05,.1))
-dbdf$depth_norm_layers <- cut(dbdf$depth_norm,seq(0.05,3.05,.1))
+dbdf$sigma_norm_layers <- cut(dbdf$sigma_norm,seq(0.05,3.05,.05))
+dbdf$depth_norm_layers <- cut(dbdf$depth_norm,seq(0.05,3.05,.05))
 ```
@@
       geom_boxplot(aes(group=depth_norm_layers), outlier.size=0.5)+
-  theme_bw()+coord_flip(xlim = c(0,2), ylim=c(0,1.5))+
+  theme_bw()+coord_flip(xlim = c(0,2), ylim=c(0,2))+
   facet_grid(monthn~variable)+
@@
 
-```{r bigplotbackscat}
+```{r Fig9, fig.width=8, fig.height=6}
 grid.arrange(bigplot1+scale_x_reverse(),
@@
 
-## Second Approach
-
-Using DBM from analytical fits
-
-```{r}
-bothfit<-merge(fit, fit_BBP, by=c("platform", "juld","month",'lon','lat'))
-
-bothfit$monthn<-factor(bothfit$month, labels = month.abb[unique(bothfit$month)])
-
-ggplot(subset(bothfit, (dcm_or_not==1) &
-                (r2adj.y>0.95)&
-                grepl('G',bothfit$shape.y)&
-                (month %in% seq(3,10))),
-       aes(x=Zmax.x, y=Zmax.y, color=factor(month)))+
-  geom_point()+theme_bw()+ylim(c(-10,60))+xlim(c(-10,60))+geom_abline(slope = 1,intercept = 0)+
-  facet_wrap(~monthn)+xlab(TeX('$z_{DCM}'))+ylab(TeX('$z_{DBM}'))
-```
-
 # Depth horizons
 
-!!! Probably have to add lights characteristics !!!
-
-Let's consider $Z_{1/2}$ as indicative of the lower boundary of the depth area with signicant CHL concentration. 
-Indeed, Sigmoid gaussian profiles are dominant through the years, with a long tail covering insignifiant CHL values over a large depth range.
-
-**C'est clair ça ? **
-
-The deeper winter MLD bounds the productive area in winter. 
-Starting with the stratification onset in March, when MLD goes up, the chloropyll content penetrates deeper, with a rapid creation of DCM.
-$Z_{DCM}$ starts at $Z_{1/2}$ (April), dissociate from $Z_{1/2}$ in June, and can't **(?)** be distinguished from $Z_{1/2}$ from July on.
-
-Very low variabiliity of summer MLD, but larger in winter. 
-Most probably winter MLD scatter is associated with spatial variability **(can be answered, I mean in regards with interannual variability)**.
-
-```{r depth}
+```{r Fig5}
 require(reshape2)
@@
                        labels=list(TeX('$z_{MLD}$'),
-                                TeX('$r_{DCM}$'),
+                                TeX('$z_{DCM}$'),
                                 TeX('$z_{low}$'),
@@
 
-Density framework shows less spatial variability, and more stable seasonal evolution.
-
-The deepest winter MLD sets pycnal layer of Z_1/2, which remains stable from February to September.
-From may to june, a DCM forms and migrate to higher layers.
-
-Unlike the previous plot, the pycnal coordinates allow to dissociate DCM from June to September.
-This is indicative of pycnal or mixing forces ruling the location of the DCM, rather than restrictevely light conditions wich tend to be more related to the depth [m] scale.
-
-Obviously nutrient content follows isopycnal layers.
-Konovalov (2006) locates the nitrate nitracline at 15.5 kg/m3.
-
-Between August and October, it seems the lower part of CHL limited and Sigma_1/2 rejoins Sigma_max. Light limitation by a well formed DCM ? 
-Indeed, it's in August that the percentage of CHL around DCM is highest, so that CHL density in the DCM zone is the thickest. 
-**Something strange with MLD .. How many defined MLD in summers ? Is there less ? is that what explain low variability in summer?**
-**I changed the definition of sigma MLD above, but ... dont get it.**
-
-```{r sigma}
+```{r Fig6}
 tmp_sig1 <- subset(tmp_fitco, select = c('month','sigmaMLD','sigmaMAX','sigmalow','sigma90B','sigma90T','sigmaiso1' ,'dcm_or_not','year','shape'))
@@
 tmp_sig1$sigmaMAX[tmp_sig1$Zmax>200]<-NA
-#tmp_sig1$Zdemi[tmp_sig1$shape %in% c("O","GE","G")]<-NA
 
@@
 
-In Summer, about 50-60 % (up to 75%) of the total chlorophyll content is located in a narrow 20m band around the DCM. 
-This DCM is located between 30-40m, which is about 4 times the optical depth estimated as the inverse of PAR attenuation profiles.
-
-The question is how much of this is missed by satellite ? 
-From May to August, less than 20% of the total Chl content is above the MLD (~)
-```{r parts}
+```{r Fig8}
 require(reshape2)
@@
 ```
+
 ## Concentrations
 
-Here we compare CHL concentrations at DCM and surface to the average Chl Content.
-
-Average CLH content is considered by dividing the vertically integrated chla content with a constant scaling depth of 40m, 
-chosen as the mean of Z 1/2, as discussed above.
-
-Except from the hint of a bloom in March, the total CHL content does not
-indicate very strong seasonal variations.
-
-Instead, the surface chlorophyll content does decrease by a factor two from April to September, while chl concentrations at DCM are above average.
-
-We note the increase in August, that was suggested to limit CHL at depth in the previous sections (ref{sec_season_sigma}).
-
-```{r concentrations}
+```{r Fig7}
 require(reshape2)
@@
 
-# Satellite confrontation
-
-L4 products obtained from CMEMS.
-Match-up extracted from CMEMS satellite products at Argo Locations.
-
-Decent correlation (0.59, p<1e-13) between satellite CHL and surface CHL from Argo profilers.
-Clear multiplicative bias of 2.1 (larger Argo values).
-
-Here we want to discuss in relative terms about the location of the bulk of Chl content, and how the seasonal cycle of Chloropyll can be grasped by satellite. 
-In the following, we thus multiply satellite products by a corrective factor of two, in order to compare seasonal evolutions on a similar scale. 
-We do not have at our disposal, sufficient in-situ HPLC data to conclude on the absolute value of CHL here, but the relative context is sufficient for our argument.
-
-A very close relationship is observed between Argo and satellite products at colocation points (nothwithstanding the multiplicative bias).
-The Argo curve of surface CHl concetration on this figure, is also in agreement with the seasonal behavior described above considering ARGo profiles over a larger period.
-
-**Attention here, we need to discuss Quenching correction, and the fact that Argo profiles do not extend to surface**
-
-```{r Satellite}
-
-source("AddSat.R")
-tmp2019 <- subset(tmp_fit,year==2019)
-Sat_tmp2019 <- AddSat(tmp2019)
-
-tmp_sa1        <- subset(Sat_tmp2019, select = c('satCHL','chla_surf','month','year'))
-tmp_sa1$satCHL <- tmp_sa1$satCHL
-tmp_sa         <- melt(tmp_sa1, id.vars=c('month','year'))
-
-ggplot(tmp_sa,aes(x=month, fill=variable, color=variable))+
-geom_smooth(aes(y=value),stat = 'summary',
-#              fun.data = median_hilow,
-              fun.data = mean_cl_boot,
-              fun.args = list(conf.int = 0.95), alpha=0.5)+
-        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12)) +
-    geom_boxplot(aes(y=value, group=interaction(month,variable)), alpha=0.2)+
-  theme(axis.text.x = element_text(angle = 90, hjust = 1))+theme_bw()+ylab('[mg/m3]')+
-  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal, name="Surface Chla", labels=c("Satellite","Argo"))
-
-```
-
-## Satellite Comparison
-
-```{r Satellite2}
-# Used for coef on next plots.
-#-summary(lm(satCHL~chla_surf, Sat_tmp2019))
-
-ggplot(Sat_tmp2019,aes(x=chla_surf,y=satCHL,color=factor(month)))+
-  geom_point()+theme_bw()+
-  #geom_smooth(method='lm')+
-  xlim(c(0,1.5))+ylim(c(0,1.5))+
-  geom_abline(intercept = 0,slope = 1,size=2)+
-  #geom_abline(intercept = 0,slope = .5,linetype=3)+
-  xlab("Argo - [mg/m3]")+ylab("Satellite - [mg/m3]")+
-  scale_color_discrete(name='', labels=month.abb)
-```
-
-```{r Satellite2_coefs}
-cor.test(Sat_tmp2019$satCHL,Sat_tmp2019$chla_surf)
-
-rmserr(Sat_tmp2019$chla_surf,Sat_tmp2019$satCHL)
-```
-
-# Discussion
-
-## "Correction of Satellite value"
-A DCM dynamics dominates from April to October.
-Contains about 50-70 % of total chl content.
-Due to this seasonal change in the vertical distribution of Chlorophyll, considering only surface information (as for instance provided by satellite) might lead to underestimate summer total chl content by a factor of up to 3.5 in august.
-
-To estimate this factor, we divided here the average CHL content as defined in Sect. ... (total content/ divided by 40m) by surface content as provided by Argo Floats.
-
-```{r}
-tmp_ra2 <- tmp_conc1
-
-tmp_ra2$surfcorrection <- tmp_ra2$total_chla/tmp_ra2$chla_surf
-
-tmp_corr <- melt(subset(tmp_ra2,select=c('month','year','surfcorrection')), id.vars=c('month','year'))
-
-ggplot(tmp_corr, aes(x=month, fill=variable, color=variable)) +
-    geom_smooth(aes(y=value),stat = 'summary',
-#              fun.data = median_hilow,
-              fun.data = mean_cl_boot,
-              fun.args = list(conf.int = 0.95), alpha=0.5)+
-        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12)) +
-    geom_boxplot(aes(y=value, group=interaction(month,variable)), alpha=0.2)+
-  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
-  ylab('DCM scaling factor')+theme_bw()+scale_y_continuous(limits=c(0,10), breaks = seq(0,10))+
-  scale_colour_discrete(guide=FALSE)+scale_fill_discrete(guide=FALSE)
-```
-
 ## Navarro's Ratio
-
-First, using Flo's approach
-
-```{r sigma ratio 1, echo=TRUE}
-# Compute the SIGMA@MAX MLD for each year and each platform
-MLDdf_info1 <- ddply(init_MLD, ~year~platform, summarize,
-                maxMLD = max(MLD, na.rm = T),
-                sigmaMaxMLD = sigmaMaxMLD[which.max(MLD)])
-
-# Compute the sigma_ratio, i.e. SIGMA@DCM/SIGMA@MAX MLD
- sigma_ratio1 <- ldply(as.list(unique(MLDdf$juld)), function(i){
-   tmp <- MLDdf[MLDdf$juld == i,]
-   tmp2 <- fit[fit$juld == i,]
-   tmp3 <- profiles[profiles$juld == i,]
-   sigmaMaxMLD <- MLDdf_info1$sigmaMaxMLD[which(MLDdf_info1$year == tmp$year & MLDdf_info1$platform == tmp$platform)]
-   sigmaDCM <- approx(tmp3$depth, tmp3$sigma, tmp2$Zmax)$y #interpolation
-   ratio = sigmaDCM/sigmaMaxMLD
-   data.frame(ratio = ratio, juld = tmp$juld[1], month = tmp$month[1])
- })
-
-# 1. First plot to see the spread in sigma MAX mld (amongst platfrom).
-ggplot(MLDdf_info1, aes(x=factor(year), y=sigmaMaxMLD, color=factor(platform)))+geom_point()+scale_y_continuous(limits=c(13.8,15.0))
-
- ggplot(sigma_ratio1, aes(x=month, y=ratio)) +
-    geom_smooth(stat = 'summary',
-#              fun.data = median_hilow,
-             fun.data = mean_cl_boot,
-              fun.args = list(conf.int = 0.95), alpha=0.5)+
-  geom_boxplot(aes(group=month), alpha=0.2, notch = TRUE)+
-  theme_bw()+scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12))+
-  scale_y_continuous(breaks = seq(0.8,1.2,0.05), minor_breaks = NULL) +
-  ylab('sigma@DCM/sigma@MLD_MAX')
-```
-
-First, using Art's approach
 
@@
 require(scales)
-# # # # # # # # # # # # # #
- # As I would have done it #
 
@@
    ratio = sigmaMAX/sigmaMaxMLD)
-
-ggplot(MLDdf_info2, aes(x=factor(year), y=sigmaMaxMLD, color=factor(platform)))+geom_point()+scale_y_continuous(limits=c(13.8,15.0))
-
-discfig1<-ggplot(sigma_ratio2, aes(x=month, y=ratio)) +
-    geom_smooth(stat = 'summary',
-#              fun.data = median_hilow,
-             fun.data = mean_cl_boot,
-              fun.args = list(conf.int = 0.95), alpha=0.5,color=brewer_pal(palette = MyPal)(2)[1],fill=brewer_pal(palette = MyPal)(2)[1])+
-  geom_boxplot(aes(group=month), alpha=0.2, notch = TRUE,color=brewer_pal(palette = MyPal)(2)[1],fill=brewer_pal(palette = MyPal)(2)[1])+
-  theme_bw()+scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12))+
-  scale_y_continuous(breaks = seq(0.8,1.2,0.05), minor_breaks = NULL) +
-  ylab(TeX('$\\sigma_{DCM}/\\sigma_{MLD,max}$'))
-print(discfig1)
-```
-
-Comparing Both
-
-```{r sigma_ratio_comp, echo=TRUE, include=FALSE}
-###
-require(reshape2)
-M1<-MLDdf_info1[,c('year','platform','sigmaMaxMLD')]
-colnames(M1)[3]<-'sigmaMaxMLD_1'
-M2<-MLDdf_info2[,c('year','platform','sigmaMaxMLD')]
-colnames(M2)[3]<-'sigmaMaxMLD_2'
-
-MM <- merge(M1,M2,by=c('year','platform'))
-
-ggplot(MM, aes(x=sigmaMaxMLD_1, y=sigmaMaxMLD_2, color=factor(platform), shape=factor(year)))+geom_point()
-
-s1<-subset(sigma_ratio1,select = c("month", "ratio"))
-colnames(s1)[2]<-'ratio_1'
-s2<-subset(sigma_ratio2,select = c("month", "ratio"))
-colnames(s2)[2]<-'ratio_2'
-
-ss <- merge(s1,s2,by=c('month'))
-ss <- melt(ss,id.vars=c("month"))
-
-ggplot(ss, aes(x=month, y=value, fill=variable, color=variable))+
-  geom_smooth(stat = 'summary',
-#              fun.data = median_hilow,
-             fun.data = mean_cl_boot,
-             fun.args = list(conf.int = 0.95), alpha=0.5)+
-  geom_boxplot(aes(group=interaction(month,variable)),
-               alpha=0.2, notch = TRUE)+
-  theme_bw()+scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12))+
-  scale_y_continuous(breaks = seq(0.8,1.2,0.05), minor_breaks = NULL) +
-  ylab('sigma@DCM/sigma@MLD_MAX')
-
-```
-
-Interannual checkup
-```{r ratio_interannual, include=FALSE}
-
-sigma_ratio2d<-ddply(sigma_ratio2,.(platform, juld), mutate,
-                    mY = dmy(paste0("15",sprintf("%02d",month),year)))
-
-ggplot(sigma_ratio2d, aes(x=mY, y=ratio)) +
-    geom_smooth(stat = 'summary',
-#              fun.data = median_hilow,
-             fun.data = mean_cl_boot,
-              fun.args = list(conf.int = 0.95), alpha=0.5)+
-  geom_boxplot(aes(group=mY), alpha=0.2, notch = TRUE)+
-  theme_bw()+
-  scale_y_continuous(breaks = seq(0.8,1.2,0.05), minor_breaks = NULL) +
-  ylab('sigma@DCM/sigma@MLD_MAX')
-
-ggplot(sigma_ratio2d, aes(x=mY, y=sigmaMAX)) +
-    geom_smooth(stat = 'summary',
-#              fun.data = median_hilow,
-             fun.data = mean_cl_boot,
-              fun.args = list(conf.int = 0.95), alpha=0.5)+
-  geom_boxplot(aes(group=mY), alpha=0.2, notch = TRUE)+
-  theme_bw()+coord_cartesian(ylim=c(15,12))+scale_y_reverse()
-```
-
-```{r ratio spatial, fig.width=8,fig.height=8}
-require(ggmap)
-mm <- get_map
-
-mycoord <- c(27,40.5,42,47)
-myMap_stamen <- get_map(location=mycoord,source="stamen", maptype="watercolor")
-save(myMap_stamen, file="BS_StaMap.Rdata") 
-#load(file="BS_StaMap.Rdata")
-
-ms<-ggmap(myMap_stamen, darken = c(0.6,"white"))
-ms1<-ms+geom_point(data=subset(sigma_ratio2,(month>3)&(month<11)&(!is.na(ratio))), aes(x=lon,y=lat, color=ratio))+facet_wrap(~month, scale="fixed", ncol=3)+theme_bw()
-ms1+scale_color_distiller(palette = 'RdYlBu')#,limits=c(0.9,1.0))
 ```
@@
 
-```{r paratdcm}
+```{r paratdcm, error=FALSE, warning=FALSE, echo=FALSE, message=FALSE, results='hide', include=FALSE, eval=TRUE}
 # Attempt to derive PARfraction at the DCM depth
@@
   ylab('[% of surface PAR at DCM]')
-print(discfig2)
-
-```
-
-```{r PARatDCM2BIS}
+#print(discfig2)
+
+```
+
+```{r PARatDCM2BIS, error=FALSE}
 #tmp_fitc<-tmp_fitc[,-which(colnames(tmp_fitc)=="PARpartDCM")]
@@
 
-discfigb2
-```
-
-```{r discfig}
-
- gA <- ggplotGrob(discfig1+geom_text(label='a)', x=3.5, y= 1.05, size=5))
- gB <- ggplotGrob(discfig2+geom_text(label='b)', x=3.5, y= 4.8 , size=5 ))
-
-grid::grid.newpage()
-grid::grid.draw(rbind(gA, gB))
-
-#grid.arrange(discfig1+geom_text(label='a)', x=3.5, y= 1.05)+theme(axis.line.y.left=element_text(margin = margin(t = 20)),#+ylab('')
- #            discfig2+geom_text(label='b)', x=3.5, y= 4.8),#+ylab('')
-#             ncol=1)
-```
-```{r discfigb}
-
- gA <- ggplotGrob(discfigb1+geom_text(label='a)', x=3.5, y= 1.05, size=5, color='black'))
- gB <- ggplotGrob(discfigb2+geom_text(label='b)', x=3.5, y= 4.8 , size=5, color='black' ))
-
-grid::grid.newpage()
-grid::grid.draw(rbind(gA, gB))
-
-#grid.arrange(discfig1+geom_text(label='a)', x=3.5, y= 1.05)+theme(axis.line.y.left=element_text(margin = margin(t = 20)),#+ylab('')
- #            discfig2+geom_text(label='b)', x=3.5, y= 4.8),#+ylab('')
-#             ncol=1)
-```
-
-```{r ratio_PARatDCM, fig.width=10,fig.height=10, include=FALSE, eval=FALSE}
+print(discfigb2)
+```
+
+# Potential Additional sections.
+
+## Spatial
+
+```{r Fig4,fig.width=8,fig.height=8}
 
 require(ggmap)
-mm <- get_map
+#mm <- get_map
 
 mycoord <- c(27,40.5,42,47)
-myMap_stamen <- get_map(location=mycoord,source="stamen", maptype="watercolor")
-save(myMap_stamen, file="BS_StaMap.Rdata") 
-#load(file="BS_StaMap.Rdata")
-
-ms<-ggmap(myMap_stamen, darken = c(0.6,"white"))
-ms1<-ms+geom_point(data=subset(tmp_fitc,(month>3)&(month<11)&(!is.na(PARpartDCM))), aes(x=lon,y=lat, color=PARpartDCM*100))+facet_wrap(~month, scale="fixed", ncol=2)+theme_bw()
-ms1+scale_color_distiller(palette = 'RdYlBu',limits=c(0,6))
-
-# ms2<-ms+geom_point(data=tmp_fitco, aes(x=lon,y=lat, color=factor(shape)))+
-#   facet_wrap(~month, scale="fixed")+theme_bw()
-# ms2#+scale_color_discrete(name="", labels=c('non-DCM','DCM'))
-
-```
-
-# Potential Additional sections.
-
-## Spatial
-
-Numerous Spatial analysis have been done without concluding results beyond "Homogeneous behavior across the central basin".
-
-```{r spatial}
-
-require(ggmap)
-mm <- get_map
-
-mycoord <- c(27,40.5,42,47)
-myMap_stamen <- get_map(location=mycoord,source="stamen", maptype="watercolor")
-save(myMap_stamen, file="BS_StaMap.Rdata") 
-#load(file="BS_StaMap.Rdata")
-
-ms<-ggmap(myMap_stamen, darken = c(0.6,"white"))
-ms1<-ms+geom_point(data=tmp_fitco, aes(x=lon,y=lat, color=factor(dcm_or_not)))+facet_wrap(~month, scale="fixed")+theme_bw()
-ms1+scale_color_discrete(name="", labels=c('non-DCM','DCM'))
-
-# ms2<-ms+geom_point(data=tmp_fitco, aes(x=lon,y=lat, color=factor(shape)))+
-#   facet_wrap(~month, scale="fixed")+theme_bw()
-# ms2#+scale_color_discrete(name="", labels=c('non-DCM','DCM'))
-
+myMap_stamen <- get_map(location=mycoord,source="stamen",maptype = "watercolor", force = TRUE)
+
+tmp_fitco$monthn<-factor(tmp_fitco$month, labels = month.abb[unique(tmp_fitco$month)])
+
+ms<-ggmap(myMap_stamen)
+ms1<-ms+geom_point(data=tmp_fitco, aes(x=lon,y=lat, color=factor(dcm_or_not)))+
+  facet_wrap(~monthn, scale="fixed")+
+  theme_bw()+
+  scale_color_discrete(name="", labels=c('non-DCM','DCM'))+
+  theme(legend.position = 'top', legend.box = "horizontal")+
+  scale_x_continuous(name='', breaks = c(27,30,33,36,39), limits = c(27,42), expand = expand_scale(add = 0))+
+  scale_y_continuous(name='', breaks = seq(41,47), limits = c(40.7,47), expand = expand_scale(add = 0))
+
+ms1
 ```
@@
 
-P_years_depth <- ggplot(tmp_zmax, aes(x=month, fill=variable, color=variable)) +
-    geom_line(data=tmp_zmaxA,aes(y=value),alpha =0.5, size=3)+
-      geom_smooth(aes(y=value, group=interaction(year, variable)),stat = 'summary',
-             fun.data = mean_cl_boot,
-              fun.args = list(conf.int = 0.1))+scale_x_continuous(name='', breaks=c(), labels="")+
-  ylab('[m]')+theme_bw()+coord_cartesian(ylim=c(90,0), expand = FALSE)+scale_y_reverse()+
-  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal)+facet_grid(.~year)
+#levels(tmp_zmax$variable)<-levels(tmp_zmax$variable)[-which()]
+#levels(tmp_zmaxA$variable)<-levels(tmp_zmax$variable)[-7]
+
+P_years_depth <- ggplot(subset(tmp_zmax, variable !="Zdemi"), aes(x=month, fill=variable, color=variable)) +
+    geom_line(data=subset(tmp_zmaxA, variable !="Zdemi"),aes(y=value),alpha =1, size=0.5, linetype=2)+
+      geom_smooth(aes(y=value, group=variable),
+                  stat = 'summary',
+                  fun.data = mean_cl_boot,
+                  fun.args = list(conf.int = 0.95), 
+                  alpha=0.2, linetype=0)+
+  scale_x_continuous(name='', breaks=c(), labels="", limits=c(.5,12.5))+
+  ylab('[m]')+theme_bw()+
+  coord_cartesian(ylim=c(90,0), expand = FALSE)+scale_y_reverse()+
+  scale_color_brewer(aesthetics = c("colour", "fill"),
+                       type = qual ,
+                       palette=MyPal,
+                       name="Depth Horizons", 
+                       labels=list(TeX('$z_{MLD}$'),
+                                TeX('$z_{DCM}$'),
+                                TeX('$z_{low}$'),
+                                TeX('$z_{50,bottom}$'),
+                                TeX('$z_{50,top}$'),
+                                TeX('$z_{\\mathrm{PAR}\\,1%}$')))+
+#  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal, name='')+
+  facet_grid(.~year)+
+  theme(legend.position = 'top', legend.box = "horizontal",panel.spacing = unit(0, "lines"))+
+  guides(colour = guide_legend(nrow = 1))
 
@@
 P_years_sig <-ggplot(tmp_sig, aes(x=month, fill=variable, color=variable)) +
-       geom_line(data=tmp_sigA,aes(y=value),alpha =0.5, size=3)+
+       geom_line(data=tmp_sigA,aes(y=value),alpha =1, size=0.5, linetype=2)+
       geom_smooth(aes(y=value, group=interaction(year, variable)),stat = 'summary',
              fun.data = mean_cl_boot,
-              fun.args = list(conf.int = 0.1))+scale_x_continuous(name='', breaks=c(), labels="")+
-  ylab('[kg/m3]')+theme_bw()+coord_cartesian(ylim=c(10,16))+scale_y_reverse()+
-  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal)+facet_grid(.~year)
+              fun.args = list(conf.int = 0.95), 
+                  alpha=0.2, linetype=0)+
+  scale_x_continuous(name='', breaks=c(), labels="", limits=c(.5,12.5))+
+  ylab('[kg/m3]')+theme_bw()+
+  coord_cartesian(ylim=c(10,16), expand = FALSE)+
+  scale_y_reverse()+
+  #scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal)+
+  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal,
+                       name="Density Horizons", 
+                       labels=list(TeX('$\\sigma_{MLD}$'),
+                                TeX('$\\sigma_{DCM}$'),
+                                TeX('$\\sigma_{low}$'),
+                                TeX('$\\sigma_{50,bottom}$'),
+                                TeX('$\\sigma_{50,top}$'),
+                                TeX('$\\sigma_{\\mathrm{PAR}\\,1%}$')))+
+  facet_grid(.~year)+
+  theme(legend.position = 'top', legend.box = "horizontal",panel.spacing = unit(0, "lines"))+
+          guides(colour = guide_legend(nrow = 1))
 
@@
 
-```{r, include=FALSE}
+```{r inter_parts, include=FALSE}
 
@@
 P_years_part <-ggplot(tmp_part, aes(x=month, fill=variable, color=variable)) +
-       geom_line(data=tmp_partA,aes(y=value),alpha =0.5, size=3)+
+       geom_line(data=tmp_partA,aes(y=value),alpha =1, size=0.5, linetype=2)+
       geom_smooth(aes(y=value, group=interaction(year, variable)),stat = 'summary',
              fun.data = mean_cl_boot,
-              fun.args = list(conf.int = 0.1))+scale_x_continuous(name='', breaks=c(), labels="")+
-  ylab('[%]')+theme_bw()+coord_cartesian(ylim=c(0,100))+
-  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal,
-                     name='part of tot CHL content', labels=c('above MLD',
-                                                              'within a 10m band around DCM',
-                                                              'above optical depth'))+
-  facet_grid(.~year)
+              fun.args =  list(conf.int = 0.95), 
+                  alpha=0.2, linetype=0)+
+  scale_x_continuous(name='', breaks=c(), labels="", limits=c(.5,12.5))+
+  ylab('[%]')+theme_bw()+coord_cartesian(ylim=c(0,100), expand = FALSE)+
+  scale_color_brewer(name='Part of tot. Chl:',
+                     labels=c('above MLD','within 5m of DCM','above optical depth'),
+                     aesthetics = c("colour", "fill"),type = qual ,palette=MyPal)+
+  facet_grid(.~year)+theme(legend.position = 'top', legend.box = "horizontal",panel.spacing = unit(0, "lines"))+ guides(colour = guide_legend(nrow = 1))
 
@@
 
-```{r, include=FALSE}
+```{r inter_conc, include=FALSE}
 
@@
 P_years_conc <-ggplot(tmp_conc, aes(x=month, fill=variable, color=variable)) +
-       geom_line(data=tmp_concA,aes(y=value),alpha =0.5, size=3)+
+       geom_line(data=tmp_concA,aes(y=value),alpha =1, size=0.5, linetype=2)+
       geom_smooth(aes(y=value, group=interaction(year, variable)),stat = 'summary',
              fun.data = mean_cl_boot,
-              fun.args = list(conf.int = 0.1))+scale_x_continuous(name='', breaks=c(), labels="")+
-  ylab('[%]')+theme_bw()+coord_cartesian(ylim=c(0,4))+
+              fun.args = list(conf.int = 0.95), 
+                  alpha=0.2, linetype=0)+
+  scale_x_continuous(name='', breaks=c(), labels="", limits=c(.5,12.5))+
+  ylab('[mg/m3]')+theme_bw()+coord_cartesian(ylim=c(0,3), expand = FALSE)+
   scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal)+
-  facet_grid(.~year)
+  facet_grid(.~year)+scale_color_brewer(aesthetics = c("colour", "fill"),type = qual,
+                       palette=MyPal, 
+                       name="Chla concentrations",
+                       labels=c("Average","Surface","DCM"))+
+  facet_grid(.~year)+theme(legend.position = 'top', legend.box = "horizontal",panel.spacing = unit(0, "lines"))+ guides(colour = guide_legend(nrow = 1))
 
@@
 
-```{r, include=FALSE}
-tmp_corrC<- dcast(tmp_corr,formula = month~variable, fun.aggregate = mean, na.rm=TRUE)
-tmp_corrA<-melt(tmp_corrC, id.vars=c('month'))
-
-P_years_corr <-ggplot(tmp_corr, aes(x=month, fill=variable, color=variable)) +
-       geom_line(data=tmp_corrA,aes(y=value),alpha =0.5, size=3)+
-      geom_smooth(aes(y=value, group=interaction(year, variable)),stat = 'summary',
-             fun.data = mean_cl_boot,
-              fun.args = list(conf.int = 0.1))+scale_x_continuous(name='', breaks=c(), labels="")+
-  ylab('[-]')+theme_bw()+coord_cartesian(ylim=c(0,4))+
-  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal)+
-  facet_grid(.~year)
-
-P_years_corr
-```
-
-```{r, fig.height=15, fig.width=10}
-grid.arrange(P_years_depth+theme(legend.position = ''),
-             P_years_sig+theme(legend.position = '', strip.background = element_blank(),strip.text.x = element_blank()), 
-             P_years_part+theme(legend.position = '', strip.background = element_blank(),strip.text.x = element_blank()),
-             P_years_conc+theme(legend.position = '', strip.background = element_blank(),strip.text.x = element_blank()),
-             P_years_corr+theme(legend.position = '', strip.background = element_blank(),strip.text.x = element_blank()) ,
+```{r Fig11, fig.height=12, fig.width=10}
+grid.arrange(P_years_depth,
+             P_years_sig+theme( strip.background = element_blank(),strip.text.x = element_blank()), 
+             P_years_part+theme( strip.background = element_blank(),strip.text.x = element_blank()),
+             P_years_conc+theme( strip.background = element_blank(),strip.text.x = element_blank()),
              ncol=1)
@@
 ```
-
-## Quick interannual Anomalies and correlations 
-```{r}
-# compute annual anomalies ? 
-Zmulti<-ddply(tmp_zmax, .(month,year,variable), function(d){
-    do<-d
-    do$anom = d$value - subset(tmp_zmaxA, (month==d$month[1]) & (variable==d$variable[1]))[,'value']
-    return(do)
-   })
-```
-
-```{r}
-Smulti<-ddply(tmp_sig, .(month,year,variable), function(d){
-    do<-d
-    do$anom = d$value - subset(tmp_sigA, (month==d$month[1]) & (variable==d$variable[1]))[,'value']
-    return(do)
-   })
-```
-
-```{r}
-Cmulti<-ddply(tmp_conc, .(month,year,variable), function(d){
-    do<-d
-    do$anom = d$value - subset(tmp_concA, (month==d$month[1]) & (variable==d$variable[1]))[,'value']
-    return(do)
-   })
-
-Pmulti<-ddply(tmp_part, .(month,year,variable), function(d){
-    do<-d
-    do$anom = d$value - subset(tmp_partA, (month==d$month[1]) & (variable==d$variable[1]))[,'value']
-    return(do)
-   })
-
-Xmulti<-ddply(tmp_corr, .(month,year,variable), function(d){
-    do<-d
-    do$anom = d$value - subset(tmp_corrA, (month==d$month[1]) & (variable==d$variable[1]))[,'value']
-    return(do)
-   })
-```
-
-```{r}
-PA_years_depth <- ggplot(Zmulti, aes(x=month, fill=variable, color=variable)) +
-    geom_smooth(aes(y=anom, group=interaction(year, variable)),stat = 'summary',
-             fun.data = mean_cl_boot,
-              fun.args = list(conf.int = 0.9))+scale_x_continuous(name='', breaks=c(), labels="")+
-#  geom_boxplot(aes(y=anom), alpha=.2)+
-  ylab('[m]')+theme_bw()+
-  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette='Set1')+facet_grid(variable~year, scales = 'free_y')
-
-PA_years_depth
-```
-
-```{r}
-PA_years_sig <- ggplot(Smulti, aes(x=month, fill=variable, color=variable)) +
-    geom_smooth(aes(y=anom, group=interaction(year, variable)),stat = 'summary',
-             fun.data = mean_cl_boot,
-              fun.args = list(conf.int = 0.9))+scale_x_continuous(name='', breaks=c(), labels="")+
-#  geom_boxplot(aes(y=anom), alpha=.2)+
-  ylab('[m]')+theme_bw()+
-  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette='Set1')+facet_grid(variable~year, scales = 'free_y')
-
-PA_years_sig
-```
-
-```{r}
-PA_years_conc <- ggplot(Cmulti, aes(x=month, fill=variable, color=variable)) +
-    geom_smooth(aes(y=anom, group=interaction(year, variable)),stat = 'summary',
-             fun.data = mean_cl_boot,
-              fun.args = list(conf.int = 0.9))+scale_x_continuous(name='', breaks=c(), labels="")+
-#  geom_boxplot(aes(y=anom), alpha=.2)+
-  ylab('[m]')+theme_bw()+
-  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal)+facet_grid(variable~year, scales = 'free_y')
-
-PA_years_conc
-```
-
-```{r}
-ZmultiCast <-  dcast(Zmulti,year~variable, value.var = 'anom', fun.aggregate = mean, na.rm=TRUE)
-ZmultiCastSD <-  dcast(Zmulti,year~variable, value.var = 'anom', fun.aggregate = sd, na.rm=TRUE)
-ZmultiCast<-ZmultiCast[,-which(colnames(ZmultiCast)=='Zdemi')]
-
-SmultiCast <-  dcast(Smulti,year~variable, value.var = 'anom', fun.aggregate = mean, na.rm=TRUE)
-
-PmultiCast <-  dcast(Pmulti,year~variable, value.var = 'anom', fun.aggregate = mean, na.rm=TRUE)
-
-CmultiCast <-  dcast(Cmulti,year~variable, value.var = 'anom', fun.aggregate = mean, na.rm=TRUE)
-
-pdt <- merge(ZmultiCast,SmultiCast,by = c('year'))
-pdt <- merge(pdt,PmultiCast,by = c('year'))
-pdt <- merge(pdt,CmultiCast,by = c('year'))
-
-require(GGally)
-ggpairs(pdt,columns = 3:11 )+theme_bw()
-```
-
-```{r}
-ggcorr(pdt, method = c("everything", "spearman"), geom = 'circle')
-```
-
-```{r}
-ZmultiCastM   <-  dcast(Zmulti,year+month~variable, value.var = 'anom', fun.aggregate = mean, na.rm=TRUE)
-
-ZmultiCastMSD <-  dcast(Zmulti,year+month~variable, value.var = 'anom',
-                        fun.aggregate = sd, na.rm=TRUE)
-ZmultiCastM   <-      ZmultiCastM[,-which(colnames(ZmultiCastM)=='Zdemi')]
-
-SmultiCastM <-  dcast(Smulti,month+year~variable, value.var = 'anom', fun.aggregate = mean, na.rm=TRUE)
-
-PmultiCastM <-  dcast(Pmulti,month+year~variable, value.var = 'anom', fun.aggregate = mean, na.rm=TRUE)
-
-CmultiCastM <-  dcast(Cmulti,month+year~variable, value.var = 'anom', fun.aggregate = mean, na.rm=TRUE)
-
-pdtM <- merge(ZmultiCastM,SmultiCastM,by = c('year','month'))
-pdtM <- merge(pdtM,PmultiCastM,by = c('year','month'))
-pdtM <- merge(pdtM,CmultiCastM,by = c('year','month'))
-
-ggpairs(pdtM,columns = c(3,4,5,9,10,14,16,17,18) )+theme_bw()
-```
-
-```{r}
-ggcorr(pdtM, method = c("pairwise.complete.obs", "spearman"), geom = 'circle')
-
-```
-
-```{r}
-ggplot(pdt,aes(x=Z90B, y=Zmax, color=factor(year)))+
-  geom_point(size=4)+
-  geom_point(data=pdtM)+theme_bw()
-```
-
-```{r}
-ggplot(pdt,aes(x=DCMratio, y=Zmax, color=factor(year)))+
-  geom_point( size=4)+
-  geom_point(data = pdtM, size=1)+
-  theme_bw()
-```
-
-```{r}
-ggplot(pdt,aes(x=DCMratio, y=sigmaMAX, color=factor(year)))+
-  geom_point()+theme_bw()
-```
-
-```{r}
-
-ggplot(pdtM,aes(x=sigmaMLD, y=sigmaMAX, shape=factor(year), color=factor(month)))+
-  geom_point()+theme_bw()+facet_wrap(~month)
-
-```
-
-# Defining ? and compare ? different type of variability.
-
-How to characterize the Seasonal STD and Annual STD ?
-
-* Spatial STD, would be the time average of the std within month+year bins
-* Seasonal STD, would be the seasonal STD of monthly means. 
-* Interannual STD, would be interannual STD of monthly averages, averaged over the months ?
-
-```{r}
-SDMAT<- function(tab_multi,tab_A,tab_all ) {
-
-  # How to characterize the Seasonal STD and Annual STD ? 
-  ##     Spatial STD, would be the time average of the std within month+year bins
-  ##    Seasonal STD, would be the seasonal STD of monthly means. 
-  ## Interannual STD, would be interannual STD of monthly averages, averaged over the months ?
-
-multiCastMSD <-  dcast(tab_multi,year+month~variable, value.var = 'anom', fun.aggregate = sd, na.rm=TRUE)
-mSpatialSD <- dcast(melt(multiCastMSD, id.vars = .(year,month)), variable~.,fun.aggregate = mean, na.rm=TRUE)
-colnames(mSpatialSD)<-c('variable','SpatialSD')
-
-mSeasonalSD <- dcast(tab_A, variable~., fun.aggregate = sd, na.rm=TRUE)
-colnames(mSeasonalSD)<-c('variable','SeasonalSD')
-
-mC2 <- dcast(tab_all,formula = year+month~variable, fun.aggregate = mean, na.rm=TRUE)
-mC3 <- dcast(melt(mC2,id.vars = .(month,year)), formula=variable+month~.,fun.aggregate = sd, na.rm=TRUE )
-colnames(mC3)[3]<-"sd"
-
-mAnnualSD <- ddply(mC3, .(variable),summarize,AnnualSD=mean(sd, na.rm=TRUE) )
-
-tt<- merge(mSpatialSD,mSeasonalSD, by="variable")
-tt<- merge(tt,mAnnualSD , by="variable")
-
-ttNorm <- ddply(tt, .(variable), mutate, 
-                OneSD=mean(c(SpatialSD,SeasonalSD,AnnualSD) ),
-                SpatialSDNorm  = SpatialSD/OneSD, 
-                SeasonalSDNorm = SeasonalSD/OneSD, 
-                AnnualSDNorm   = AnnualSD/OneSD)
-
-return(ttNorm)
-}
-```
-
-```{r}
-sdZ<- SDMAT(Zmulti, tmp_zmaxA, tmp_zmax)
-
-sdS<- SDMAT(Smulti, tmp_sigA , tmp_sig)
-sdC<- SDMAT(Cmulti, tmp_concA, tmp_conc)
-
-allsd<-rbind(sdZ, sdS, sdC)
-
-OrderedSDPlot<- function(t,allsd, norm=TRUE){
-  if (norm){normstring="Norm"}else{normstring=""}
-bibi<- allsd[,c("variable",paste0(t,"SD",normstring))]
-bibi$variable<-factor(bibi$variable,
-                      levels=bibi$variable[order(bibi[,paste0(t,"SD",normstring)], decreasing = TRUE)], ordered=TRUE)
-
-p<-ggplot(bibi, aes_string(x="variable", y=paste0(t,"SD",normstring)))+
-  geom_col(position = 'dodge')+theme_bw()+
-  theme(axis.text.x = element_text(angle = 90))
-return(p)
-}
-
-OrderedSDPlot("Spatial" , allsd, norm=TRUE)
-OrderedSDPlot("Annual"  , allsd, norm=TRUE)
-OrderedSDPlot("Seasonal", allsd, norm=TRUE)
-
-OrderedSDPlot("Spatial" , sdZ, norm=FALSE)
-OrderedSDPlot("Spatial" , sdS, norm=FALSE)
-
-```
-
-```{r}
-
-allsd$variable<-factor(allsd$variable,
-                      levels=allsd$variable[order(allsd[,paste0("Spatial","SD","Norm")], decreasing = TRUE)], ordered=TRUE)
-
-ggplot(melt(subset(allsd, select=c("variable","SpatialSDNorm","SeasonalSDNorm","AnnualSDNorm")),
-            id.vars=.(variable), variable.name = "Stat"), 
-       aes(x=variable, y=value, color=Stat, fill=Stat))+
-  geom_col(position = 'dodge')+theme_bw()+
-  theme(axis.text.x = element_text(angle = 90))+
-  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal)
-
-```
-
-## As introduction before processing
-
-### Depth
-Fig. [DEPTH] shows the mean Chla content per boxes of X METERS-width over periods of ten days for
-all Chla profiles.
-Over-imposed is the spatial median of the 1 and 10% isolumes.
-**Would be better if computed on the same time-bins, for simplicity**
-Those were obtained by fitting simple exponential decay of PAR to derive both PAR0 and attenuation parameters. 
-Only about half (**?**) of the profiles contain PAR measurements.
-
-We observe here :
-
-* Subsurface CHL maximum from ~day 100 to 280.
-* Core CHL is:
-    * above 10% from 280 to 100 ; 
-    * more or less at 1% (or below) from 100 to 150. 
-    * in the upper part of the 1% 10% interval from 150 to 180.
-
-**It is important to comment on the relevance of the analysis.**
-The width of temporal and vertical bins in this processing have been chosen to ensure that the relative error on displayed mean chl content is below 20% all over the plot (or strip parts if not possible).
-This also ensure a meaningfull analysis, despite spatial variability in the horizontal dimension which is integrated in our approach.
-
-![alt text](./mean_chla_Z_context.png)
-
-### SIGMA
-
-Fig. [RHO] follows the same organization than Fig. [DEPTH] using XXX width for the bins. 
-Here, we added MLD computed from profiles's T & S following Kara et al. 2008.
-In particular, we indicate the range of maximum density of the mixed layer, reached around d50.
-
-We note that :
-
-* CHL remains above MLDmax all year long
-
-* CHL is
-    * above MLD from ~320 to 25.
-    * across mld in [25 - 100] and [280-315].
-    * below MDL from 100-280.
-
-![alt text](./sigma_context.png)
-
-```{r, include=FALSE}
-
-seasonplot<- function(vavar,vname, df=tmp_fitc){
-g<-  ggplot(df, aes_string(x="month",y=vavar)) +
-    geom_boxplot(aes(group=month), notch = T)+
-    geom_smooth(stat = 'summary',
-#              fun.data = median_hilow,
-              fun.data = mean_cl_boot,
-              fun.args = list(conf.int = 0.95), alpha=0.5)+
-  scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12)) +
-  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
-  ylab(vname)+theme_bw()
-
-return(g)
-}
-
-P_season_tot <- seasonplot("total_chla","Total Chla Content - [mg/m²]")
-P_season_tot
-
-P_season_UpMLD <- seasonplot("UpMLD_chla","Chl above MLD - [mg/m²]")
-P_season_UpMLD
-
-P_season_DoMLD <- seasonplot("DoMLD_chla","Chl below MLD - [mg/m²]")
-P_season_DoMLD
-
-P_season_RaMLD <- seasonplot("RaMLD_chla","part of TotCHL above MLD - [%]")
-P_season_RaMLD
-
-P_season_Vis <- seasonplot("visible_chla","Chl above Optical Depth - [mg/m²]")
-P_season_Vis
-
-P_season_VisR <- seasonplot("visible_ratio","Part of visible CHL - [%]")
-P_season_VisR
-
-P_season_Zmax <- seasonplot("Zmax","Depth of DCM - [m]")
-P_season_Zmax+ylim(c(100,0))
-
-```
-
-## Number of profiles and number of DCM profiles.
-
-```{r, fig.height=3}
-ggplot(tmp_my, aes(x=month, color=factor(year), y=nprof)) +
-    geom_line()+theme_bw()+ylab('number of profiles -[%]')+ 
-  scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12))
-
-ggplot(tmp_my, aes(x=month, color=factor(year), y=percentage_dcm)) +
-    geom_line()+theme_bw()+ylab('percentage of DCM profiles -[%]')+ 
-  scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12)) 
-```
-
-This makes much more sense if we integrate 'Other' as DCM profiles.
-
-```{r percentprofiles}
-
-tmp_my2<-ddply(tmp_fitc, .(month,year), summarize,
-                nprof = length(dcm_or_not),
-                percentage_dcm =  sum(dcm_or_not)/length(dcm_or_not)*100
-                )
-
-tmp_myo<-ddply(tmp_fitco, .(month,year), summarize,
-                nprof = length(dcm_or_not),
-                percentage_dcm =  sum(dcm_or_not)/length(dcm_or_not)*100
-                )
-
-ggplot(tmp_my, aes(x=month, color=factor(year), y=percentage_dcm)) +
-    geom_line()+theme_bw()+ylab('percentage of DCM profiles -[%]')+ 
-  scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12))
-
-ggplot(melt(merge(tmp_my2[,c(1,2,4)],tmp_myo[,c(1,2,4)],by=c('month','year')),id.vars=c('month','year')),
-       aes(x=month,  y=value, fill=variable, color=variable)) +
-  geom_smooth(stat = 'summary',
-#              fun.data = median_hilow,
-              fun.data = mean_cl_boot,
-              fun.args = list(conf.int = 0.95), alpha=0.5)+
-    #geom_smooth(data=tmp_myo,stat = 'summary',
-#              fun.data = median_hilow,,
-     #         fun.data = mean_cl_boot,
-      #        fun.args = list(conf.int = 0.95), alpha=0.5, fill='blue', color='blue')+
-    theme_bw()+ylab('[%]')+ 
-  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual,
-                     palette=MyPal,
-                     name='percentage of DCM profiles',
-                     labels=c('excl. "Others"', 'incl. "Others"'))+
-  scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12))
-
-# ggplot(tmp_my2, aes(x=month, y=percentage_dcm)) +
-#     geom_line()+geom_smooth(aes(y=value),stat = 'summary',
-# #              fun.data = median_hilow,
-#               fun.data = mean_cl_boot,
-#               fun.args = list(conf.int = 0.95), alpha=0.5)+
-#   theme_bw()+ylab('percentage of DCM profiles -[%]')+ 
-#   scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12))
-
-```
-
-## Optical Community Index
-
-Optical Community Index use the ratio between backscattering and fluorescence to infer changes in the optical properties of plankton cells, and thereby on planktonic groups.
-
-Here, we used the depth horizons given above (and derived for each profile) to distinguisch depth ranges :
-
-* Above the CHl Bulk.
-* Within the Bulk
-* Below.
-
-A significant difference in this index is observed for the layer above the bulk CHL, with much higer BBP/chl ratio.
-
-The same analysis was attempted considering additional layers (eg. involving a narrow band around DCM), but only surface planktons depicted a 
-clear optical community index signature.
-
-```{r bbratio}
-loc <- subset(tmp,
-              (fluo>0.1) & (!is.na(sigma))& (!is.na(depth)) & (sigma<15.5),
-              select = c('depth','month','fluo','sigma','bbp','juld','platform'))
-
-ll<-merge(loc,tmp_fitc,by=c('juld','platform'))
-
-lld <- ddply(ll,.(juld, platform, depth), transform, 
-                DepthRegion= ifelse(depth < Z90T, 'Above',
-                                    ifelse(depth < Z90B, 'Within Bulk',
-                                           'Below')))
-
-g1 <- ggplot(lld,aes(y=bbp/fluo, fill=factor(DepthRegion)))+#cut(sigma,c(9,13.5,14.5,15.5))
-  geom_boxplot(notch = TRUE, outlier.size = 0.2)+
-  theme_bw()+
-  facet_grid(~cut(month.x, breaks = c(0,2,4,6,8,10,12)))+
-  scale_x_discrete()+
-  scale_fill_brewer(palette = 3,type='seq',name='Layers - [kg/m3]')
-
-print(g1)
-```
-
-## Others profiles
-
-All "other" profiles emerges from DCM profiles, and goes back to DCM profiles. 
-The succession between shape is hard to read in z coordinates.
-
-In sigma coordinates it to emergence of a secondary bloom on top of the (stable) DCM. 
-This never last for more than a month (check) and may be induced by local events such as mesoscale dynamics.
-
-```{r other1}
-
-tmp_fitc$dshape<- paste(tmp_fitc$dcm_or_not,tmp_fitc$shape,sep='_')
-
-tee<-subset(tmp_fitc, select = c("juld","dshape","month","year","platform","dcm_or_not"))
-
-which(tee$dshape=="0_O")
-
-tee[which(tee$dshape=="0_O"),]
-
-ggplot(tee[which(tee$dshape=="0_O")-1,],aes(x=dshape))+geom_bar()+ggtitle("dshape before Others")
-ggplot(tee[which(tee$dshape=="0_O")+1,],aes(x=dshape))+geom_bar()+ggtitle("dshape after Others")
-
-ggplot(tee[which(tee$dshape=="0_O")-1,],aes(x=dcm_or_not))+geom_bar()+ggtitle("dshape after Others")
-
-```
-
-```{r other2}
-#rr  <- subset(complete_tmp, (platform=="7900591")&(juld>23900)&(juld<24000))
-#rr2 <- subset(tmp_fitc, (platform=="7900591")&(juld>23900)&(juld<24000))
-
-##
-rr  <- subset(complete_tmp, (platform=="6903240")&(juld>25350)&(juld<25440))
-rr2 <- subset(tmp_fitc, (platform=="6903240")&(juld>25350)&(juld<25440))
-
-red<-5
-
-ggplot(rr, aes(y=-depth, x=fluo +(juld-23946)/red, color=factor(juld)))+
-  geom_path(size=2)+ylim(c(-100,0))+
-  geom_errorbarh(aes(y=-Zmax, xmin=(juld-23946)/red, xmax=1+(juld-23946)/red))+theme_bw()
-
-ggplot(rr, aes(y=-sigma, color=factor(juld)))+
-  geom_path(aes(x=fluo+(juld-23946)/red),size=2)+
-  geom_errorbarh(data=rr2, aes(y=-sigmaMAX, xmin=(juld-23946)/red, xmax=1+(juld-23946)/red))+theme_bw()
-
-```
-
-```{r other3}
-rr  <- subset(complete_tmp, (platform=="7900591")&(juld>23900)&(juld<24000))
-rr2 <- subset(tmp_fitc, (platform=="7900591")&(juld>23900)&(juld<24000))
-
-red<-5
-
-ggplot(rr, aes(y=-depth, x=fluo +(juld-23946)/red, color=factor(juld)))+
-  geom_path(size=2)+ylim(c(-100,0))+
-  geom_errorbarh(aes(y=-Zmax, xmin=(juld-23946)/red, xmax=1+(juld-23946)/red))+theme_bw()
-
-ggplot(rr, aes(y=-sigma, color=factor(juld)))+
-  geom_path(aes(x=fluo+(juld-23946)/red),size=2)+
-  geom_errorbarh(data=rr2, aes(y=-sigmaMAX, xmin=(juld-23946)/red, xmax=1+(juld-23946)/red))+theme_bw()
-
-```
-
-```{r}
-knitr::knit_exit()
-```

### 2020-10-26 article_figures_ARTHUR_CAPET.Rmd
add light horizons

--- 2020-07-07 dcm_investigation_clean_Results_AC.Rmd
@@
 }
+
+```
+
+```{r add light data to full data}
+interpolated_light_data <- ldply(as.list(unique(complete_tmp2$juld)), function(i){
+  tmp1 <- complete_tmp2[complete_tmp2$juld == i,]
+  tmp2 <- initPAR[initPAR$juld == i,]
+  if(nrow(tmp2) == 0){
+    absolute_light <- rep(NA, nrow(tmp1))
+    # relative % of incoming surface PAR
+    relative_light <- absolute_light
+  }else{
+    absolute_light <- approx(tmp2$depth, tmp2$par, tmp1$depth)$y
+    # compute relative % of incoming surface PAR
+    relative_light <- (absolute_light/tmp2$par[1])*100 # could also put max(tmp2$par) car surface = max_par, therefore no ordering issue will appear (but tmp2$par[1] is good) 
+  }
+  data.frame(depth = tmp1$depth, absolute_light = absolute_light, relative_light = relative_light)
+})
+
+# add it to complete_tmp2
+complete_tmp2 <- cbind(complete_tmp2, light = interpolated_light_data$relative_light, light_absolute = interpolated_light_data$absolute_light)
 
@@
                             #Ziso1         = isoPAR(depth = depth , PAR = par),
-                            sigmaiso1      = try_default(approx(x=depth, y=sigma, xout=unique(Ziso1b), rule=2)$y,NA, quiet = FALSE)
+                            sigmaiso1      = try_default(approx(x=depth, y=sigma, xout=unique(Ziso1b), rule=2)$y,NA, quiet = FALSE),
+                          ### 
+                          # Adding diags for LIGHT Horizon here
+                            ISOlow       = try_default(approx(x=depth, y=light, xout=ZLow, rule=2)$y,NA, quiet = FALSE),
+                            ISO90B       = try_default(approx(x=depth, y=light, xout=Z90B, rule=2)$y,NA, quiet = FALSE),
+                            ISO90T       = try_default(approx(x=depth, y=light, xout=Z90T, rule=2)$y,NA, quiet = FALSE),
+                            ISOMLD       = min(light, na.rm = TRUE),
+                            ISOMAX       = try_default(approx(x=depth, y=light, xout=unique(Zmax), rule=2)$y,NA, quiet = FALSE),
+                            ISODEMI      = try_default(approx(x=depth, y=light, xout=unique(Zdemi), rule=2)$y,NA, quiet = FALSE),
+                          # just to see
+                            ISO_iso1 = try_default(approx(x=depth, y=light, xout=unique(Ziso1b), rule=2)$y,NA, quiet = FALSE)
                           )
@@
 
-Density framework shows less spatial variability, and more stable seasonal evolution.
-
-The deepest winter MLD sets pycnal layer of Z_1/2, which remains stable from February to September.
-From may to june, a DCM forms and migrate to higher layers.
-
-Unlike the previous plot, the pycnal coordinates allow to dissociate DCM from June to September.
-This is indicative of pycnal or mixing forces ruling the location of the DCM, rather than restrictevely light conditions wich tend to be more related to the depth [m] scale.
-
-Obviously nutrient content follows isopycnal layers.
-Konovalov (2006) locates the nitrate nitracline at 15.5 kg/m3.
-
-Between August and October, it seems the lower part of CHL limited and Sigma_1/2 rejoins Sigma_max. Light limitation by a well formed DCM ? 
-Indeed, it's in August that the percentage of CHL around DCM is highest, so that CHL density in the DCM zone is the thickest. 
-**Something strange with MLD .. How many defined MLD in summers ? Is there less ? is that what explain low variability in summer?**
-**I changed the definition of sigma MLD above, but ... dont get it.**
-
-```{r sigma}
+```{r Fig6}
 tmp_sig1 <- subset(tmp_fitco, select = c('month','sigmaMLD','sigmaMAX','sigmalow','sigma90B','sigma90T','sigmaiso1' ,'dcm_or_not','year','shape'))
 
-tmp_sig1$sigmaMAX[tmp_sig1$dcm_or_not==0]<-NA
-tmp_sig1$sigmaMAX[tmp_sig1$Zmax>200]<-NA
-#tmp_sig1$Zdemi[tmp_sig1$shape %in% c("O","GE","G")]<-NA
+tmp_sig1$ISOMAX[tmp_sig1$dcm_or_not==0]<-NA
+tmp_sig1$ISOMAX[tmp_sig1$Zmax>200]<-NA
 
@@
 
+## Absolute light Horizons
+
+```{r Review Fig light}
+
+tmp_iso1 <- subset(tmp_fitco, select = c('month','ISOMLD','ISOMAX','ISOlow','ISO90B','ISO90T','ISO_iso1' ,'dcm_or_not','year','shape'))
+
+tmp_iso1$sigmaMAX[tmp_iso1$dcm_or_not==0]<-NA
+tmp_iso1$sigmaMAX[tmp_iso1$Zmax>200]<-NA
+
+tmp_iso <- melt(tmp_iso1[,-which(colnames(tmp_iso1)=='dcm_or_not')], id.vars=c('month','year','shape'))
+
+ggplot(tmp_iso, aes(x=month, fill=variable, color=variable)) +
+    geom_smooth(aes(y=value),stat = 'summary',
+#              fun.data = median_hilow,
+              fun.data = mean_cl_boot,
+              fun.args = list(conf.int = 0.95), alpha=0.5)+
+  geom_boxplot(aes(y=value, group=interaction(month,variable)), alpha=0.2, notch = TRUE)+
+        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12)) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
+  #scale_y_continuous(trans = 'log10') + ylab('[microMoleQuanta/m^2/sec]') +
+  ylab('% of Incoming PAR') + theme_bw()  + scale_y_continuous(trans = 'log10') +
+      scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal,
+                       name="ISO Horizons", 
+                       labels=list(TeX('$\\ISO_{MLD}$'),
+                                TeX('$\\ISO_{DCM}$'),
+                                TeX('$\\ISO_{low}$'),
+                                TeX('$\\ISO_{50,bottom}$'),
+                                TeX('$\\ISO_{50,top}$'),
+                                TeX('$\\ISO_{\\mathrm{PAR}\\,1%}$')))
+
+```
+
 ## Vertical distribution of the CHL content
 
-In Summer, about 50-60 % (up to 75%) of the total chlorophyll content is located in a narrow 20m band around the DCM. 
-This DCM is located between 30-40m, which is about 4 times the optical depth estimated as the inverse of PAR attenuation profiles.
-
-The question is how much of this is missed by satellite ? 
-From May to August, less than 20% of the total Chl content is above the MLD (~)
-```{r parts}
+```{r Fig8}
 require(reshape2)

### 2020-10-27 article_figures_ARTHUR_CAPET.Rmd
add light horizons
update light horizons

@@
 complete_tmp2 <- cbind(complete_tmp2, light = interpolated_light_data$relative_light, light_absolute = interpolated_light_data$absolute_light)
+#complete_tmp2 <- cbind(complete_tmp2, light = interpolated_light_data$absolute_light)
 
@@
                             ISO90T       = try_default(approx(x=depth, y=light, xout=Z90T, rule=2)$y,NA, quiet = FALSE),
-                            ISOMLD       = min(light, na.rm = TRUE),
+                            ISOMLD       = try_default(approx(x=depth, y=light, xout=unique(MLD), rule=2)$y,NA, quiet = FALSE),
                             ISOMAX       = try_default(approx(x=depth, y=light, xout=unique(Zmax), rule=2)$y,NA, quiet = FALSE),
                             ISODEMI      = try_default(approx(x=depth, y=light, xout=unique(Zdemi), rule=2)$y,NA, quiet = FALSE),
-                          # just to see
-                            ISO_iso1 = try_default(approx(x=depth, y=light, xout=unique(Ziso1b), rule=2)$y,NA, quiet = FALSE)
+                            ISO_iso1 = try_default(approx(x=depth, y=light, xout=unique(Ziso1b), rule=2)$y,NA, quiet = FALSE),
+                          # Add ABSOLUTE Light levels
+                            ISOalow       = try_default(approx(x=depth, y=light_absolute, xout=ZLow, rule=2)$y,NA, quiet = FALSE),
+                            ISOa90B       = try_default(approx(x=depth, y=light_absolute, xout=Z90B, rule=2)$y,NA, quiet = FALSE),
+                            ISOa90T       = try_default(approx(x=depth, y=light_absolute, xout=Z90T, rule=2)$y,NA, quiet = FALSE),
+                            ISOaMLD       = try_default(approx(x=depth, y=light_absolute, xout=unique(MLD), rule=2)$y,NA, quiet = FALSE),
+                            ISOaMAX       = try_default(approx(x=depth, y=light_absolute, xout=unique(Zmax), rule=2)$y,NA, quiet = FALSE),
+                            ISOaDEMI      = try_default(approx(x=depth, y=light_absolute, xout=unique(Zdemi), rule=2)$y,NA, quiet = FALSE),
+                            ISOa_iso1 = try_default(approx(x=depth, y=light_absolute, xout=unique(Ziso1b), rule=2)$y,NA, quiet = FALSE)
                           )
@@
 ```{r}
-
 tmp_fitco<- tmp_fitc
@@
 
-## Absolute light Horizons
+## Relative & Absolute light Horizons
 
@@
 
-tmp_iso1 <- subset(tmp_fitco, select = c('month','ISOMLD','ISOMAX','ISOlow','ISO90B','ISO90T','ISO_iso1' ,'dcm_or_not','year','shape'))
+#relative light
+#tmp_iso1 <- subset(tmp_fitco, select = c('month','ISOMLD','ISOMAX','ISOlow','ISO90B','ISO90T','ISO_iso1' ,'dcm_or_not','year','shape'))
+tmp_iso1 <- subset(tmp_fitco, select = c('month','ISOMAX','ISOlow','ISO90B','ISO90T','dcm_or_not','year','shape'))
 
@@
 
-ggplot(tmp_iso, aes(x=month, fill=variable, color=variable)) +
+relative_light <- ggplot(tmp_iso, aes(x=month, fill=variable, color=variable)) +
     geom_smooth(aes(y=value),stat = 'summary',
 #              fun.data = median_hilow,
-              fun.data = mean_cl_boot,
+#              fun.data = mean_cl_boot,
               fun.args = list(conf.int = 0.95), alpha=0.5)+
@@
   ylab('% of Incoming PAR') + theme_bw()  + scale_y_continuous(trans = 'log10') +
-      scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal,
+      # scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal,
+      #                  name="ISO Horizons", 
+      #                  labels=list(#TeX('$\\ISO_{MLD}$'),
+      #                           TeX('$\\ISO_{DCM}$'),
+      #                           TeX('$\\ISO_{low}$'),
+      #                           TeX('$\\ISO_{50,bottom}$'),
+      #                           TeX('$\\ISO_{50,top}$')))#,
+      #                           #TeX('$\\ISO_{\\mathrm{PAR}\\,1%}$')))
+      scale_color_manual(aesthetics = c("colour", "fill"),values = c("#D95F02","#7570B3","#E7298A","#66A61E"), # [1] "#1B9E77" "#D95F02" "#7570B3" "#E7298A" "#66A61E" "#E6AB02" "#A6761D" "#666666"
                        name="ISO Horizons", 
-                       labels=list(TeX('$\\ISO_{MLD}$'),
-                                TeX('$\\ISO_{DCM}$'),
+                       labels=list(TeX('$\\ISO_{DCM}$'),
                                 TeX('$\\ISO_{low}$'),
                                 TeX('$\\ISO_{50,bottom}$'),
-                                TeX('$\\ISO_{50,top}$'),
-                                TeX('$\\ISO_{\\mathrm{PAR}\\,1%}$')))
+                                TeX('$\\ISO_{50,top}$')))
 
+relative_light
+
+#absolute light
+tmp_iso1 <- subset(tmp_fitco, select = c('month','ISOaMAX','ISOalow','ISOa90B','ISOa90T','dcm_or_not','year','shape'))
+
+tmp_iso1$sigmaMAX[tmp_iso1$dcm_or_not==0]<-NA
+tmp_iso1$sigmaMAX[tmp_iso1$Zmax>200]<-NA
+
+tmp_iso <- melt(tmp_iso1[,-which(colnames(tmp_iso1)=='dcm_or_not')], id.vars=c('month','year','shape'))
+
+absolute_light <- ggplot(tmp_iso, aes(x=month, fill=variable, color=variable)) +
+    geom_smooth(aes(y=value),stat = 'summary',
+#              fun.data = median_hilow,
+#              fun.data = mean_cl_boot,
+              fun.args = list(conf.int = 0.95), alpha=0.5)+
+  geom_boxplot(aes(y=value, group=interaction(month,variable)), alpha=0.2, notch = TRUE)+
+        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12)) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
+  scale_y_continuous(trans = 'log10') + ylab('[microMoleQuanta/m^2/sec]') + theme_bw()+
+  #ylab('% of Incoming PAR') + theme_bw()  + scale_y_continuous(trans = 'log10') +
+      # scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal,
+      #                  name="ISO Horizons", 
+      #                  labels=list(TeX('$\\ISO_{DCM}$'),
+      #                           TeX('$\\ISO_{low}$'),
+      #                           TeX('$\\ISO_{50,bottom}$'),
+      #                           TeX('$\\ISO_{50,top}$')))
+    scale_color_manual(aesthetics = c("colour", "fill"),values = c("#D95F02","#7570B3","#E7298A","#66A61E"), # [1] "#1B9E77" "#D95F02" "#7570B3" "#E7298A" "#66A61E" "#E6AB02" "#A6761D" "#666666"
+                       name="ISO Horizons", 
+                       labels=list(TeX('$\\ISO_{DCM}$'),
+                                TeX('$\\ISO_{low}$'),
+                                TeX('$\\ISO_{50,bottom}$'),
+                                TeX('$\\ISO_{50,top}$')))
+
+absolute_light
+
+# # https://www.datanovia.com/en/blog/top-r-color-palettes-to-know-for-great-data-visualization/
+# library(RColorBrewer)
+# display.brewer.pal(n = 8, name = 'Dark2')
+# brewer.pal(n=8, name='Dark2')
+
+#grid.arrange(relative_light + theme(legend.position="none"), absolute_light, nrow = 2)
+grid.arrange(relative_light, absolute_light, nrow = 2)
 ```
@@
                      aesthetics = c("colour", "fill"),type = qual ,palette=MyPal)#+ylim(c(0,100))
+
 ```

### 2020-11-05 article_figures_ARTHUR_CAPET.Rmd
update fig

@@
 ms<-ggmap(myMap_stamen)
-ms1<-ms+geom_point(data=tmp_fitco, aes(x=lon,y=lat, color=factor(dcm_or_not)))+
+ms1<-ms+geom_point(data=tmp_fitco, aes(x=lon,y=lat, color=factor(dcm_or_not)), alpha=.6)+
   facet_wrap(~monthn, scale="fixed")+
   theme_bw()+
-  scale_color_discrete(name="", labels=c('non-DCM','DCM'))+
+  #scale_color_discrete(name="", labels=c('non-DCM','DCM'))+
+  scale_color_manual(values = c("black", "red"), labels=c('non-DCM','DCM'), name="")+
   theme(legend.position = 'top', legend.box = "horizontal")+
   scale_x_continuous(name='', breaks = c(27,30,33,36,39), limits = c(27,42), expand = expand_scale(add = 0))+
-  scale_y_continuous(name='', breaks = seq(41,47), limits = c(40.7,47), expand = expand_scale(add = 0))
+  scale_y_continuous(name='', breaks = seq(41,47), limits = c(40.7,47), expand = expand_scale(add = 0)) +
+  # for another wrap colour (B/W instead of grey)
+  theme(panel.background=element_rect(fill='white', colour='black'),strip.background=element_rect(fill='white', colour='black'))
 

### 2020-11-12 article_figures_ARTHUR_CAPET.Rmd
Light Plots + chla/bbp ratio

--- 2020-10-26 article_figures_ARTHUR_CAPET.Rmd
@@
 
-p2b_start = c(PAR0 = 1500 ,  ks0 = 0.04 , kl0=0.001) 
+p2b_start = c(PAR0 = 1500 ,  ks0 = 0.04 , kl0=0.01) 
 p2b_lower = c(PAR0 = 0    ,  ks0 = 0    , kl0=0    )
@@
 
-## First attempt derives APR @ 1m from interpolation and look for 1/100 of this value
+## First attempt derives PAR @ 1m from interpolation and look for 1/100 of this value
 isoPAR <- function(depth, PAR){
@@
     P <- PAR[which( !is.na(depth) & PAR>0.1  )]
-
-    m <<-nls(PAR ~ Att_2band(depth,PAR0,ks0,kl0),
+    m <<-nls2(PAR ~ Att_2band(depth,PAR0,ks0,kl0),
            data = data.frame(depth=depth, PAR=PAR),
@@
     z100 <- interp1(PARcon,seq(1,200), PAR0/100) 
-      return(z100)},
+      return(c(z100,PAR0))},
       DefOut_isoPAR)
@@
                           Ziso1 = isoPAR(depth = depth , PAR = par),
-                          Ziso1b = isoPARb(depth = depth , PAR = par)
+                          Ziso1b = isoPARb(depth = depth , PAR = par)[1],
+                          PAR0  = isoPARb(depth = depth , PAR = par)[2]
                           )
@@
 }
-
 ```
@@
 ```{r add light data to full data}
-interpolated_light_data <- ldply(as.list(unique(complete_tmp2$juld)), function(i){
-  tmp1 <- complete_tmp2[complete_tmp2$juld == i,]
-  tmp2 <- initPAR[initPAR$juld == i,]
-  if(nrow(tmp2) == 0){
-    absolute_light <- rep(NA, nrow(tmp1))
-    # relative % of incoming surface PAR
+complete_tmp2 <- ddply(complete_tmp2,c('juld','platform'), function(dsub){
+  tmp <- subset(initPAR, (platform==dsub$platform[1]) & (juld==dsub$juld[1]) )
+  if(nrow(tmp) == 0){
+    absolute_light <- rep(NA, nrow(dsub))
     relative_light <- absolute_light
   }else{
-    absolute_light <- approx(tmp2$depth, tmp2$par, tmp1$depth)$y
-    # compute relative % of incoming surface PAR
-    relative_light <- (absolute_light/tmp2$par[1])*100 # could also put max(tmp2$par) car surface = max_par, therefore no ordering issue will appear (but tmp2$par[1] is good) 
+    absolute_light <- approx(tmp$depth, tmp$par, dsub$depth)$y
+    relative_light <- (absolute_light/dsub$PAR0)*100 # could also put max(tmp2$par) car surface = max_par, therefore no ordering issue will appear (but tmp2$par[1] is good) 
   }
-  data.frame(depth = tmp1$depth, absolute_light = absolute_light, relative_light = relative_light)
+  dsub$absolute_light<-absolute_light
+  dsub$relative_light<-relative_light
+  return(dsub)
 })
-
-# add it to complete_tmp2
-complete_tmp2 <- cbind(complete_tmp2, light = interpolated_light_data$relative_light, light_absolute = interpolated_light_data$absolute_light)
 
@@
                             sigmaDEMI      = try_default(approx(x=depth, y=sigma, xout=unique(Zdemi), rule=2)$y,NA, quiet = FALSE), 
-                            #Ziso1         = isoPAR(depth = depth , PAR = par),
                             sigmaiso1      = try_default(approx(x=depth, y=sigma, xout=unique(Ziso1b), rule=2)$y,NA, quiet = FALSE),
@@
                           # Adding diags for LIGHT Horizon here
-                            ISOlow       = try_default(approx(x=depth, y=light, xout=ZLow, rule=2)$y,NA, quiet = FALSE),
-                            ISO90B       = try_default(approx(x=depth, y=light, xout=Z90B, rule=2)$y,NA, quiet = FALSE),
-                            ISO90T       = try_default(approx(x=depth, y=light, xout=Z90T, rule=2)$y,NA, quiet = FALSE),
-                            ISOMLD       = min(light, na.rm = TRUE),
-                            ISOMAX       = try_default(approx(x=depth, y=light, xout=unique(Zmax), rule=2)$y,NA, quiet = FALSE),
-                            ISODEMI      = try_default(approx(x=depth, y=light, xout=unique(Zdemi), rule=2)$y,NA, quiet = FALSE),
-                          # just to see
-                            ISO_iso1 = try_default(approx(x=depth, y=light, xout=unique(Ziso1b), rule=2)$y,NA, quiet = FALSE)
+                            ISOlow       = try_default(approx(x=depth, y=relative_light, xout=ZLow, rule=2)$y,NA, quiet = FALSE),
+                            ISO90B       = try_default(approx(x=depth, y=relative_light, xout=Z90B, rule=2)$y,NA, quiet = FALSE),
+                            ISO90T       = try_default(approx(x=depth, y=relative_light, xout=Z90T, rule=2)$y,NA, quiet = FALSE),
+                            ISOMLD       = try_default(approx(x=depth, y=relative_light, xout=unique(MLD), rule=2)$y,NA, quiet = FALSE),
+                            ISOMAX       = try_default(approx(x=depth, y=relative_light, xout=unique(Zmax), rule=2)$y,NA, quiet = FALSE),
+                            ISODEMI      = try_default(approx(x=depth, y=relative_light, xout=unique(Zdemi), rule=2)$y,NA, quiet = FALSE),
+                            ISO_iso1     = try_default(approx(x=depth, y=relative_light, xout=unique(Ziso1b), rule=2)$y,NA, quiet = FALSE),
+                          # Add ABSOLUTE Light levels
+                            ISOalow       = try_default(approx(x=depth, y=light_absolute, xout=ZLow, rule=2)$y,NA, quiet = FALSE),
+                            ISOa90B       = try_default(approx(x=depth, y=light_absolute, xout=Z90B, rule=2)$y,NA, quiet = FALSE),
+                            ISOa90T       = try_default(approx(x=depth, y=light_absolute, xout=Z90T, rule=2)$y,NA, quiet = FALSE),
+                            ISOaMLD       = try_default(approx(x=depth, y=light_absolute, xout=unique(MLD), rule=2)$y,NA, quiet = FALSE),
+                            ISOaMAX       = try_default(approx(x=depth, y=light_absolute, xout=unique(Zmax), rule=2)$y,NA, quiet = FALSE),
+                            ISOaDEMI      = try_default(approx(x=depth, y=light_absolute, xout=unique(Zdemi), rule=2)$y,NA, quiet = FALSE),
+                            ISOa_iso1     = try_default(approx(x=depth, y=light_absolute, xout=unique(Ziso1b), rule=2)$y,NA, quiet = FALSE)
                           )
@@
 dbdf$fluo_norm <- dbdf$fluo/dbdf$chla_dcm
+
 dbdf$sigma_norm <- (dbdf$sigma-dbdf$sigmaMLD)/(dbdf$sigmaMAX-dbdf$sigmaMLD+.00000001)
@@
 
-dbdf$sigma_norm_layers <- cut(dbdf$sigma_norm,seq(0.05,3.05,.05))
-dbdf$depth_norm_layers <- cut(dbdf$depth_norm,seq(0.05,3.05,.05))
+dbdf$ration <- dbdf$fluo_norm/ dbdf$bbp_norm1 
+#dbdf$ratio  <- dbdf$fluo / dbdf$bbp
+
+dbdf$sigma_norm_layers <- cut(dbdf$sigma_norm,seq(0.05,3.05,.1))
+dbdf$depth_norm_layers <- cut(dbdf$depth_norm,seq(0.05,3.05,.1))
 ```
@@
 ```{r}
-blbl<-subset(dbdf, select=c("sigma_norm_layers","fluo_norm", "depth_norm_layers","depth_norm","sigma_norm","bbp_norm1","month",'lon'))
+blbl<-subset(dbdf, select=c("sigma_norm_layers","fluo_norm", "depth_norm_layers",
+                            "depth_norm","sigma_norm","bbp_norm1","month",'lon',"ration"))
 require(reshape2)
+
 blbl<-melt(blbl, id.vars=.(sigma_norm_layers,depth_norm_layers,month,depth_norm,sigma_norm,lon))
@@
 blbl$variable<-as.character(blbl$variable)
-blbl$variable[which(blbl$variable=="fluo_norm")]<-"Chla - norm."
-blbl$variable[which(blbl$variable=="bbp_norm1")]<-"Bbp - norm."
-
-blbl$variable<-factor(blbl$variable, levels=c("Chla - norm.","Bbp - norm."))
+blbl$variable[which(blbl$variable=="fluo_norm")]<-"Norm. Chla"
+blbl$variable[which(blbl$variable=="bbp_norm1")]<-"Norm. Bbp"
+blbl$variable[which(blbl$variable=="ration")]<-"N. Chla / N. bbp"
+blbl$variable<-factor(blbl$variable, levels=c("Norm. Chla","Norm. Bbp","N. Chla / N. bbp"))
 
@@
       geom_boxplot(aes(group=depth_norm_layers), outlier.size=0.5)+
-  theme_bw()+coord_flip(xlim = c(0,2), ylim=c(0,2))+
-  facet_grid(monthn~variable)+
+  theme_bw()+coord_flip(xlim = c(2,0), ylim=c(0,2))+
+  facet_grid(monthn~variable, scale="free")+
   geom_vline(xintercept  = 1)+xlab('Depth - norm.')+ylab('')
@@
         scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12)) +
-  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
-  ylab('[kg/m3]')+theme_bw()+coord_cartesian(ylim=c(16,10))+scale_y_reverse()+
+  theme_bw()+
+  theme(panel.grid.minor.x = element_line(colour = "grey"),
+        panel.grid.major.x = element_line(colour = "white")) +
+  ylab('[kg/m3]')+coord_cartesian(ylim=c(16,10))+scale_y_reverse()+
       scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal,
@@
                                 TeX('$\\sigma_{50,top}$'),
-                                TeX('$\\sigma_{\\mathrm{PAR}\\,1%}$')))+
-  geom_hline( yintercept = 14.5)
+                                TeX('$\\sigma_{\\mathrm{PAR}\\,1%}$')))
 
@@
 
-tmp_iso1 <- subset(tmp_fitco, select = c('month','ISOMLD','ISOMAX','ISOlow','ISO90B','ISO90T','ISO_iso1' ,'dcm_or_not','year','shape'))
+#relative light
+#tmp_iso1 <- subset(tmp_fitco, select = c('month','ISOMLD','ISOMAX','ISOlow','ISO90B','ISO90T','ISO_iso1' ,'dcm_or_not','year','shape'))
+tmp_iso1 <- subset(tmp_fitco, select = c('month','ISOMLD','ISOMAX','ISOlow','ISO90B','ISO90T','ISO_iso1','dcm_or_not','year'))
 
-tmp_iso1$sigmaMAX[tmp_iso1$dcm_or_not==0]<-NA
-tmp_iso1$sigmaMAX[tmp_iso1$Zmax>200]<-NA
+tmp_iso1$ISOMAX[tmp_iso1$dcm_or_not==0]<-NA
+tmp_iso1$ISOMAX[(tmp_iso1$month<3) | (tmp_iso1$month>10)]<-NA
 
-tmp_iso <- melt(tmp_iso1[,-which(colnames(tmp_iso1)=='dcm_or_not')], id.vars=c('month','year','shape'))
+tmp_iso <- melt(tmp_iso1[,-which(colnames(tmp_iso1)=='dcm_or_not')], id.vars=c('month','year'))
 
-ggplot(tmp_iso, aes(x=month, fill=variable, color=variable)) +
+relative_light <- ggplot(tmp_iso, aes(x=month, fill=variable, color=variable)) +
     geom_smooth(aes(y=value),stat = 'summary',
-#              fun.data = median_hilow,
-              fun.data = mean_cl_boot,
               fun.args = list(conf.int = 0.95), alpha=0.5)+
@@
         scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12)) +
-  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
-  #scale_y_continuous(trans = 'log10') + ylab('[microMoleQuanta/m^2/sec]') +
-  ylab('% of Incoming PAR') + theme_bw()  + scale_y_continuous(trans = 'log10') +
-      scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal,
+theme_bw()+
+  theme(panel.grid.minor.x = element_line(colour = "grey"),
+        panel.grid.major.x = element_line(colour = "white")) +
+  ylab('% of Incoming PAR') +  scale_y_continuous(trans = 'log10') +
+  scale_color_manual(aesthetics = c("colour", "fill"),
+                         values = c("#1B9E77", "#D95F02", "#7570B3", "#E7298A", "#66A61E", "#E6AB02"),
                        name="ISO Horizons", 
@@
                                    TeX('$\\ISO_{50,top}$'),
-                                TeX('$\\ISO_{\\mathrm{PAR}\\,1%}$')))
+                                   TeX('$\\ISO_{1%}$')))
 
+relative_light
+
+#absolute light
+tmp_iso1 <- subset(tmp_fitco, select = c('month','ISOaMLD','ISOaMAX','ISOalow','ISOa90B','ISOa90T','dcm_or_not','year','shape'))
+
+tmp_iso1$ISOaMAX[tmp_iso1$dcm_or_not==0]<-NA
+tmp_iso1$ISOaMAX[(tmp_iso1$month<3) | (tmp_iso1$month>10)]<-NA
+tmp_iso <- melt(tmp_iso1[,-which(colnames(tmp_iso1)=='dcm_or_not')], id.vars=c('month','year','shape'))
+
+absolute_light <- ggplot(tmp_iso, aes(x=month, fill=variable, color=variable)) +
+    geom_smooth(aes(y=value),stat = 'summary',
+#              fun.data = median_hilow,
+#              fun.data = mean_cl_boot,
+              fun.args = list(conf.int = 0.95), alpha=0.5)+
+  geom_boxplot(aes(y=value, group=interaction(month,variable)), alpha=0.2, notch = TRUE)+
+        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12)) +
+  theme_bw()+
+  theme(panel.grid.minor.x = element_line(colour = "grey"),
+        panel.grid.major.x = element_line(colour = "white")) +
+  scale_y_continuous(trans = 'log10') +
+  ylab(TeX('$\\mu molQuanta\\,m^{-2}\\,s^{-1}]$')) +
+  scale_color_manual(aesthetics = c("colour", "fill"),
+                     values = c("#1B9E77", "#D95F02", "#7570B3", "#E7298A", "#66A61E"),
+                       name="ISO Horizons", 
+                       labels=list(TeX('$\\ISO_{MLD}$'),
+                                   TeX('$\\ISO_{DCM}$'),
+                                TeX('$\\ISO_{low}$'),
+                                TeX('$\\ISO_{50,bottom}$'),
+                                TeX('$\\ISO_{50,top}$')))
+
+absolute_light
+
+# # https://www.datanovia.com/en/blog/top-r-color-palettes-to-know-for-great-data-visualization/
+# library(RColorBrewer)
+# display.brewer.pal(n = 8, name = 'Dark2')
+# brewer.pal(n=8, name='Dark2')
+
+#grid.arrange(relative_light + theme(legend.position="none"), absolute_light, nrow = 2)
+#grid.arrange(relative_light, absolute_light, nrow = 2)
 ```

### 2020-11-12 article_figures_FLORIAN_RICOUR.Rmd
update fig2

@@
   scale_y_reverse() + geom_path(data = data, aes(x = raw_roesler_fdom, y = depth, colour = "ROESLER + FDOM"), lwd = 1.5) +
-  xlab(expression(Chlorophyll~a~(mg/m^3)))+ ylab("Depth [m]") +
+  #xlab(expression(Chlorophyll~a~(mg/m^3)))+ 
+  ylab("Depth [m]") +
   geom_hline(yintercept = data_info$depthmin[1], color = "black", lty = 2) +
@@
   geom_point(data = df, aes(x = cdom/10, y = depth), colour = "black", size = .5) + 
-  geom_point(data=hplc, aes(y = depth_hplc, x = chla_hplc), colour = "red", size = 2, shape = 15)  + 
+  #geom_point(data=hplc, aes(y = depth_hplc, x = chla_hplc), colour = "red", size = 2, shape = 15)  + 
   scale_color_discrete(name = "Correction") +
-  theme_bw() + theme(legend.position = "none")
+  theme_bw() + theme(legend.position = "none") +
+  # add a secondary axis
+  scale_x_continuous(expression(Chlorophyll~a~(mg/m^3)), sec.axis = dup_axis(name = "CDOM (ppb)", trans = ~ .*10))
 

### 2020-11-12 article_figures_ARTHUR_CAPET.Rmd
light update 2

@@
                           # Add ABSOLUTE Light levels
-                            ISOalow       = try_default(approx(x=depth, y=light_absolute, xout=ZLow, rule=2)$y,NA, quiet = FALSE),
-                            ISOa90B       = try_default(approx(x=depth, y=light_absolute, xout=Z90B, rule=2)$y,NA, quiet = FALSE),
-                            ISOa90T       = try_default(approx(x=depth, y=light_absolute, xout=Z90T, rule=2)$y,NA, quiet = FALSE),
-                            ISOaMLD       = try_default(approx(x=depth, y=light_absolute, xout=unique(MLD), rule=2)$y,NA, quiet = FALSE),
-                            ISOaMAX       = try_default(approx(x=depth, y=light_absolute, xout=unique(Zmax), rule=2)$y,NA, quiet = FALSE),
-                            ISOaDEMI      = try_default(approx(x=depth, y=light_absolute, xout=unique(Zdemi), rule=2)$y,NA, quiet = FALSE),
-                            ISOa_iso1     = try_default(approx(x=depth, y=light_absolute, xout=unique(Ziso1b), rule=2)$y,NA, quiet = FALSE)
+                            ISOalow       = try_default(approx(x=depth, y=absolute_light, xout=ZLow, rule=2)$y,NA, quiet = FALSE),
+                            ISOa90B       = try_default(approx(x=depth, y=absolute_light, xout=Z90B, rule=2)$y,NA, quiet = FALSE),
+                            ISOa90T       = try_default(approx(x=depth, y=absolute_light, xout=Z90T, rule=2)$y,NA, quiet = FALSE),
+                            ISOaMLD       = try_default(approx(x=depth, y=absolute_light, xout=unique(MLD), rule=2)$y,NA, quiet = FALSE),
+                            ISOaMAX       = try_default(approx(x=depth, y=absolute_light, xout=unique(Zmax), rule=2)$y,NA, quiet = FALSE),
+                            ISOaDEMI      = try_default(approx(x=depth, y=absolute_light, xout=unique(Zdemi), rule=2)$y,NA, quiet = FALSE),
+                            ISOa_iso1     = try_default(approx(x=depth, y=absolute_light, xout=unique(Ziso1b), rule=2)$y,NA, quiet = FALSE)
                           )
@@
 
-#relative light
-#tmp_iso1 <- subset(tmp_fitco, select = c('month','ISOMLD','ISOMAX','ISOlow','ISO90B','ISO90T','ISO_iso1' ,'dcm_or_not','year','shape'))
 tmp_iso1 <- subset(tmp_fitco, select = c('month','ISOMLD','ISOMAX','ISOlow','ISO90B','ISO90T','ISO_iso1','dcm_or_not','year'))
@@
     geom_smooth(aes(y=value),stat = 'summary',
+                              fun.data = mean_cl_boot,
               fun.args = list(conf.int = 0.95), alpha=0.5)+
@@
 #              fun.data = median_hilow,
-#              fun.data = mean_cl_boot,
+              fun.data = mean_cl_boot,
               fun.args = list(conf.int = 0.95), alpha=0.5)+

### 2020-12-21 article_figures_ARTHUR_CAPET.Rmd
update markdown for figs

@@
     P <- PAR[which( !is.na(depth) & PAR>0.1  )]
-    m <<-nls2(PAR ~ Att_2band(depth,PAR0,ks0,kl0),
+    m <<-nls(PAR ~ Att_2band(depth,PAR0,ks0,kl0),
            data = data.frame(depth=depth, PAR=PAR),
@@
 
-```{r Fig9, fig.width=8, fig.height=6}
+```{r Fig10, fig.width=8, fig.height=6}
 grid.arrange(bigplot1+scale_x_reverse(),
@@
 
-ggplot(tmp_zmax, aes(x=month, fill=variable, color=variable)) +
-    geom_smooth(aes(y=value),stat = 'summary',
+depthplot <- ggplot(tmp_zmax, aes(x=month)) +
+    geom_smooth(aes(y=value, fill=variable, color=variable),stat = 'summary',
 #              fun.data = median_hilow,
@@
               fun.args = list(conf.int = 0.95), alpha=0.5)+
-  geom_boxplot(aes(y=value, group=interaction(month,variable)), alpha=0.2, notch = TRUE)+
-        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12)) +
+  geom_boxplot(aes(y=value, fill=variable, color=variable, group=interaction(month,variable)), alpha=0.2, notch = TRUE)+
+        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12), limits = c(0.5,12.5), expand = c(0, 0)) +
           scale_y_reverse(breaks = seq(100,0,-10), minor_breaks = NULL) +
-  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
   ylab('[m]')+theme_bw()+coord_cartesian(ylim=c(100,0))+
+    theme(panel.grid.minor.x = element_line(colour = "grey"),
+        panel.grid.major.x = element_line(colour = "white")) +
   #scale_y_reverse()+
@@
                                 TeX('$z_{\\mathrm{PAR}\\,1%}$')))
+
+depthplot
 ```
@@
 
-ggplot(tmp_sig, aes(x=month, fill=variable, color=variable)) +
-    geom_smooth(aes(y=value),stat = 'summary',
+densplot <- ggplot(tmp_sig, aes(x=month)) +
+    geom_smooth(aes(y=value, fill=variable, color=variable),stat = 'summary',
 #              fun.data = median_hilow,
@@
               fun.args = list(conf.int = 0.95), alpha=0.5)+
-  geom_boxplot(aes(y=value, group=interaction(month,variable)), alpha=0.2, notch = TRUE)+
-        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12)) +
+  geom_boxplot(aes(y=value, fill=variable, color=variable,group=interaction(month,variable)), alpha=0.2, notch = TRUE)+
+        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12), expand = c(1, 1)*0.01) +
   theme_bw()+
@@
         panel.grid.major.x = element_line(colour = "white")) +
-  ylab('[kg/m3]')+coord_cartesian(ylim=c(16,10))+scale_y_reverse()+
+  ylab(TeX('$\\left[kg\\,m^{-3}\\right]$$'))+coord_cartesian(ylim=c(16,10))+scale_y_reverse()+
       scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal,
@@
 
+densplot
+
 ```
@@
 ```{r Review Fig light}
-
 tmp_iso1 <- subset(tmp_fitco, select = c('month','ISOMLD','ISOMAX','ISOlow','ISO90B','ISO90T','ISO_iso1','dcm_or_not','year'))
@@
   geom_boxplot(aes(y=value, group=interaction(month,variable)), alpha=0.2, notch = TRUE)+
-        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12)) +
+        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12), expand = c(1, 1)*0.01) +
 theme_bw()+
@@
 relative_light
+```
 
+```{r Fig7}
 #absolute light
@@
 
-absolute_light <- ggplot(tmp_iso, aes(x=month, fill=variable, color=variable)) +
-    geom_smooth(aes(y=value),stat = 'summary',
+absolute_light <- ggplot(tmp_iso, aes(x=month)) +
+    geom_smooth(aes(y=value, fill=variable, color=variable),stat = 'summary',
 #              fun.data = median_hilow,
@@
               fun.args = list(conf.int = 0.95), alpha=0.5)+
-  geom_boxplot(aes(y=value, group=interaction(month,variable)), alpha=0.2, notch = TRUE)+
-        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12)) +
+  geom_boxplot(aes(y=value, fill=variable, color=variable, group=interaction(month,variable)), alpha=0.2, notch = TRUE)+
+        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12), expand = c(1, 1)*0.01) +
   theme_bw()+
@@
   scale_y_continuous(trans = 'log10') +
-  ylab(TeX('$\\mu molQuanta\\,m^{-2}\\,s^{-1}]$')) +
+  ylab(TeX('$\\left[\\mu mol\\,photons\\,m^{-2}\\,s^{-1}\\right]$')) +
   scale_color_manual(aesthetics = c("colour", "fill"),
                      values = c("#1B9E77", "#D95F02", "#7570B3", "#E7298A", "#66A61E"),
-                       name="ISO Horizons", 
-                       labels=list(TeX('$\\ISO_{MLD}$'),
-                                   TeX('$\\ISO_{DCM}$'),
-                                TeX('$\\ISO_{low}$'),
-                                TeX('$\\ISO_{50,bottom}$'),
-                                TeX('$\\ISO_{50,top}$')))
+                       name="PAR Horizons",
+                      labels=list(TeX('$\\mathrm{PAR$_{MLD}$'),
+                                   TeX('$\\mathrm{PAR}_{DCM}$'),
+                                   TeX('$\\mathrm{PAR}_{low}$'),
+                                   TeX('$\\mathrm{PAR}_{50,bottom}$'),
+                                   TeX('$\\mathrm{PAR}_{50,top}$')))
 
@@
 
+```{r FigR5, fig.width=10, fig.height=10}
+gA <- ggplotGrob(depthplot+
+  geom_text(data=data.frame(x=1, y=0, label='a)'), aes(x=x, y=y, label=label), color='black', fill='black', size=5))
+gB <- ggplotGrob(densplot+
+  geom_text(data=data.frame(x=1, y=10, label='b)'), aes(x=x, y=y, label=label), color='black', fill='black', size=5))
+gC <- ggplotGrob(absolute_light+
+  geom_text(data=data.frame(x=1, y=300, label='c)'), aes(x=x, y=y, label=label), color='black', fill='black', size=5))
+grid::grid.newpage()
+grid::grid.draw(rbind(gA, gB, gC))
+```
+
 ## Vertical distribution of the CHL content
 
-```{r Fig8}
+```{r Fig9}
 require(reshape2)
@@
 
-ggplot(tmp_part, aes(x=month, fill=variable, color=variable)) +
-    geom_smooth(aes(y=value),stat = 'summary',
+partplot <- ggplot(tmp_part, aes(x=month)) +
+    geom_smooth(aes(y=value, fill=variable, color=variable),stat = 'summary',
 #              fun.data = median_hilow,
@@
               fun.args = list(conf.int = 0.95), alpha=0.5)+
-        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12)) +
+        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12), expand = c(1,1)*0.01) +
+    theme_bw()+
+  theme(panel.grid.minor.x = element_line(colour = "grey"),
+        panel.grid.major.x = element_line(colour = "white")) +
         scale_y_continuous(breaks = seq(0,100,10), minor_breaks = NULL) +
-    geom_boxplot(aes(y=value, group=interaction(month,variable)), alpha=0.2)+
-  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
-  ylab('[%]')+theme_bw()+
+    geom_boxplot(aes(y=value, fill=variable, color=variable, group=interaction(month,variable)), alpha=0.2)+
+  ylab('[%]')+
   scale_color_brewer(name='Part of tot. Chl:',
@@
                      aesthetics = c("colour", "fill"),type = qual ,palette=MyPal)#+ylim(c(0,100))
+
+partplot
 
@@
 
-```{r Fig7}
+```{r Fig8}
 require(reshape2)
@@
 
-  ggplot(tmp_conc, aes(x=month, fill=variable, color=variable)) +
-      geom_smooth(aes(y=value),stat = 'summary',
+concplot<-  ggplot(tmp_conc, aes(x=month)) +
+      geom_smooth(aes(y=value, fill=variable, color=variable),stat = 'summary',
   #              fun.data = median_hilow,
@@
                 fun.args = list(conf.int = 0.95), alpha=0.5)+
-          scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12)) +
-      geom_boxplot(aes(y=value, group=interaction(month,variable)), alpha=0.2)+
+          scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12), expand = c(0, 0)) +
+        theme_bw()+
+  theme(panel.grid.minor.x = element_line(colour = "grey"),
+        panel.grid.major.x = element_line(colour = "white")) +
+      geom_boxplot(aes(y=value, fill=variable, color=variable, group=interaction(month,variable)), alpha=0.2)+
     theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
-    ylab('[mg/m3]')+theme_bw()+coord_cartesian(ylim=c(0,3.5))+
-    scale_color_brewer(aesthetics = c("colour", "fill"),type = qual,
-                       palette=MyPal, 
-                       name="Chla concentrations",
-                       labels=c("Average","Surface","DCM"))
+    ylab(TeX('$\\left[mg\\,m^{-3}\\right]$$'))+coord_cartesian(ylim=c(0,2.5))+
+    scale_color_manual(aesthetics = c("colour", "fill"),
+                     values = c("#1B9E77", "#7570B3","#D95F02"),#,  "#E7298A", "#66A61E"),
+                       name="Chla concentration", 
+                       labels=c("Total (scaled)","Surface","DCM"))
+
+concplot
+```
+
+```{r FigR6, fig.width=10, fig.height=6}
+gA <- ggplotGrob(concplot+
+  geom_text(data=data.frame(x=1, y=2.5, label='a)'), aes(x=x, y=y, label=label), color='black', fill='black', size=5))
+gB <- ggplotGrob(partplot+
+  geom_text(data=data.frame(x=1, y=100, label='b)'), aes(x=x, y=y, label=label), color='black', fill='black', size=5))
+
+grid::grid.newpage()
+grid::grid.draw(rbind(gA,gB))
 ```
@@
 
-```{r ratio_spatial2b}
+```{r Fig11, fig.width=10, fig.height=3}
 
@@
        aes(x = month, y = ratio, color=cutlon, fill=cutlon))+
-  theme_bw()+
    geom_boxplot(aes(group= bibi),
                 alpha=0.2, notch = TRUE, varwidth = FALSE, position='dodge2')+
-  scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12))+
+  scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12), expand = c(1,1)*0.01)+
+          theme_bw()+
+  theme(panel.grid.minor.x = element_line(colour = "grey"),
+        panel.grid.major.x = element_line(colour = "white")) +
   scale_color_brewer(aesthetics = c("colour", "fill"),
@@
 
-```{r Fig4,fig.width=8,fig.height=8}
+```{r Fig4,fig.width=8,fig.height=5}
 
@@
                   alpha=0.2, linetype=0)+
-  scale_x_continuous(name='', breaks=c(), labels="", limits=c(.5,12.5))+
+  scale_x_continuous(name='', breaks=c(), labels="", limits=c(.5,12.5), expand = c(0,0))+
   ylab('[m]')+theme_bw()+
@@
                        palette=MyPal,
-                       name="Depth Horizons", 
+                       name="Depth Horizons : ", 
                        labels=list(TeX('$z_{MLD}$'),
@@
   scale_x_continuous(name='', breaks=c(), labels="", limits=c(.5,12.5))+
-  ylab('[kg/m3]')+theme_bw()+
-  coord_cartesian(ylim=c(10,16), expand = FALSE)+
-  scale_y_reverse()+
+  ylab(TeX('$\\left[kg\\,m^{-3}\\right]$$'))+
+  coord_cartesian(ylim=c(16,10), expand = FALSE)+
+  theme_bw()+
   #scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal)+
   scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal,
-                       name="Density Horizons", 
+                       name="Density Horizons : ", 
                        labels=list(TeX('$\\sigma_{MLD}$'),
@@
 
+```{r inter_light, include=FALSE}
+#absolute light
+tmp_isoC<- dcast(tmp_iso,formula = month~variable, fun.aggregate = median, na.rm=TRUE)
+tmp_isoA<-melt(tmp_isoC, id.vars=c('month'))
+
+P_years_iso <-ggplot(tmp_iso, aes(x=month, fill=variable, color=variable)) +
+       geom_line(data=tmp_isoA,aes(y=value),alpha =1, size=0.5, linetype=2)+
+      geom_smooth(aes(y=value, group=interaction(year, variable)),stat = 'summary',
+             fun.data = mean_cl_boot,
+              fun.args = list(conf.int = 0.95), 
+                  alpha=0.2, linetype=0)+
+  scale_x_continuous(name='', breaks=c(), labels="", limits=c(.5,12.5))+
+  ylab(TeX('$\\left[\\mu mol\\,photons\\,m^{-2}\\,s^{-1}\\right]$'))+theme_bw()+
+    scale_y_continuous(trans = 'log10') +
+  #scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal)+
+  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal,
+                       name="PAR Horizons : ", 
+                       labels=list(TeX('$\\mathrm{PAR$_{MLD}$'),
+                                   TeX('$\\mathrm{PAR}_{DCM}$'),
+                                   TeX('$\\mathrm{PAR}_{low}$'),
+                                   TeX('$\\mathrm{PAR}_{50,bottom}$'),
+                                   TeX('$\\mathrm{PAR}_{50,top}$')))+
+  facet_grid(.~year)+
+  theme(legend.position = 'top', legend.box = "horizontal",panel.spacing = unit(0, "lines"))+
+          guides(colour = guide_legend(nrow = 1))
+P_years_iso
+
+```
+
 ```{r inter_parts, include=FALSE}
@@
                   alpha=0.2, linetype=0)+
-  scale_x_continuous(name='', breaks=c(), labels="", limits=c(.5,12.5))+
+  scale_x_continuous(name='', breaks=c(), labels="", limits=c(.5,12.5), expand = c(0,0))+
   ylab('[%]')+theme_bw()+coord_cartesian(ylim=c(0,100), expand = FALSE)+
-  scale_color_brewer(name='Part of tot. Chl:',
+  scale_color_brewer(name='Part of tot. Chl : ',
                      labels=c('above MLD','within 5m of DCM','above optical depth'),
@@
               fun.args = list(conf.int = 0.95), 
-                  alpha=0.2, linetype=0)+
-  scale_x_continuous(name='', breaks=c(), labels="", limits=c(.5,12.5))+
+                  alpha=0.3, linetype=0)+
+  scale_x_continuous(name='', breaks=c(), labels="", limits=c(.5,12.5), expand = c(0,0))+
   ylab('[mg/m3]')+theme_bw()+coord_cartesian(ylim=c(0,3), expand = FALSE)+
@@
                        palette=MyPal, 
-                       name="Chla concentrations",
-                       labels=c("Average","Surface","DCM"))+
+                       name="Chla concentrations : ",
+                       labels=c("Total (scaled)","Surface","DCM"))+
   facet_grid(.~year)+theme(legend.position = 'top', legend.box = "horizontal",panel.spacing = unit(0, "lines"))+ guides(colour = guide_legend(nrow = 1))
@@
 
-```{r Fig11, fig.height=12, fig.width=10}
+```{r Fig12, fig.height=12, fig.width=10}
 grid.arrange(P_years_depth,
              P_years_sig+theme( strip.background = element_blank(),strip.text.x = element_blank()), 
+             P_years_iso+theme( strip.background = element_blank(),strip.text.x = element_blank()), 
              P_years_part+theme( strip.background = element_blank(),strip.text.x = element_blank()),

### 2020-12-21 article_figures_FLORIAN_RICOUR.Rmd
update markdown for figs

--- 2020-07-29 article_figures_FLORIAN_RICOUR.Rmd
@@
                     year = year[1], DOY = DOY[1])
+
 rm(ncfile, smoothed_cdom, smoothed_fluo)
@@
 
-```{r correction_fig, include = T}
+```{r correction_fig, include = T, fig.width=8}
 #HPLC DATA FROM DEPLOYMENT
@@
   scale_color_discrete(name = "Correction") +
-  theme_bw() + theme(legend.position = "none")
+  theme_bw() + theme(legend.position = "none") +
+  # add a secondary axis
+  scale_x_continuous(expression(Chlorophyll~a~(mg/m^3)), sec.axis = dup_axis(name = "CDOM (ppb)", trans = ~ .*10))
 
@@
     dat <- cbind(tmp2$depth, dat)
+  }else if(shape == "O"){
+    return(ggplot(tmp2, aes(x = fluo, y = depth)) + geom_point() + scale_y_reverse(limits = c(90,0)) +
+    xlab("Normalized Chla") + ylab("Depth [m]") + theme_bw())
   }
@@
     theme_bw()
-
 }
@@
 
-```{r profile_examples}
+```{r profile_examples, fig.height=10, fig.width=10}
 
-flabels <- c("Gaussian (G)","Sigmoid (S)","Gaussian-Sigmoid (GS)","Gaussian-Exponential (GE)")
-profID  <- c(111,7,12,195)
+flabels <- c("Gaussian (G)","Sigmoid (S)","Gaussian-Sigmoid (GS)","Gaussian-Exponential (GE)", "NON-DCM GS",
+             "NON-DCM GE", "Other (O)", "NON-DCM G")
+profID  <- c(111,7,12,195,3,222,656,143)
 
-ex1 <- fit_curve(profID[1])+ggtitle(flabels[1]) + theme(axis.title.x=element_blank())
-ex2 <- fit_curve(profID[2])+ggtitle(flabels[2]) + theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
-ex3 <- fit_curve(profID[3])+ggtitle(flabels[3]) 
-ex4 <- fit_curve(profID[4])+ggtitle(flabels[4]) + theme(axis.title.y=element_blank())
+# DCM
+ex1 <- fit_curve(profID[1])+ggtitle(flabels[1]) + theme(axis.title.x=element_blank()) # DCM - Gaussian
+ex2 <- fit_curve(profID[2])+ggtitle(flabels[2])  # NON-DCM - Sigmoid
+ex3 <- fit_curve(profID[3])+ggtitle(flabels[3]) + theme(axis.title.x=element_blank()) # DCM - GS
+ex4 <- fit_curve(profID[4])+ggtitle(flabels[4]) + theme(axis.title.x=element_blank()) # GE
 
-grid.arrange(ex1, ex2, ex3, ex4, nrow = 2, ncol = 2)
+# NON DCM : O, GE, G, GS
+ex5 <- fit_curve(profID[5])+ggtitle(flabels[5]) + theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank()) # NON-DCM - GS
+ex6 <- fit_curve(profID[6])+ggtitle(flabels[6]) + theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank()) # GE
+ex7 <- fit_curve(profID[7])+ggtitle(flabels[7]) + theme(axis.title.y=element_blank()) # O
+ex8 <- fit_curve(profID[8])+ggtitle(flabels[8]) + theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank()) # G
+
+grid.arrange(ex1, ex8, ex3, ex5, ex4, ex6, ex2, ex7, nrow = 4, ncol = 2)
 
